### 2021-04-10 paper.tex
updates

\documentclass[11pt]{article}

\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}
%\usepackage{geometry}
\usepackage{graphicx}
\usepackage{enumerate}
%\usepackage{caption,subcaption}

\theoremstyle{definition}
\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{hyp}[thm]{Hypothesis}
\newtheorem{ex}[thm]{Example}

\numberwithin{equation}{section}
\numberwithin{thm}{section}

\DeclareMathOperator\erf{erf}

\newcommand{\winva}{{w_1^{-1}(a)}}
\newcommand{\winvb}{{w_1^{-1}(b)}}

\usepackage{authblk}

\title{Periodic Traveling Waves in an Integro-Difference Equation With a Nonmonotone Growth Function and Strong Allee Effect}

\author{Michael Nestor, Bingtuan Li
\thanks{M. Nestor's email is \href{mailto:mdnest01@louisville.edu}{mdnest01@louisville.edu}. B. Li was partially supported by the National Science Foundation under Grant DMS-1515875 and Grant DMS-1951482.}}

\affil{Department of Mathematics, University of Louisville, \newline Louisville, KY 40292.}

\begin{document}

\maketitle

\begin{abstract}
We derive sufficient conditions for the existence of periodic traveling wave solutions for a class of integro-difference equation with piecewise constant growth function exhibiting a period two cycle and a strong Allee effect. We also prove the convergence of solutions with compactly supported initial data to translations of the traveling wave under appropriate conditions. 
\end{abstract}

{\bf Key words:} Integro-difference equation, period two cycle, Allee effect, periodic traveling wave.
\newline

{\bf AMS Subject Classification:} 92D40, 92D25.

\section{Introduction}

Integro-difference equations are of great interest in the studies of invasions of populations with discrete generations and separate growth and dispersal stages. They have been used to predict changes in gene frequency \cite{lui82a, lui82b, lui83, slatkin, w78}, and applied to ecological problems~\cite{hh, ks, kot89, kot92, kotbook, lut, nkl,otto}. Previous rigrous studies on integro-difference equations have assumed that the growth function is nondecreasing~\cite{w78, wein82}, or  is nonmonotone without strong Allee effect~\cite{lui83, wang}. The results show existence of constant spreading speeds and travelng waves with fixed shapes and speeds.   Sullivan et al. ~\cite{pnas} demonstrated numerically  that an integro-difference equation with a nonmonotone growth function exhibiting  a strong Allee effect can generate traveling waves with fluctuating speeds. In this paper we give a sufficient condition for the existence of periodic traveling waves with a periodic speed for such an equation with a specific growth function.

We consider the following integro-difference equation
\begin{align}\label{q}
u_{n+1}(x)\;=\;Q[u_n](x)\;:=(k*(g\circ u_n))(x)\;=\,\int^{\infty}_{-\infty}k(x-y)\,g\big(u_n(y)\big)\,\mathrm{d}y,
\end{align}
where 
\begin{equation} \label{g}
g(u) = \begin{cases}
0, & \text{if } u < a, \\
1, & \text{if } a \leq u \leq b, \\
m, & \text{if } u > b,
\end{cases}
\end{equation}
with $0<a<m<b<1$. $g(u)$ is a piecewise constant nonmonotone growth function exhibiting a strong Allee effect~\cite{all}. Specifically, it has a stable fixed point at zero and a stable period two cycle $(1,m)$ with $a$ the Allee threshold value.

Piecewise constant growth functions and uniform distributions have been used in the studies of integro-difference equations; see for example~\cite{kot1, lut,otto,  pnas}. We rigorously construct periodic traveling waves with periodic speeds for (\ref{q}). To the best of our knowledge, this is the first time that traveling waves with oscillating speeds have been analytically established  for scalar spatiotemporal equations with constant parameters. We also show the convergence of solutions with compactly supported initial data to translations of the traveling wave under appropriate conditions. Equation (\ref{q}) may be viewed as a symbolic model for integro-difference equations with a growth function exhibiting a strong Allee effect and a period two cycle. The results obtained this paper provide important insights into integro-difference equations with general growth functions.

\section{Periodic traveling waves}

Let $C(\mathbb R)$ denote the space of continuous functions $\mathbb R\to\mathbb R$ equipped with the supremum-norm $||u||_\infty=\sup_{x\in\mathbb R}|u(x)|$ for any $u\in C(\mathbb R)$.

For the remainder of the paper, we assume the following hypothesis on the dispersal kernel:

\def\Hone{(\text{H1})}
\def\Htwo{(\text{H2})}
\def\Hthree{(\text{H3})}
\def\Hfour{(\text{H4})}

\begin{hyp} \label{hypothesis1} The disperal kernel $k$ is Lebesgue measurable, and

\begin{enumerate}[i.)]
\item $k$ is non-negative, and $\int_{-\infty}^{\infty} k(x) \, dx = 1$;

\item $k(x)=k(-x)$ for all $x\in\mathbb R$;

\item the support of $k$ is connected;

\item  for all $y\in\mathbb R$, for all $\mu\in(0,1)$, the function $f(x)= k(x)-\mu k(x-y)$ has at most one zero-crossing on $\mathbb R$.
\end{enumerate}
\end{hyp}

 Let $w_1$ and $w_2$ be two functions belonging to $C(\mathbb R)$ defined by
\begin{equation} \label{w1}
w_1(x) = \int_x^\infty k(y) \, dy
\end{equation}
and
\begin{equation} \label{w2}
w_2(x) = \int_{-\infty}^{\infty} k(y) g(w_1(x-y)) \, dy 
\end{equation}

Assuimption i. implies $w_1$ and $w_2$ have well-defined limits at $\pm\infty$ given by $w_1(\infty)=w_2(\infty)=0$, $w_1(-\infty)=1$, and $w_2(-\infty)=m$. Furthermore, $w_1$ is monotonically decreasing, while $w_2$ may be non-monotonic. Assumption iii. guarantees a unique right-inverse satisfying $w_1(w_1^{-1}(p))=p$ for $0<p<1$.

\begin{lem} \label{lemma1}
If condition (x) is satisfied then $Q[w_2](x)=w_1(x-2c^*)$ for a unique $c^*\in\mathbb R$.
\end{lem}

\begin{proof} Let $\alpha,\beta\in\mathbb R$ such that $w_1(\alpha)=a$ and $w_1(\beta)=b$.  By the definition of $w_1$, it is decreasing and satisfies $w_1(-\infty)=1$ and $w_1(\infty)=0$, hence $\alpha$ and $\beta$ are unique.  Applying the growth function $g$ yields
\begin{equation} \label{gw1}
g(w_1(x)) = \begin{cases}
m & x < \beta \\
1 & \beta \leq x \leq \alpha \\
0 & x > \alpha
\end{cases} \end{equation}
Applying the convolution operator yields a formula for $w_2(x)$:
\begin{equation} \label{w2}
\begin{aligned}
w_2(x) &= \int_{-\infty}^{\infty} k(y) g(w_1(x-y)) \, dy \\
&= \int_{x-\alpha}^{x-\beta} k(y)\,dy + \int_{x-\beta}^{\infty} m k(y)\,dy \\
&= \int_{x-\alpha}^{\infty} k(y)\,dy - \int_{x-\beta}^{\infty} (1-m) k(y)\,dy
\end{aligned}
\end{equation}
Taking the derivative with respect to $x$, we find
\begin{equation}
\frac{dw_2}{dx} = -k(x-\alpha) + (1-m)k(x-\beta)
\end{equation}
It follows from assumption iv. of \ref{hypothesis1} that $dw_2/dx$ has at most one zero-crossing. Hence, $w_2$ has at most one turning point. Since $w_2(-\infty)=m$ and $w_2(\infty)=0$, and $w_2$ is non-negative, there are only two cases.

First, $w_2$ has no turning point, and is monotone decreasing on $\mathbb R$. Then $w_2$ has a right inverse on $(0,m)$ satisfying $w_2(w_2^{-1}(p))=p$ for any $0<p<m$. Second, $w_2$ has a single turning point $x_0\in\mathbb R$. It follows that $w_2$ must be decreasing on $(x_0,\infty)$ and increasing on $(-\infty,x_0)$, with $w_2(x_0)\geq m$. In this case $w_2$ also has a well-defined right inverse on $(0,m)$, and furthermore $w_2^{-1}(p)>x_0$ for any $0<p<m$.

In either case, $w_2$ has a right inverse $w_2^{-1}$ on the interval $(0,m)$. Since $0<a<m$, we can take $c^*=\frac{1}{2}w_2^{-1}(a)$, so that $w_2(x)<a$ if and only if $x>2c^*$. Furthermore, since $||w_2||_\infty \leq b$, we have $w_2(x)\leq b$ almost everywhere. Thus,
\begin{equation} \label{gw2}
g(w_2(x)) = \begin{cases}
1 & x \leq 2c^* \\
0 & x > 2c^*
\end{cases}
\end{equation}
almost everywhere. Applying the convolution operator, we obtain
\begin{equation}
Q[w_2](x) = \int_{x-2c^*}^{\infty} k(y)\,dy = w_1(x-2c^*).
\end{equation}
\end{proof}

\begin{thm} \label{theorem1}
If $||w_2||_\infty\leq b$, then the sequence $(u_n)_{n=0}^{\infty}$ defined by
\begin{equation} \label{ptw}
u_{2n}(x) = w_1(x-2nc^*), \quad 
u_{2n+1}(x) = w_2(x-2nc^*)
\end{equation}
satisfies $u_{n+1}=Q[u_n]$ for all $n\geq 0$.
\end{thm}

\begin{proof}
By induction on $n$. For $n=0$, we have $u_0(x)=w_1(x)$ and $u_1(x)=Q[w_1](x)=w_2(x)$ by definition.

For the inductive step, assume $u_{2n}(x) = w_1(x-2nc^*)$ and $u_{2n+1}(x) = w_2(x-2nc^*)$ for some $n\geq 0$. By Lemma \ref{lemma1} and the translation invariance property of $Q$, we have
\begin{equation} \begin{aligned}
u_{2n+2}(x) = w_1(x-2nc^*-2c^*) = Q[w_2](x-2nc^*) = Q[u_{2n+1}](x)
\end{aligned} \end{equation}
 Likewise,
\begin{equation}
u_{2n+3}(x) = w_2(x-2nc^*-2c^*) = Q[w_1](x-2nc^*-2c^*) = Q[u_{2n+2}](x).
\end{equation}
\end{proof}

\begin{thm}  \label{theorem2}
If $||w_2||_\infty\leq b$, the sequence $(u_n)_{n=0}^{\infty}$ defined in Theorem \ref{theorem1} satisfies
\begin{equation}
\lim_{n\to\infty}\inf_{x<2nc}u_{2n}(x)=1, \quad \forall c\in(0,c^*)
\end{equation}
and
\begin{equation}
\lim_{n\to\infty}\inf_{x<2nc}u_{2n+1}(x)=m, \quad \forall c\in(0,c^*)
\end{equation}
and 
\begin{equation}
\lim_{n\to\infty}\sup_{x>nc}u_n(x)=0, \quad \forall c\in(c^*,\infty).
\end{equation}
\end{thm}

The next theorem concerns the spreading behavior of solutions to the IDE \eqref{q} with compactly supported initial data. We also assume the disperal kernel is compactly supported.

\begin{thm} Suppose $||w_2||_\infty \leq b$ and $k(x)$ has compact support. Assume the following hold:

\begin{enumerate}[i.)]
\item $c^*$ is positive,\
\item the initial condition $u_0$ has compact support;
\item the set $A=\{x\in\mathbb R:a\leq u_0(x)\leq b\}$  is connected and sufficiently large.
\end{enumerate}
 Then the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$, satisfies
\begin{equation}
\lim_{n\to\infty}\inf_{|x|<2nc}u_{2n}(x)=1, \quad \forall c\in(0,c^*)
\end{equation}
and
\begin{equation}
\lim_{n\to\infty}\inf_{|x|<2nc}u_{2n+1}(x)=m, \quad \forall c\in(0,c^*)
\end{equation}
and 
\begin{equation}
\lim_{n\to\infty}\sup_{|x|>nc}u_n(x)=0, \quad \forall c\in(c^*,\infty).
\end{equation}
\end{thm}

\begin{proof}
Let $(-\sigma,\sigma)$ be the support of $k$, for $0<\sigma<\infty$. Since $A$ is connected, we may also assume by the translation invariance property that $A=[-r,r]$ for some $r \geq 0$. Furthermore, since $u_0$ has compact support we must have $u_0(x)=0$ outside a bounded interval $(r^-,r^+) \supset A$, where $r^- < -r \leq r < r^+$.

Next, we will show that $0<u_0(x)<a$ for $x\in(r^-,r^+)\setminus A$. If we suppose to the contrary that $u_0(x)>b$ for some $x$ in this set, then suppose without loss of generality $x\in(r,r^+)$ such that $u_0(x)>b$. It follows by the intermediate value theorem that $u_0(x')=b$ for some $x' \in (x,r^+)$. But then $r\in A$, $x\notin A$, and $x'\in A$ with $r<x<x'$, violating the connectedness of $A$.

The preceding argument shows
\begin{equation}
g(u_0(x)) = \begin{cases}
1 & |x| < r \\
0 & |x| \geq r
\end{cases}
\end{equation}

To prove the theorem, we will show the spreading property is satisfied for all $r\geq2\sigma$. From $r\geq \sigma$ it follows,
\begin{equation}
u_1(x) = w_1(|x|-r)
\end{equation}
Then,
\begin{equation} g(u_1(x)) = \begin{cases}
m & |x|<r+\beta \\
1 & r+\beta\leq |x|\leq r+\alpha \\
0 & |x|>r+\alpha
\end{cases}
\end{equation}
where $\alpha$ and $\beta$ are defined as in Lemma \ref{lemma1}, and satisfy $-\sigma<\beta<\alpha<\sigma$. Note that $g(u_1(x))=g(Q[w](x))$ for all $x>-r-\beta$. Thus, $r\geq 2\sigma$ guarantees $r+\beta\geq\sigma$. It follows that
\begin{equation}
u_2(x) = Q[w_1](|x|-r) = w_2(|x|-r)
\end{equation}
Applying $g$, we get
\begin{equation}
g(u_2(x)) = \begin{cases}
1 & |x| \leq  r+2c^* \\
0 & |x| >  r+2c^*
\end{cases}
\end{equation}
Since $c^*>0$ we have $r+2c^*>r\geq\alpha$, so
\begin{equation}
u_3(x) = w_1(|x|-r-2c^*)
\end{equation}

The preceding argument can be repeated inductively to obtain
\begin{equation}
u_{2n+1}(x) = w_1(|x|-r-2nc^*)
\end{equation}
and
\begin{equation}
u_{2n+2}(x) = w_2(|x|-r-2nc^*)
\end{equation}
for all $n\geq 0$.
\end{proof}

\begin{rem}
This theorem indicates that a solution with proper compactly supported initial data coverges to translations of periodic traveling waves with profiles $w_1(x)$ and $w_2(x)$ in the positive direction and profiles $w_1(-x)$ and $w_2(-x)$ in the negative direction.
\end{rem}

\section{Examples}

In this section, we apply the results of Section 2 to three particular choices of dispersal kernel. We show that they satisfy Hypothesis \ref{hypothesis1}, and then provide an estimate of the wavespeed $c^*$.

\begin{ex}
The Laplace kernel,
\begin{equation}
k(x) = \frac{1}{2} e^{-|x|}
\end{equation}

The traveling waves are given by
\begin{equation}
w_1(x) =   \begin{cases} 
1 - \frac{1}{2}e^{x} & x \leq 0 \\
\frac{1}{2}e^{-x} & x > 0
\end{cases}
\end{equation}
and
\begin{equation}
w_2(x) = \int_{-\infty}^\winvb mk(x-y)\,dy + \int_{\winvb}^\winva k(x-y)\,dy
\end{equation}
with
$$ w_1^{-1}(p) = \begin{cases} -\log(2p) & p\leq \frac{1}{2} \\ \log(2-2p) & p > \frac{1}{2} \end{cases} $$
Then
$$ w_2(x) = \begin{cases}
\int_{-\infty}^{-\log(2b)} \frac{m}{2}e^{-|x-y|}\,dy + \int_{-\log(2b)}^{-\log(2a)} \frac{1}{2}e^{-|x-y|} \,dy & a<\frac{1}{2}, b < \frac{1}{2} \\
\int_{-\infty}^{\log(2-2b)} \frac{m}{2}e^{-|x-y|} \,dy + \int_{\log(2-2b)}^{-\log(2a)} \frac{1}{2}e^{-|x-y|} \,dy & a<\frac{1}{2}, b \geq \frac{1}{2} \\ 
\int_{-\infty}^{\log(2-2b)} \frac{m}{2}e^{-|x-y|} \,dy + \int_{\log(2-2b)}^{\log(2-2a)} \frac{1}{2}e^{-|x-y|} \,dy & a\geq\frac{1}{2}, b \geq \frac{1}{2} \\
\end{cases} $$
Now make the substitution $y'=x-y$.
$$ w_2(x) = \begin{cases}
\int_{x+\log(2b)}^{\infty} \frac{m}{2}e^{-|y'|}\,dy' + \int_{x+\log(2b)}^{x+\log(2a)} \frac{1}{2}e^{-|y'|} \,dy' & a<\frac{1}{2}, b < \frac{1}{2} \\
\int_{x-\log(2-2b)}^{\infty} \frac{m}{2}e^{-|y'|} \,dy' + \int_{x-\log(2-2b)}^{x+\log(2a)} \frac{1}{2}e^{-|y'|} \,dy' & a<\frac{1}{2}, b \geq \frac{1}{2} \\ 
\int_{x-\log(2-2b)}^{\infty} \frac{m}{2}e^{-|y'|} \,dy' + \int_{x-\log(2-2b)}^{x-\log(2-2a)} \frac{1}{2}e^{-|y'|} \,dy' & a\geq\frac{1}{2}, b \geq \frac{1}{2} \\
\end{cases} $$

We will now split into further cases.

Case 1: $a<b<\frac{1}{2}$. Then
$$ w_2(x) = \int_{x+\log(2b)}^{\infty} \frac{m}{2}e^{-|y|}\,dy + \int_{x+\log(2b)}^{x+\log(2a)} \frac{1}{2}e^{-|y|} \,dy $$
$$ = $$

\end{ex}

\begin{ex} Consider the Gaussian kernel with mean $0$ and variance $1$ given by
$$ k(x) = \frac{1}{\sqrt{2\pi}} e^{-\frac{x^2}{2}} $$
$k$ is symmetric, strictly increasing on $(-\infty,0)$ and strictly decreasing on $(0,\infty)$, hence conditions i.-iii. of Hypothesis \ref{hypothesis1} are satisfied. For condition iv., let $y \in \mathbb R$ and $\mu\in(0,1)$. It can be shown that $k(x) - \mu k(x-y) = B(x)(1-Ce^{-xy})$ where $B(x)=e^{-\frac{x^2}{2}}/\sqrt{2\pi}$ is a strictly positive function and $C>0$. This quantity decreases monotonically from $1$ to $-\infty$ with a unique zero-crossing at $x=\frac{y}{2}-\frac{\ln \mu}{y}$. Thus, Hypothesis \ref{hypothesis1} is satisfied.

The periodic traveling wave solutions $w_1(x)$ and $w_2(x)$ are given by
\begin{equation}
w_1(x) = \frac{1}{2} - \frac{1}{2}\erf\left(\frac{x}{\sqrt{2}}\right)
\end{equation}
and
\begin{equation}
w_2(x)=  \frac{m}{2} + \frac{1-m}{2} \erf \left( \frac{x-\beta}{\sqrt 2}\right) - \frac{1}{2} \erf \left( \frac{x-\alpha}{\sqrt2} \right)
\end{equation}
where $\alpha=\sqrt{2}\erf^{-1}\left(1-2a\right)$, and $\beta=\sqrt{2}\erf^{-1}\left(1-2b\right)$, and $\erf$ is the error function defined by $\erf(x) =\frac{2}{\sqrt\pi}\int_0^x e^{-y^2}\,dy$.

$w_2$ has a unique global maximum at $x^*=\frac{\alpha+\beta}{2} + \frac{1}{\alpha-\beta}\ln\left(1-m\right)$. Thus, by Theorem \ref{theorem1}, $w_1$ and $w_2$ are a periodic traveling wave solution if $w_2(x^*)\leq b$.
\end{ex}

%\begin{ex} The Laplace kernel is given by
%$$ k(x) = \frac{1}{2} e^{-\frac{1}{2}|x|} $$
%
%It can be checked that $k(x)$ satisfies all of Hypothesis \ref{hypothesis1}. To show part iv., let $\mu\in(0,1)$, and assume without loss of generality $y>0$. (If $y=0$ then $f(x)$ is simply $k(x)$ rescaled, hence strictly positive.) For $y>0$, we have
%$$ f(x) = k(x) - \mu k(x-y) = \frac{1}{2} \begin{cases}
%e^x - \mu e^{x-y} & \text{if } x < 0 \\
%e^{-x} - \mu e^{x-y} & \text{if } 0 \leq x < y \\
%
%e^{-x} -\mu e^{-(x-y)} & \text{if } x \geq y
%\end{cases} $$
%$f$ is continuous, satisfies $f(-\infty)=f(\infty)=0$, is increasing on $(-\infty,0)$ and decreasing on $(0,\alpha)$. If $e^y\geq \mu$, then $f$ is decreasing on $(y,\infty)$, so $f$ has no zero-crossings Otherwise, if $e^y< \mu$, then $f$ is increasing on $(y,\infty)$ and has exactly one zero-crossing. In both cases, condition iv. is satisfied.
%
%We have three cases:
%
% If $a<\frac{1}{2}$ and $b<\frac{1}{2}$, then
%$$ \begin{aligned}
%w_2(-x) &= n_{2}K\left(x-\frac{1}{\alpha}\ln\left(2a\right)\right)-\left(1-m\right)K\left(x-\frac{1}{\alpha}\ln\left(2b\right)\right) \\
%&= \begin{cases}
%\left(\frac{1}{4a}-\frac{1-m}{4b}\right)e^{\alpha x} & x < \frac{1}{\alpha}\ln\left(2a\right) \\
%1-ae^{-\alpha x}-\frac{1-m}{4b}e^{\alpha x} &  \frac{1}{\alpha}\ln\left(2a\right) \leq x < \frac{1}{\alpha}\ln\left(2b\right) \\
%m+\left((1-m)b-a\right)e^{-\alpha x} &  x \geq \frac{1}{\alpha}\ln\left(2b\right)
%\end{cases} 
%\end{aligned} $$
%If $b-(1-m)a\geq 2ab$, then $c^*$ is given by $c^*=\frac{1}{2\alpha}\ln\left(\frac{b-(1-m)a}{4a^2b}\right)$.
%\end{ex}

\begin{ex}
Consider the uniform dispersal kernel given by
\begin{equation}
k(x) = \begin{cases}
\frac{1}{2} & |x|\leq 1 \\
0 & |x| > 1
\end{cases} \end{equation}

Then $w_1$ is given by
\begin{equation}  \label{w1}
\begin{aligned}
w_1(x) 
= \begin{cases}
1, & x \in (-\infty, -1), \\
\frac{1}{2}-\frac{1}{2}x, & x \in [-1, 1] ,\\
0, & x \in (1, \infty),
\end{cases}
\end{aligned} \end{equation}
with inverse $w_1^{-1}(p)=1-2p$ for $0<p<1$. Let $\alpha=1-2a$ and $\beta=1-2b$. Then
\begin{equation} \label{w2}
\begin{aligned}
w_2(x) 
= \begin{cases}
m,
& x \in (-\infty, \beta-1), \\
\frac{1-m}{2}x + m + b - mb,
& x \in [\beta - 1, 
 \alpha- 1), \\
-\frac{m}{2}x +m+b- mb-a,
& x \in [\alpha - 1, \beta + 1), \\
-\frac{1}{2} x-a+1,
& x \in [\beta + 1, \alpha + 1], \\
0,
& x \in (\alpha+1,\infty).
\end{cases}
\end{aligned} \end{equation}

Observe that $w_2$ has a global maximum at $x=\alpha-1$ so that $||w_2||_\infty=w_2(\alpha-1)=m+(b-a)(1-m)$. By Theorem \ref{theorem2}, the pair $w_1$ and $w_2$ are a solution to equation \eqref{ptw} if $m-a<m(b-a)$.

We can also explicitly calculate the speed of the wave given by
\begin{equation} \label{c}
c^* = \begin{cases}
1 - 2a & \text{if } a \leq b/2, \\
1 -b + \frac{b - 2a}{m} & \text{if }a > b/2.
\end{cases}
\end{equation}
\end{ex}
\begin{rem}
$w_1(x)$ is positive for $x<1$ and zero for $x\geq1$, and $w_2(x)$ is positive for $x<2-2a$ and zero for $x\geq 2-2a$. Thus, $\eqref{q}$ has a traveling wave with wave profiles $w_1(x)$ and $w_2(x)$, intermediate wave speeds $c_1=1-2a$ and $c_2=2c^*-c_1$,  and average wave speed  $c^*$.  It is easily seen that $c_1=c_2$ if $a \leq b/2$, and $|c_1-c_2|=(2\alpha-\beta)(1-\frac{1}{m})>0$ if $a>b/2$. So for $a>b/2$, the traveling wave is periodic with two different intermediate wave speeds. Furthermore, the difference between these two intermediate speeds is increasing in $a$, decreasing in $b$, and increasing in $m$. This behavior is illustrated with two difference choices of parameters in Figure \ref{fig:wavespeed}.
\end{rem}

The regions in the parameter space where oscillating spreading speed exists can be determined as follows: for any fixed choice of $(n_1,n_2)$, with $0<n_1<n_2$, let $R$ be the set of pairs $(a,b)\in\mathbf R^2$ such that the hypothesis of Theorem 2.1 holds. Then $R$ is a triangle in the $a$-$b$ plane with endpoints at $(0,n_2)$, $(n_1,n_1)$, and $(n_1,n_2)$, depicted in Figure \ref{fig:phaseportrait}. The line $b=2a$ partitions $R$ into two non-empty sets $R_1=\{(a,b)\in R:a\leq b/2\}$ and $R_2=\{(a,b)\in R:a> b/2\}$ such that the traveling has constant speed if $(a,b)\in R_1$ and oscillating speed if $(a,b)\in R_2$.

\begin{thebibliography}{9}
\bibitem{all}  W. C. Allee. 1931. Animal Aggregations. A Study on
General Sociology. University of Chicago Press, Chicago, IL.

%\bibitem{htw90} D. P. Hardin, P. Tak$\acute{\mbox{a}}\check{\mbox{c}}$, and G. F. Webb. 1990. Dispersion population %models discrete in time and
%continuous in space. J. Math. Biol. {\bf 28}: 1-20.

\bibitem{hh} A. Hastings and K. Higgins. 1994. Persistence of transients in spatially
structured ecological models. Science {\bf 263}: 1133-1136.

%\bibitem{hz} S.-B. Hsu and X.-Q. Zhao. 2008. Spreading speeds and traveling waves for nonmonotone integrodifference equations. SIAM J. Math. Anal. {\bf} 40: 776–789

\bibitem{ks} M. Kot and W. M. Schaffer. 1986.  Discrete-time growth-dispersal models.
Math. Biosci. {\bf 80}: 109-136.

\bibitem{kot89} M. Kot. 1989. Diffusion-driven period doubling bifurcations.
Biosystems {\bf 22}: 279-287.

\bibitem{kot92} M. Kot. 1992. Discrete-time traveling waves:
Ecological examples. J. Math. Biol. {\bf 30}: 413-436.

\bibitem{kot1} M. Kot, M. A. Lewis, and P. van den Driessche. 1996. Dispersal data and the spread of invading
organisms. Ecology {\bf 77}: 2027-2042.

%\bibitem{kot2} M. Kot, J. Medlock, T. Reluga, and D. B. Walton. 2004. Stochasticity, invasions, and branching random walks. Theor. Popul. Biol. {\bf 66}: 175-184.

%\bibitem{li09} B. Li, M. A. Lewis, and H. F. Weinberger. 2009.  Existence of traveling waves for integral recursions with nonmonotone growth functions. J. Math. Biol. {\bf 58}: 323-338.

\bibitem{kotbook} M. Kot. 2001. Elements of Mathematical Ecology.
Cambridge University Press. Cambridge, United Kingdom.

\bibitem{lui82a} R. Lui. 1982. A nonlinear integral operator arising from a model in population
genetics. I. Monotone initial data. SIAM. J. Math. Anal. {\bf 13}:
913-937.

\bibitem{lui82b} R. Lui. 1982. A nonlinear integral operator arising from a model in population
genetics. II. Initial data with compact support. SIAM. J. Math.
Anal. {\bf 13}: 938-953.

\bibitem{lui83} R. Lui. 1983. Existence and stability of traveling wave solutions of a nonlinear
integral operator. J. Math. Biol. {\bf 16}:199-220.

\bibitem{lut}
F. Lutscher. 2019. Integrodifference Equations in Spatial Ecology.  Springer.

\bibitem{nkl} M. Neubert, M. Kot, and M. A. Lewis. 1995. Dispersal and pattern formation in a
discrete-time predator-prey model. Theor. Pop. Biol. {\bf 48}
: 7-43.

\bibitem{otto} G. Otto. 2017. Non-spreading Solutiona in a Integro-Difference Model Incorporating Allee and Overcompensation Effects. Ph. D thesis, University of Louisville.

\bibitem{slatkin} M. Slatkin. 1973. Gene flow and selection in a cline.
Genetice {\bf 75}: 733-756.

\bibitem{pnas} L. L. Sullivan, B. Li, T. E. X. Miller, M. G. Neubert, and A. K. Shaw. 2017.
Density dependence in demography and dispersal generates fluctuating invasion speeds. Proc. Natl. Acad. Sci. USA {\bf
114}: 5053-5058.

\bibitem{wang} M. H. Wang, M. Kot, and M. G. Neubert. 2002. Integrodifference equations, Allee effects, and
invasions. J. Math. Biol. {\bf 44}: 150-168.

\bibitem{w78} H. F. Weinberger. 1978. Asymptotic behavior of a model in  population genetics,
in Nonlinear Partial Differential Equations  and Applications, ed.
J. M. Chadam. Lecture Notes in Mathematics {\bf 648}: 47-96.
Springer-Verlag, Berlin.

\bibitem{wein82} H. F.  Weinberger. 1982. Long-time beahvior of a class of biological models. SIAM. J.
Math. Anal. {\bf 13}: 353-396.

\end{thebibliography}

\end{document}

\end{document}

### 2021-05-09 paper_draft2.tex
added exponential case 2

--- 2021-04-10 paper.tex
@@
 
+In this section, we generalize the theory of traveling wave solutions of \ref{q} to the theory of periodic traveling waves.
+
 Let $C(\mathbb R)$ denote the space of continuous functions $\mathbb R\to\mathbb R$ equipped with the supremum-norm $||u||_\infty=\sup_{x\in\mathbb R}|u(x)|$ for any $u\in C(\mathbb R)$.
@@
 Hence, $w_2$ has at most one turning point.
-Since $w_2(-\infty)=m$ and $w_2(\infty)=0$, and $w_2$ is non-negative, there are only two cases.
+This leaves two cases: either $w_2$ has no turning points and is monotonically decreasing, or it has one turning point, to the left of which $w_2$ is increasing and to the right it is decreasing.
+In both cases, $w_2$ has a continuous right inverse on the open interval $(0,m)$.
 
-First, $w_2$ has no turning point, and is monotone decreasing on $\mathbb R$.
-Then $w_2$ has a right inverse on $(0,m)$ satisfying $w_2(w_2^{-1}(p))=p$ for any $0<p<m$.
-Second, $w_2$ has a single turning point $x_0\in\mathbb R$.
-It follows that $w_2$ must be decreasing on $(x_0,\infty)$ and increasing on $(-\infty,x_0)$, with $w_2(x_0)\geq m$.
-In this case $w_2$ also has a well-defined right inverse on $(0,m)$, and furthermore $w_2^{-1}(p)>x_0$ for any $0<p<m$.
-
-In either case, $w_2$ has a right inverse $w_2^{-1}$ on the interval $(0,m)$.
-Since $0<a<m$, we can take $c^*=\frac{1}{2}w_2^{-1}(a)$, so that $w_2(x)<a$ if and only if $x>2c^*$.
-Furthermore, since $||w_2||_\infty \leq b$, we have $w_2(x)\leq b$ almost everywhere.
-Thus,
+Since $0<a<m$, we can take $x_0=w_2^{-1}(a)$  so that $w_2$ exceeds the Allee threshold to the left of $x_0$ and is below the Allee threshold on the right. Applying the growth function,
 \begin{equation} \label{gw2}
 g(w_2(x)) = \begin{cases}
-1 & x \leq 2c^* \\
-0 & x > 2c^*
-\end{cases}
+1 & x \leq w_2^{-1}(a) \\
+0 & x > w_2^{-1}(a)
+\end{cases} \quad \text{almost everywhere}
 \end{equation}
-almost everywhere. Applying the convolution operator, we obtain
+Applying the integro-difference operator, we obtain
 \begin{equation}
-Q[w_2](x) = \int_{x-2c^*}^{\infty} k(y)\,dy = w_1(x-2c^*).
+Q[w_2](x) = \int_{x-w_2^{-1}(a)}^{\infty} k(y)\,dy = w_1(x-w_2^{-1}(a)).
+\end{equation}
+By defining $c^* = \frac{1}{2}w_2^{-1}(a)$, and applying the integro-difference operator, we can see that $w_1$ and $w_2$ are both solutions to the periodic traveling wave equation with mean speed $c^*$:
+\begin{equation}
+Q^2[w_1](x) = w_1(x-2c^*); \quad Q^2[w_2](x) = w_2(x-2c^*)
 \end{equation}
@@
 \begin{thm}  \label{theorem2}
-If $||w_2||_\infty\leq b$, the sequence $(u_n)_{n=0}^{\infty}$ defined in Theorem \ref{theorem1} satisfies
+For all $\epsilon>0$, the sequence $(u_n)_{n=0}^{\infty}$ defined in Theorem \ref{theorem1} satisfies
 \begin{equation}
-\lim_{n\to\infty}\inf_{x<2nc}u_{2n}(x)=1, \quad \forall c\in(0,c^*)
+\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n}(x)=1
 \end{equation}
@@
 \begin{equation}
-\lim_{n\to\infty}\inf_{x<2nc}u_{2n+1}(x)=m, \quad \forall c\in(0,c^*)
+\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n+1}(x)=m
 \end{equation}
@@
 \begin{equation}
-\lim_{n\to\infty}\sup_{x>nc}u_n(x)=0, \quad \forall c\in(c^*,\infty).
+\lim_{n\to\infty}\sup_{x>n(c^*+\epsilon)}u_n(x)=0.
 \end{equation}
@@
 
-In this section, we apply the results of Section 2 to three particular choices of dispersal kernel.
-We show that they satisfy Hypothesis \ref{hypothesis1}, and then provide an estimate of the wavespeed $c^*$.
+In this section, we construct the population density functions $w_1$ and $w_2$ for several choices of dispersal kernel.
 
@@
 
+Conversely, we may define $\sigma_p=\text{sign}(p-\frac{1}{2})$. Then, we have $w_1^{-1}(p)=\sigma_p\log(\sigma_p(2p+1)+1)$. The above equation then simplifies to
+\begin{equation}
+w_2(x) = \int_{-\infty}^{\sigma_a\log(\sigma_a(2a+1)+1)} mk(x-y)\,dy + \int_{\sigma_b\log(\sigma_b(2p+1)+1)}^{\sigma_a\log(\sigma_a(2a+1)+1)} k(x-y)\,dy
+\end{equation}
+
 We will now split into further cases.
@@
 Case 1: $a<b<\frac{1}{2}$. Then
-$$ w_2(x) = \int_{x+\log(2b)}^{\infty} \frac{m}{2}e^{-|y|}\,dy + \int_{x+\log(2b)}^{x+\log(2a)} \frac{1}{2}e^{-|y|} \,dy $$
-$$ = $$
+$$ w_2(x) = \int_{x-\log(2b)}^{\infty} \frac{m}{2}e^{-|y|}\,dy + \int_{x-\log(2b)}^{x-\log(2a)} \frac{1}{2}e^{-|y|} \,dy $$
+We can expand this out using $\min$ and $\max$ functions. Let $x_a=x-\log(2a)$ and $x_b=x-\log(2b)$. Then
+$$ w_2(x) = \int_{\min(x_b,0)}^0 \frac{m}{2} e^y \, dy + \int_{\max(x_b,0)}^{\infty} \frac{m}{2} e^{-y} \, dy
++ \int_{\min(x_b,0)}^{\min(x_a,0)} \frac{1}{2} e^y \, dy + \int_{\max(x_b,0)}^{\max(x_a,0)} \frac{1}{2} e^{-y} \, dy $$
+We can now take the integral:
+$$ \frac{m}{2} - \frac{m}{2} e^{\min(x_b,0)} - \frac{m}{2} e^{-\max(x_b,0)} + \frac{1}{2} e^{\min(x_a,0)} - \frac{1}{2} e^{\min(x_b,0)} - \frac{1}{2} e^{-\max(x_a,0)} + \frac{1}{2} e^{-\max(x_b,0)} $$
+This is equal to
+$$ \frac{m}{2} - \frac{m}{2} \min(e^{x_b},1) - \frac{m}{2} \min(e^{-x_b},1) + \frac{1}{2} \min(e^{x_a},1) - \frac{1}{2} \min(e^{x_b},1) - \frac{1}{2} \min(e^{-x_a},1) + \frac{1}{2} \min(e^{-x_b},1) $$
+$$ = \frac{m}{2} - \frac{m+1}{2} \min(e^{x_b},1) - \frac{m+1}{2} \min(e^{-x_b},1) - \frac{1}{2} \min(e^{x_a},1) - \frac{1}{2} \min(e^{-x_a},1)$$
+$$ = \frac{m}{2} - \frac{m+1}{2}\left( \min(e^{x_b},1) - \min(e^{-x_b},1) \right) - \frac{1}{2} \left( \min(e^{x_a},1) - \min(e^{-x_a},1) \right) $$
+
+$$ = \frac{m}{2} - \frac{m+1}{2}\left( \min(2be^{-x},1) - \min(\frac{1}{2b}e^{x},1) \right) - \frac{1}{2} \left( \min(2ae^{-x},1) - \min(\frac{1}{2a}e^{x},1) \right) $$
+
+It can be written in three cases
+
+$$ w_2(x) = \begin{cases} \displaystyle
+m - \frac{am+a-b}{4ab} e^x & x <\log(2a) \\
+\displaystyle
+m + 1 - \frac{m+1}{4b} e^x - ae^{-x} & \log(2a) \leq x \leq \log(2b) \\
+\displaystyle
+(mb+b-a) e^{-x}  & x > \log(2b)
+\end{cases} $$
+
+Since $w_2$ is increasing for $x<\log(2a)$, we know the solution to $w_2(x)=a$ must lie on the second or third pieces.
+This can be determined by checking the sign of $w_2(\log(2b))-a$.
+If it is positive, the horizontal line $y=a$ intersects the curve $y=w_2(x)$ on the third piece, and the solution can be found by solving $(mb+b-a)e^{-x}=a$.
+Otherwise, if the sign is negative, the solution occurs on the second piece as the solution to the equation
+
+$$ w_2(x)=a \iff m + 1 - \frac{m+1}{4b} e^x - ae^{-x} = a $$
+
+First let us group like terms and multiply by $4b$:
+
+$$ (m+1) e^x + (m + 1 - a) - 4abe^{-x} = 0 $$
+
+Using the substitution $y=e^x$, this equation becomes a quadratic in $y$:
+
+$$ (m+1) y^2 + (m + 1 - a) y - 4ab = 0 $$
+
+The solution is
+
+$$ y = \frac{a-m-1 \pm \sqrt{(m+1-a)^2 + 16ab(m+1)}}{2m+2}$$
+
+We know the global maximum of $w_2(x)$ lies somewhere in the open interval $(\log(2a),\log(2b))$, therefore we take the greater solution so that
+
+$$ c^* = \frac{1}{2} \log\left(  \frac{a-m-1 + \sqrt{(m+1-a)^2 + 16ab(m+1)}}{2m+2} \right) $$
+
+Then we can obtain the critical wave speed in two cases:
+$$ c^* = \begin{cases} \displaystyle
+\frac{1}{2} \log \left( \frac{mb+b-a}{a} \right) & m \geq \frac{2ab+a-b}{b} \\
+\displaystyle
+ \frac{1}{2} \log\left(  \frac{a-m-1 + \sqrt{(m+1-a)^2 + 16ab(m+1)}}{2m+2} \right) & m < \frac{2ab+a-b}{b}
+\end{cases} $$
+
+Case 2: $a<\frac{1}{2}<b$. Then
+$$ w_2(x) = \int_{x+\log(2-2b)}^{\infty} \frac{m}{2}e^{-|y|}\,dy + \int_{x+\log(2-2b)}^{x-\log(2a)} \frac{1}{2}e^{-|y|} \,dy $$
+
+Then
+
+$$ w_2(x) = \frac{m}{2} - \frac{m+1}{2}\left( \min(\frac{e^{-x}}{2-2b},1) - \min((2-2b)e^{x},1) \right) - \frac{1}{2} \left( \min(2ae^{-x},1) - \min(\frac{1}{2a}e^{x},1) \right) $$
+
+so
+
+$$ w_2(x) = \begin{cases}
+\displaystyle
+m - \frac{4a(m+1)(1-b)-1}{4a} e^x & x <\log(2a) \\
+\displaystyle
+m+1 - (m+1)(a-b) e^x - ae^{-x} & \log(2a) \leq x \leq -\log(2-2b) \\
+\displaystyle
+\frac{m+1-4a(1-b)}{4(1-b)} e^{-x}  & x > -\log(2-2b)
+\end{cases} $$
 

### 2021-06-01 paper_draft2.tex
worked on Gaussian kernel

@@
 The Laplace kernel,
-\begin{equation}
+\begin{equation}\label{laplacekernel}
 k(x) = \frac{1}{2} e^{-|x|}
@@
 
-The traveling waves are given by
+One can easily verify conditions i. - iii. of Hypothesis 2.1. To check condition iv., we introduce the following lemma:
+
+\begin{lem}
+The Laplace kernel \eqref{laplacekernel} satisfies condition (iv.) of Hypothesis 2.1.
+\end{lem}
+
+\begin{proof}
+let $f=f_{m,y}$ be the scalar function of $x$ with two parameters $y\in\mathbb R$ and $\mu\in(0,1)$ defined by
+$$ f(x)= f_{m,y}(x) = \frac{1}{2} e^{-|x|} - \frac{\mu}{2}e^{-|x-y|} $$
+
+If $y=0$, then $f$ has no zero-crossings, since $f_{m,0}(x)=\frac{1-\mu}{2}e^{-|x|}$ is strictly positive.
+If $y$ is nonzero, then one can easily check the symmetry relation $f_{m,-y}(x)=f_{m,y}(-x)$.
+Since the number of zero-crossings are invariant with respect to a reflection about the vertical axis, we can assume without loss of generality $y>0$.
+
+Under this assumption, $f$ is strictly increasing on $(-\infty,0)$, and strictly decreasing on $(0,y)$. The behavior on $(y,\infty)$ is determined by the sign of $e^{-y}-m$. There are three cases:
+
+\begin{enumerate}
+\item if $e^{-y}>m$, then $f$ is decreasing on $(0,\infty)$, hence has no zero-crossings;
+\item if $e^{-y}<m$, then $f$ has a unique zero-crossing at $x=\frac{1}{2}(y-\ln(m))$;
+\item if $e^{-y}=m$, then $f$ vanishes on $(y,\infty)$, hence it has no zero-crossings.
+\end{enumerate}
+In each case, the number of zero-crossings does not exceed one.
+\end{proof}
+
+We have shown that the Laplace kernel satisfies Hypothesis 2.1; thus, we can construct a periodic traveling wave solution:
+
 \begin{equation}
@@
 and
-\begin{equation}
-w_2(x) = \int_{-\infty}^\winvb mk(x-y)\,dy + \int_{\winvb}^\winva k(x-y)\,dy
+\begin{equation}\label{laplacew2}
+w_2(x) = \int_{x-\winva}^{\infty} \frac{1}{2} e^{-|y|} \,dy - \int_{x-\winva}^{\infty} \frac{1-m}{2} e^{-|y|} \,dy
 \end{equation}
 with
-$$ w_1^{-1}(p) = \begin{cases} -\log(2p) & p\leq \frac{1}{2} \\ \log(2-2p) & p > \frac{1}{2} \end{cases} $$
+$$ w_1^{-1}(p) = \begin{cases} -\ln(2p) & p\leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases} $$
+
+The integrals in \eqref{laplacew2} can be computed using elementary methods to obtain
+\begin{equation}
+w_2(x) = \begin{cases}
+-\frac{1}{2}e^{x-w_1^{-1}(a)} + \frac{1}{2}e^{x-w_1^{-1}(b)} & x < w_1^{-1}(b) \\
+1 - \frac{1}{2} e^{x-w_1^{-1}(a)} - \frac{1}{2} e^{-(x-w_1^{-1}(b))} & w_1^{-1}(b) < x < w_1^{-1}(a) \\
+\frac{1}{2} e^{-(x-w_1^{-1}(a))} - \frac{1}{2} e^{-(x-w_1^{-1}(b))} & x > w_1^{-1}(a)
+\end{cases}
+\end{equation}
+
 Then
@@
 
-\begin{ex} Consider the Gaussian kernel with mean $0$ and variance $1$ given by
+\begin{ex} Consider the Gaussian kernel with zero mean and unit variance given by
 $$ k(x) = \frac{1}{\sqrt{2\pi}} e^{-\frac{x^2}{2}} $$
@@
 For condition iv., let $y \in \mathbb R$ and $\mu\in(0,1)$.
-It can be shown that $k(x) - \mu k(x-y) = B(x)(1-Ce^{-xy})$ where $B(x)=e^{-\frac{x^2}{2}}/\sqrt{2\pi}$ is a strictly positive function and $C>0$.
+It can be shown that $k(x) - \mu k(x-y) = B(x)(1-Ce^{-xy})$ where $B(x)$ is a strictly positive function of $x$, and $C>0$.
 This quantity decreases monotonically from $1$ to $-\infty$ with a unique zero-crossing at $x=\frac{y}{2}-\frac{\ln \mu}{y}$.

### 2021-06-01 paper_draft2.tex
gaussian kernel work

@@
 \begin{enumerate}
-\item if $e^{-y}>m$, then $f$ is decreasing on $(0,\infty)$, hence has no zero-crossings;
-\item if $e^{-y}<m$, then $f$ has a unique zero-crossing at $x=\frac{1}{2}(y-\ln(m))$;
-\item if $e^{-y}=m$, then $f$ vanishes on $(y,\infty)$, hence it has no zero-crossings.
+\item if $y<\ln\frac{1}{m}$, then $f$ is decreasing on $(0,\infty)$, hence has no zero-crossings;
+\item if $y>\ln\frac{1}{m}$, then $f$ has a unique zero-crossing at $x=\frac{1}{2}(y-\ln(m))$;
+\item if $y=\ln\frac{1}{m}$, then $f$ vanishes on $(y,\infty)$, hence it has no zero-crossings.
 \end{enumerate}
@@
 \begin{equation}\label{laplacew2}
-w_2(x) = \int_{x-\winva}^{\infty} \frac{1}{2} e^{-|y|} \,dy - \int_{x-\winva}^{\infty} \frac{1-m}{2} e^{-|y|} \,dy
+w_2(x) = \int_{x-\winva}^{\infty} \frac{1}{2} e^{-|y|} \,dy - \int_{x-\winvb}^{\infty} \frac{1-m}{2} e^{-|y|} \,dy
 \end{equation}
@@
 w_2(x) = \begin{cases}
--\frac{1}{2}e^{x-w_1^{-1}(a)} + \frac{1}{2}e^{x-w_1^{-1}(b)} & x < w_1^{-1}(b) \\
+\frac{1}{2} e^x \left( e^{-w_1^{-1}(b)} -e^{-w_1^{-1}(a)} \right)  & x < w_1^{-1}(b) \\
 1 - \frac{1}{2} e^{x-w_1^{-1}(a)} - \frac{1}{2} e^{-(x-w_1^{-1}(b))} & w_1^{-1}(b) < x < w_1^{-1}(a) \\
-\frac{1}{2} e^{-(x-w_1^{-1}(a))} - \frac{1}{2} e^{-(x-w_1^{-1}(b))} & x > w_1^{-1}(a)
+\frac{1}{2} e^{-x} \left(  e^{w_1^{-1}(a)} - e^{w_1^{-1}(b)} \right) & x > w_1^{-1}(a)
 \end{cases}
 \end{equation}
+
+We can split into three cases:
+
+\begin{enumerate}
+\item $a<\frac{1}{2}$, $b<\frac{1}{2}$. Then
+\begin{equation}
+w_2(x) = \begin{cases}
+\frac{1}{2} e^x \left( e^{-w_1^{-1}(b)} -e^{-w_1^{-1}(a)} \right)  & x < w_1^{-1}(b) \\
+1 - \frac{1}{2} e^{x-w_1^{-1}(a)} - \frac{1}{2} e^{-(x-w_1^{-1}(b))} & w_1^{-1}(b) < x < w_1^{-1}(a) \\
+\frac{1}{2} e^{-x} \left(  e^{w_1^{-1}(a)} - e^{w_1^{-1}(b)} \right) & x > w_1^{-1}(a)
+\end{cases}
+\end{enumerate}
 

### 2021-06-13 paper_draft3.tex
Rework

--- 2021-06-01 paper_draft2.tex
@@
 \newcommand{\winvb}{{w_1^{-1}(b)}}
+\renewcommand{\a}{\alpha}
+\renewcommand{\b}{\beta}
+\newcommand{\m}{\mu}
 
@@
 
+{\bf Todo:} Proof of Theorem 2.2.
+\newline
+
 {\bf AMS Subject Classification:} 92D40, 92D25.
@@
 g(u) = \begin{cases}
-0, & \text{if } u < a, \\
-1, & \text{if } a \leq u \leq b, \\
-m, & \text{if } u > b,
+0, & \text{if } u < \a, \\
+1, & \text{if } \a \leq u \leq \b, \\
+\m, & \text{if } u > \b,
 \end{cases}
 \end{equation}
-with $0<a<m<b<1$.
+with $0<\a<\m<\b<1$.
 $g(u)$ is a piecewise constant nonmonotone growth function exhibiting a strong Allee effect~\cite{all}.
-Specifically, it has a stable fixed point at zero and a stable period two cycle $(1,m)$ with $a$ the Allee threshold value.
+Specifically, it has a stable fixed point at zero and a stable period two cycle $(1,\m)$ with $\a$ the Allee threshold value.
 
@@
 
-In this section, we generalize the theory of traveling wave solutions of \ref{q} to the theory of periodic traveling waves.
-
-Let $C(\mathbb R)$ denote the space of continuous functions $\mathbb R\to\mathbb R$ equipped with the supremum-norm $||u||_\infty=\sup_{x\in\mathbb R}|u(x)|$ for any $u\in C(\mathbb R)$.
-
-For the remainder of the paper, we assume the following hypothesis on the dispersal kernel:
+In this section, we construct a periodic traveling wave solution to the recurrence \eqref{q}. We will assume the dispersal kernel $k$ satisfies the following hypotheses:
 
@@
 
-\begin{hyp} \label{hypothesis1} The disperal kernel $k$ is Lebesgue measurable, and
+%\begin{hyp} \label{hypothesis1} The disperal kernel $k$ is Lebesgue measurable, and
 
-\begin{enumerate}[i.)]
-\item $k$ is non-negative, and $\int_{-\infty}^{\infty} k(x) \, dx = 1$;
+\begin{enumerate}[(H1)]
+\item $k$ is a non-negative Lebesgue-integrable function with $\int_{-\infty}^{\infty} k(x) \, dx = 1$;
 
@@
 
-\item  for all $y\in\mathbb R$, for all $\mu\in(0,1)$, the function $f(x)= k(x)-\mu k(x-y)$ has at most one zero-crossing on $\mathbb R$.
+\item  for all $\lambda\in(0,1)$, for all $y\in\mathbb R$, the function $x \mapsto k(x)-\lambda k(x-y)$ has at most one zero-crossing in $\mathbb R$.
 \end{enumerate}
-\end{hyp}
+%\end{hyp}
+
+Under these assumptions, the cumulative density function $F(x)=\int_{-\infty}^{x}k(y)\,dy$ has a well-defined right inverse $F^{-1}$ satisfying $F(F^{-1}(p))=p$ for all $0<p<1$.
+Furthermore, it satisfies the symmetry relation $F(-x)=1-F(x)$.
 
@@
 
-Assuimption i.
-implies $w_1$ and $w_2$ have well-defined limits at $\pm\infty$ given by $w_1(\infty)=w_2(\infty)=0$, $w_1(-\infty)=1$, and $w_2(-\infty)=m$.
+Hypothesis (H1) implies $w_1$ and $w_2$ have well-defined limits at $\pm\infty$ given by $w_1(\infty)=w_2(\infty)=0$, $w_1(-\infty)=1$, and $w_2(-\infty)=\m$.
 Furthermore, $w_1$ is monotonically decreasing, while $w_2$ may be non-monotonic.
-Assumption iii.
-guarantees a unique right-inverse satisfying $w_1(w_1^{-1}(p))=p$ for $0<p<1$.
 
 \begin{lem} \label{lemma1}
-If condition (x) is satisfied then $Q[w_2](x)=w_1(x-2c^*)$ for a unique $c^*\in\mathbb R$.
+If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then there exists unique $c^*\in\mathbb R$ such that $Q[w_2](x)=w_1(x-2c^*)$ for all $x\in\mathbb R$.
 \end{lem}
 
-\begin{proof} Let $\alpha,\beta\in\mathbb R$ such that $w_1(\alpha)=a$ and $w_1(\beta)=b$.
-By the definition of $w_1$, it is decreasing and satisfies $w_1(-\infty)=1$ and $w_1(\infty)=0$, hence $\alpha$ and $\beta$ are unique.
-Applying the growth function $g$ yields
+\begin{proof} Let $x_\a=\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}$.
+It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$.
+Thus, composing $w_1(x)$ with the growth function $g$ yields
 \begin{equation} \label{gw1}
 g(w_1(x)) = \begin{cases}
-m & x < \beta \\
-1 & \beta \leq x \leq \alpha \\
-0 & x > \alpha
+\mu & x < x_\beta \\
+1 & x_\beta \leq x \leq x_\a \\
+0 & x > x_\a
 \end{cases} \end{equation}
+
 Applying the convolution operator yields a formula for $w_2(x)$:
-\begin{equation} \label{w2}
+\begin{equation} \label{w2calculation}
 \begin{aligned}
 w_2(x) &= \int_{-\infty}^{\infty} k(y) g(w_1(x-y)) \, dy \\
-&= \int_{x-\alpha}^{x-\beta} k(y)\,dy + \int_{x-\beta}^{\infty} m k(y)\,dy \\
-&= \int_{x-\alpha}^{\infty} k(y)\,dy - \int_{x-\beta}^{\infty} (1-m) k(y)\,dy
+&= \int_{x-x_\a}^{x-x_\b} k(y)\,dy + \m \int_{x-\beta}^{\infty} k(y)\,dy \\
+&= \int_{x-x_\a}^{\infty} k(y)\,dy - (1-\m) \int_{x-x_\b}^{\infty} k(y)\,dy
 \end{aligned}
 \end{equation}
+
 Taking the derivative with respect to $x$, we find
+\begin{equation}\label{dw2dx}
+\frac{dw_2}{dx} = -k(x-x_\a) + (1-\m)k(x-x_\b)
+\end{equation}
+
+From hypothesis (H4), we can conclude that \eqref{dw2dx} has at most one zero-crossing, hence $w_2(x)$ has at most one turning point. This leaves two cases:
+\begin{enumerate}[{Case} 1.]
+\item If $w_2$ has no turning points, it must be monotonically decreasing.
+\item If $w_2$ has a single turning point $x^*$, then $w_2(x)$ is increasing on $(-\infty,x^*)$ and decreasing on $(x^*,\infty)$, with $\m \leq w_2(x^*)\leq \b$.
+\end{enumerate}
+
+In both cases, $w_2(x)$ has a well-defined right inverse on the open interval $(0,\m)$. Since $0<\a<\m$, let
 \begin{equation}
-\frac{dw_2}{dx} = -k(x-\alpha) + (1-m)k(x-\beta)
+c^*=\frac{1}{2}\sup\{x\in\mathbb R\mid w_2(x)\geq\a\}
 \end{equation}
-It follows from assumption iv.
-of \ref{hypothesis1} that $dw_2/dx$ has at most one zero-crossing.
-Hence, $w_2$ has at most one turning point.
-This leaves two cases: either $w_2$ has no turning points and is monotonically decreasing, or it has one turning point, to the left of which $w_2$ is increasing and to the right it is decreasing.
-In both cases, $w_2$ has a continuous right inverse on the open interval $(0,m)$.
 
-Since $0<a<m$, we can take $x_0=w_2^{-1}(a)$  so that $w_2$ exceeds the Allee threshold to the left of $x_0$ and is below the Allee threshold on the right. Applying the growth function,
+It follows that $w_2(x)\geq\a$ for $x\leq 2c^*$ and $w_2(x)<\alpha$ for $x>2c^*$. Along with the assumption that $\sup_{x\in\mathbb R}w_2(x)\leq\b$, we can compose with $g$ as follows:
 \begin{equation} \label{gw2}
 g(w_2(x)) = \begin{cases}
-1 & x \leq w_2^{-1}(a) \\
-0 & x > w_2^{-1}(a)
-\end{cases} \quad \text{almost everywhere}
+1 & x \leq 2c^* \\
+0 & x > 2c^*
+\end{cases} \end{equation}
+
+Taking convolution with $k$, we obtain
+\begin{equation}
+Q[w_2](x) = \int_{x-x_0}^{\infty} k(y)\,dy = w_1(x-2c^*).
 \end{equation}
-Applying the integro-difference operator, we obtain
-\begin{equation}
-Q[w_2](x) = \int_{x-w_2^{-1}(a)}^{\infty} k(y)\,dy = w_1(x-w_2^{-1}(a)).
-\end{equation}
-By defining $c^* = \frac{1}{2}w_2^{-1}(a)$, and applying the integro-difference operator, we can see that $w_1$ and $w_2$ are both solutions to the periodic traveling wave equation with mean speed $c^*$:
-\begin{equation}
-Q^2[w_1](x) = w_1(x-2c^*); \quad Q^2[w_2](x) = w_2(x-2c^*)
-\end{equation}
+%By defining $c^* = \frac{1}{2}x_0$, and applying the integro-difference operator, we can see that $w_1$ and $w_2$ are both solutions to the periodic traveling wave equation with mean speed $c^*$:
+%\begin{equation}
+%Q^2[w_1](x) = w_1(x-2c^*); \quad Q^2[w_2](x) = w_2(x-2c^*)
+%\end{equation}
 \end{proof}
@@
 \begin{thm} \label{theorem1}
-If $||w_2||_\infty\leq b$, then the sequence $(u_n)_{n=0}^{\infty}$ defined by
+If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then the recurrence \eqref{q} has a periodic traveling wave solution given by
 \begin{equation} \label{ptw}
-u_{2n}(x) = w_1(x-2nc^*), \quad 
-u_{2n+1}(x) = w_2(x-2nc^*)
+W_n(x) = \begin{cases}
+w_1(x-nc^*) & n \text{ even} \\
+w_2(x-nc^*) & n \text{ odd}
+\end{cases}
 \end{equation}
-satisfies $u_{n+1}=Q[u_n]$ for all $n\geq 0$.
 \end{thm}
@@
 \begin{proof}
-By induction on $n$. For $n=0$, we have $u_0(x)=w_1(x)$ and $u_1(x)=Q[w_1](x)=w_2(x)$ by definition.
-
-For the inductive step, assume $u_{2n}(x) = w_1(x-2nc^*)$ and $u_{2n+1}(x) = w_2(x-2nc^*)$ for some $n\geq 0$. By Lemma \ref{lemma1} and the translation invariance property of $Q$, we have
-\begin{equation} \begin{aligned}
-u_{2n+2}(x) = w_1(x-2nc^*-2c^*) = Q[w_2](x-2nc^*) = Q[u_{2n+1}](x)
-\end{aligned} \end{equation}
- Likewise,
-\begin{equation}
-u_{2n+3}(x) = w_2(x-2nc^*-2c^*) = Q[w_1](x-2nc^*-2c^*) = Q[u_{2n+2}](x).
-\end{equation}
+DO THIS
 \end{proof}
@@
 
-In this section, we construct the population density functions $w_1$ and $w_2$ for several choices of dispersal kernel.
+In this section, we construct the periodic traveling wave solution for several well-known disperal kernels in population biology, namely the uniform, Laplace, and normal distributions.
+For the uniform and Laplace kernels, we were able to construct a piecewise expression for the mean wave speed in terms of the model parameters.
 
@@
 
-One can easily verify conditions i. - iii. of Hypothesis 2.1. To check condition iv., we introduce the following lemma:
-
-\begin{lem}
-The Laplace kernel \eqref{laplacekernel} satisfies condition (iv.) of Hypothesis 2.1.
-\end{lem}
-
-\begin{proof}
-let $f=f_{m,y}$ be the scalar function of $x$ with two parameters $y\in\mathbb R$ and $\mu\in(0,1)$ defined by
-$$ f(x)= f_{m,y}(x) = \frac{1}{2} e^{-|x|} - \frac{\mu}{2}e^{-|x-y|} $$
-
-If $y=0$, then $f$ has no zero-crossings, since $f_{m,0}(x)=\frac{1-\mu}{2}e^{-|x|}$ is strictly positive.
-If $y$ is nonzero, then one can easily check the symmetry relation $f_{m,-y}(x)=f_{m,y}(-x)$.
-Since the number of zero-crossings are invariant with respect to a reflection about the vertical axis, we can assume without loss of generality $y>0$.
-
-Under this assumption, $f$ is strictly increasing on $(-\infty,0)$, and strictly decreasing on $(0,y)$. The behavior on $(y,\infty)$ is determined by the sign of $e^{-y}-m$. There are three cases:
-
-\begin{enumerate}
-\item if $y<\ln\frac{1}{m}$, then $f$ is decreasing on $(0,\infty)$, hence has no zero-crossings;
-\item if $y>\ln\frac{1}{m}$, then $f$ has a unique zero-crossing at $x=\frac{1}{2}(y-\ln(m))$;
-\item if $y=\ln\frac{1}{m}$, then $f$ vanishes on $(y,\infty)$, hence it has no zero-crossings.
-\end{enumerate}
-In each case, the number of zero-crossings does not exceed one.
-\end{proof}
-
-We have shown that the Laplace kernel satisfies Hypothesis 2.1; thus, we can construct a periodic traveling wave solution:
+The reader can easily verify that the Laplace kernel satisfies hypotheses (H1) - (H3). The proof that is also satisfies (H4) is left in the appendix. The periodic traveling waves are given by
 
@@
 and
-\begin{equation}\label{laplacew2}
-w_2(x) = \int_{x-\winva}^{\infty} \frac{1}{2} e^{-|y|} \,dy - \int_{x-\winvb}^{\infty} \frac{1-m}{2} e^{-|y|} \,dy
-\end{equation}
-with
-$$ w_1^{-1}(p) = \begin{cases} -\ln(2p) & p\leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases} $$
-
-The integrals in \eqref{laplacew2} can be computed using elementary methods to obtain
+%\begin{equation}\label{laplacew2}
+%w_2(x) = \begin{cases}
+%m - \frac{1}{2} e^{x - \alpha} + \frac{1-\m}{2} e^{x - \beta} & x < \beta \\
+%1 - \frac{1}{2} e^{x-\alpha} - \frac{1-\m}{2} e^{-(x-\beta)} & \beta \leq x \leq \alpha \\
+%\frac{1}{2} e^{-(x-\alpha)} - \frac{1-\m}{2} e^{-(x-\beta)} & x > \alpha
+%\end{cases}
+%\end{equation}
 \begin{equation}
 w_2(x) = \begin{cases}
-\frac{1}{2} e^x \left( e^{-w_1^{-1}(b)} -e^{-w_1^{-1}(a)} \right)  & x < w_1^{-1}(b) \\
-1 - \frac{1}{2} e^{x-w_1^{-1}(a)} - \frac{1}{2} e^{-(x-w_1^{-1}(b))} & w_1^{-1}(b) < x < w_1^{-1}(a) \\
-\frac{1}{2} e^{-x} \left(  e^{w_1^{-1}(a)} - e^{w_1^{-1}(b)} \right) & x > w_1^{-1}(a)
+m + C_1 e^x & x < \beta \\
+1 - C_2 e^x - C_3 e^{-x} & \beta < x < \alpha \\
+C_4 e^{-x} & \alpha < x 
+\end{cases} \end{equation}
+where $\alpha=w_1^{-1}(\a)$, $\beta=w_1^{-1}(\b)$, with
+$$ w_1^{-1}(p) = \begin{cases} -\ln(2p) & p\leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases} $$
+The constants $C_1,C_2,C_3$, and $C_4$ are continuous functions of the growth parameters, with $C_2,C_3,C_4\geq0$, and they are given by
+\newcommand{\Conecaseone}{\b(1-\m)-\a}
+\newcommand{\Conecasetwo}{\frac{1-\m-4\a(1-\b)}{4(1-\b)}}
+\newcommand{\Conecasethree}{- \frac{1-\b+\m(1-\a)}{4(1-\a)(1-\b)} }
+
+\begin{equation}
+C_1 = \begin{cases}
+\Conecaseone & \a,\b < \frac{1}{2} \\
+\Conecasetwo & \a<\frac{1}{2}<\b \\
+\Conecasethree & \frac{1}{2}<a,b
+\end{cases} \end{equation}
+
+\newcommand{\Ctwocaseone}{\a}
+\newcommand{\Ctwocasetwo}{\frac{1}{4(1-\a)}}
+
+\begin{equation}
+C_2 = \begin{cases}
+\Ctwocaseone & \a < \frac{1}{2} \\
+\Ctwocasetwo & \a > \frac{1}{2}
+\end{cases} \end{equation}
+
+\newcommand{\Cthreecaseone}{\frac{1-\m}{4\b}}
+\newcommand{\Cthreecasetwo}{(1-\m)(1-\b)}
+
+\begin{equation}
+C_3 = \begin{cases}
+\Cthreecaseone & \b < \frac{1}{2} \\
+\Cthreecasetwo & \b > \frac{1}{2}
+\end{cases} \end{equation}
+
+\newcommand{\Cfourcaseone}{\frac{\b-\a(1-m)}{4\a\b}}
+\newcommand{\Cfourcasetwo}{\frac{1-4\a(1-\m)(1-\b)}{4\a}}
+\newcommand{\Cfourcasethree}{1-\a-(1-\m)(1-\b)}
+
+\begin{equation}
+C_4 = \begin{cases}
+\Cfourcaseone & \a,\b < \frac{1}{2} \\
+\Cfourcasetwo & \a<\frac{1}{2}<\b \\
+\Cfourcasethree & \frac{1}{2}<a,b
+\end{cases} \end{equation}
+
+To find $c^*$, we can now condition on the values of $w_2(\alpha)$ and $w_2(\beta)$.
+% If $w_2(\alpha)=C_4e^{-\alpha}>a$, then we know $x_a>\alpha$, so that $C_4e^{-x_a}=C_4e^{-2c^*}=a$ implies $c^*=\frac{1}{2}\ln(\frac{C_4}{a})$.
+%
+%If $w_2(\alpha)<a$ and $w_2(\beta)>a$, then we solve the equation
+%
+%$$ 1 - C_2e^x - C_3e^{-x} = a $$
+%
+%Multiplying through by $e^x$ yields a quadratic in $e^x$:
+%
+%$$ e^x - C_2e^{2x} - C_3 = ae^x $$
+%
+%$$ C_2 e^{2x} + (a-1) e^x + C_3 = 0 $$
+%
+%$$ e^x = \frac{1-a \pm \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} $$
+%
+%Since $C_2,C_3$ are negative, we know the function is concave down on this piece.
+Therefore, we take the rightmost solution, since the curve must be increasing through this point since the solution is unique.
+%
+%$$ c^* = \frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} \right) $$
+%
+%In the final case where $w_2(\beta)<a$, we have
+%
+%$$ m + C_1 e^{x_a} = a $$
+%implies
+%$$ C_1e^{x_a} = a-m$$
+%$$ x_a = \ln \frac{a-m}{C_1} $$
+%$$ c^* = \frac{1}{2} \ln \frac{a-m}{C_1} $$
+%
+%Our general formula is thus
+%\begin{equation}
+%c^* = \begin{cases}
+%\frac{1}{2} \ln \left( \frac{C_4}{a} \right) & a<w_2(\alpha) \\
+%\frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} \right) & w_2(\alpha)<a<w_2(\beta) \\
+%\frac{1}{2} \ln \left( \frac{a-m}{C_1}\right) & a>w_2(\beta)
+%\end{cases}
+%\end{equation}
+%Equivalently,
+\begin{equation}
+c^* = \begin{cases}
+\frac{1}{2} \ln \left( \frac{C_4}{a} \right) & a<C_4e^{-\alpha} \\
+\frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} \right) & C_4e^{-\alpha}<a<m+C_1e^\alpha\\
+\frac{1}{2} \ln \left( \frac{a-m}{C_1}\right) & a>m+C_1e^\alpha
 \end{cases}
@@
 
-We can split into three cases:
+Since the form of $w_2(x)$, and thus of $c^*$, depends on the values of $\a$ and $\b$; thus we will split into three cases for further analysis.
 
-\begin{enumerate}
-\item $a<\frac{1}{2}$, $b<\frac{1}{2}$. Then
+%Let $c_1$ and $c_2$ denote the intermediate wave speeds measured at some threshold $0<h<m$.
+For this analysis we chose the threshold of $h=a$.
+Thus $c_1 = w_2^{-1}(a) - w_1^{-1}(a)=2c^*-\alpha$, and $c_2=2c^*+\alpha-c_1=2\alpha$.
+We can now define the relative fluctuation in wavespeed by
+%
+%$$ f = \frac{|c_1-c_2|}{c^*} = \frac{|2c^*-3\alpha|}{c^*} $$
+%
+%We can also consider
+%
+%$$ f^2 = \frac{(c_1-c_2)^2}{(c^*)^{2}} $$
+%
+%The derivative is
+%
+%$$ \frac{df^2}{da} = \frac{d}{da}(c_1-c_2)^2\frac{1}{(c^*)^2} $$
+%
+%$$ = 2(c_1-c_2)(\frac{dc_1}{da}-\frac{dc_2}{da})(c^*)^{-2} - 2(c_1-c_2)^2(c^*)^{-3} $$
+%
+%$$ = \frac{2(c_1-c_2)}{(c^*)^2}\left((\frac{dc_1}{da}-\frac{dc_2}{da}) - \frac{c_1-c_2}{c^*}\right) $$
+%
+%It follows that $f$ is differentiable with respect to all the parameters almost everywhere. We conjecture that
+%
+%$$ \frac{df}{da} \geq 0 , \quad \text{almost everywhere} $$
+%
+%We will first consider the case $a,b<\frac{1}{2}$, and $a<C_4e^{-\alpha}$. We then have $\alpha=-\ln(2a)$, $c^*=\frac{1}{2}\ln\frac{b-(1-m)a}{4a^2b}$ so that
+%
+%$$ f = \frac{|\ln\frac{b-(1-m)a}{4a^2b}+3\ln(2a)|}{\ln\frac{b-(1-m)a}{4a^2b}} $$
+%$$ = \frac{|\ln(2a(b-(1-m)a))-\ln(b)|}{\ln(b-(1-m)a)-\ln(4a^2b)}  $$
+
+\begin{enumerate}[{Case} 1.]
+
+\item $\a<\frac{1}{2}$, $\b<\frac{1}{2}$.
 \begin{equation}
 w_2(x) = \begin{cases}
-\frac{1}{2} e^x \left( e^{-w_1^{-1}(b)} -e^{-w_1^{-1}(a)} \right)  & x < w_1^{-1}(b) \\
-1 - \frac{1}{2} e^{x-w_1^{-1}(a)} - \frac{1}{2} e^{-(x-w_1^{-1}(b))} & w_1^{-1}(b) < x < w_1^{-1}(a) \\
-\frac{1}{2} e^{-x} \left(  e^{w_1^{-1}(a)} - e^{w_1^{-1}(b)} \right) & x > w_1^{-1}(a)
+\m + (\Conecaseone) e^x  & x < -\ln(2\b) \\
+1 - \Ctwocaseone e^x - \Cthreecaseone e^{-x} & -\ln(2\b) < x < -\ln(2\a) \\
+\Cfourcaseone e^{-x} & x > -\ln(2\a)
 \end{cases}
+\end{equation}
+
+We have $w_2(\alpha)=\frac{\b-\a(1-\m)}{2\b}$ and $w_2(\beta)=\m + \frac{\b(1-\m)-\a}{2\b}$. Thus,
+\begin{equation}
+c^* = \begin{cases}
+\frac{1}{2} \ln \left( \frac{\b-\a(1-\m)}{4\a^2\b} \right) & \a < \frac{\b-\a(1-\m)}{2\b} \\
+\frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - \frac{\a(1-m)}{b}}}{2\a} \right) & \frac{\b-\a(1-\m)}{2\b} < a < \frac{\b(1+\m)-\a}{2\b} \\
+\frac{1}{2} \ln \left( \frac{a-m}{\b(1-\m)-\a}\right) & a > \frac{\b(1+\m)-\a}{2\b}
+\end{cases}
+\end{equation}
+
+\item $\a<\frac{1}{2}$, $\b>\frac{1}{2}$.
+\begin{equation}
+w_2(x) = \begin{cases}
+\m + \Conecasetwo e^x  & x < \ln(2-2\b) \\
+1 - \Ctwocaseone e^x - \Cthreecasetwo e^{-x} & \ln(2-2\b) < x < -\ln(2\a) \\
+\Cfourcasetwo e^{-x} & x > -\ln(2\a)
+\end{cases}
+\end{equation}
+
+We have $w_2(\alpha)=\frac{1-4\a(1-\m)(1-\b)}{2}$ and $w_2(\beta)=\frac{1+\m-4\a(1-\b)}{2}$. Thus,
+\begin{equation}
+c^* = \begin{cases}
+\frac{1}{2} \ln \left( \frac{1-4\a(1-\m)(1-\b)}{4\a^2} \right) & a<\frac{1-4\a(1-\m)(1-\b)}{2} \\
+\frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4a(1-\m)(1-\b)}}{2a} \right) & \frac{1-4\a(1-\m)(1-\b)}{2}<a<\frac{1+\m-4\a(1-\b)}{2} \\
+\frac{1}{2} \ln \left( \frac{4(a-m)(1-b)}{1-\m-4\a(1-\b)}\right) & a>\frac{1+\m-4\a(1-\b)}{2}
+\end{cases}
+\end{equation}
+
+\item $\a>\frac{1}{2}$, $\b>\frac{1}{2}$.
+\begin{equation}
+w_2(x) = \begin{cases}
+\m \Conecasethree e^x  & x < \ln(2-2\b) \\
+1 - \Ctwocasetwo e^x - \Cthreecasetwo e^{-x} & \ln(2-2\b) < x < \ln(2-2\a) \\
+(\Cfourcasethree) e^{-x} & x > \ln(2-2\a)
+\end{cases}
+\end{equation}
+
+Thus, $w_2(\alpha)=\frac{1-\a-(1-\m)(1-\b)}{2(1-a)}$ and $w_2(\beta)=\m - \frac{1-\b+\m(1-\a)}{2(1-\a)}$
+
+\begin{equation}
+c^* = \begin{cases}
+\frac{1}{2} \ln \left( \frac{1-\a-(1-\m)(1-\b)}{a} \right) & a<\frac{1-\a-(1-\m)(1-\b)}{2(1-a)} \\
+\frac{1}{2} \ln \Big( 2(1-a)\left[1-a + \sqrt{\frac{(1-a)^3-(1-\m)(1-\b) }{1-\a}}\right] \Big) & \frac{1-\a-(1-\m)(1-\b)}{2(1-a)}<a<\frac{\b-1+\m(1-\a)}{2(1-\a)} \\
+\frac{1}{2} \ln \left( \frac{4(m-a)(1-\a)(1-\b)}{1-\b+\m(1-\a)}\right) & a>\frac{\b-1+\m(1-\a)}{2(1-\a)}
+\end{cases}
+\end{equation}
+
 \end{enumerate}
 
-Then
-$$ w_2(x) = \begin{cases}
-\int_{-\infty}^{-\log(2b)} \frac{m}{2}e^{-|x-y|}\,dy + \int_{-\log(2b)}^{-\log(2a)} \frac{1}{2}e^{-|x-y|} \,dy & a<\frac{1}{2}, b < \frac{1}{2} \\
-\int_{-\infty}^{\log(2-2b)} \frac{m}{2}e^{-|x-y|} \,dy + \int_{\log(2-2b)}^{-\log(2a)} \frac{1}{2}e^{-|x-y|} \,dy & a<\frac{1}{2}, b \geq \frac{1}{2} \\ 
-\int_{-\infty}^{\log(2-2b)} \frac{m}{2}e^{-|x-y|} \,dy + \int_{\log(2-2b)}^{\log(2-2a)} \frac{1}{2}e^{-|x-y|} \,dy & a\geq\frac{1}{2}, b \geq \frac{1}{2} \\
-\end{cases} $$
-Now make the substitution $y'=x-y$.
-$$ w_2(x) = \begin{cases}
-\int_{x+\log(2b)}^{\infty} \frac{m}{2}e^{-|y'|}\,dy' + \int_{x+\log(2b)}^{x+\log(2a)} \frac{1}{2}e^{-|y'|} \,dy' & a<\frac{1}{2}, b < \frac{1}{2} \\
-\int_{x-\log(2-2b)}^{\infty} \frac{m}{2}e^{-|y'|} \,dy' + \int_{x-\log(2-2b)}^{x+\log(2a)} \frac{1}{2}e^{-|y'|} \,dy' & a<\frac{1}{2}, b \geq \frac{1}{2} \\ 
-\int_{x-\log(2-2b)}^{\infty} \frac{m}{2}e^{-|y'|} \,dy' + \int_{x-\log(2-2b)}^{x-\log(2-2a)} \frac{1}{2}e^{-|y'|} \,dy' & a\geq\frac{1}{2}, b \geq \frac{1}{2} \\
-\end{cases} $$
-
-Conversely, we may define $\sigma_p=\text{sign}(p-\frac{1}{2})$. Then, we have $w_1^{-1}(p)=\sigma_p\log(\sigma_p(2p+1)+1)$. The above equation then simplifies to
-\begin{equation}
-w_2(x) = \int_{-\infty}^{\sigma_a\log(\sigma_a(2a+1)+1)} mk(x-y)\,dy + \int_{\sigma_b\log(\sigma_b(2p+1)+1)}^{\sigma_a\log(\sigma_a(2a+1)+1)} k(x-y)\,dy
-\end{equation}
-
-We will now split into further cases.
-
-Case 1: $a<b<\frac{1}{2}$. Then
-$$ w_2(x) = \int_{x-\log(2b)}^{\infty} \frac{m}{2}e^{-|y|}\,dy + \int_{x-\log(2b)}^{x-\log(2a)} \frac{1}{2}e^{-|y|} \,dy $$
-We can expand this out using $\min$ and $\max$ functions. Let $x_a=x-\log(2a)$ and $x_b=x-\log(2b)$. Then
-$$ w_2(x) = \int_{\min(x_b,0)}^0 \frac{m}{2} e^y \, dy + \int_{\max(x_b,0)}^{\infty} \frac{m}{2} e^{-y} \, dy
-+ \int_{\min(x_b,0)}^{\min(x_a,0)} \frac{1}{2} e^y \, dy + \int_{\max(x_b,0)}^{\max(x_a,0)} \frac{1}{2} e^{-y} \, dy $$
-We can now take the integral:
-$$ \frac{m}{2} - \frac{m}{2} e^{\min(x_b,0)} - \frac{m}{2} e^{-\max(x_b,0)} + \frac{1}{2} e^{\min(x_a,0)} - \frac{1}{2} e^{\min(x_b,0)} - \frac{1}{2} e^{-\max(x_a,0)} + \frac{1}{2} e^{-\max(x_b,0)} $$
-This is equal to
-$$ \frac{m}{2} - \frac{m}{2} \min(e^{x_b},1) - \frac{m}{2} \min(e^{-x_b},1) + \frac{1}{2} \min(e^{x_a},1) - \frac{1}{2} \min(e^{x_b},1) - \frac{1}{2} \min(e^{-x_a},1) + \frac{1}{2} \min(e^{-x_b},1) $$
-$$ = \frac{m}{2} - \frac{m+1}{2} \min(e^{x_b},1) - \frac{m+1}{2} \min(e^{-x_b},1) - \frac{1}{2} \min(e^{x_a},1) - \frac{1}{2} \min(e^{-x_a},1)$$
-$$ = \frac{m}{2} - \frac{m+1}{2}\left( \min(e^{x_b},1) - \min(e^{-x_b},1) \right) - \frac{1}{2} \left( \min(e^{x_a},1) - \min(e^{-x_a},1) \right) $$
-
-$$ = \frac{m}{2} - \frac{m+1}{2}\left( \min(2be^{-x},1) - \min(\frac{1}{2b}e^{x},1) \right) - \frac{1}{2} \left( \min(2ae^{-x},1) - \min(\frac{1}{2a}e^{x},1) \right) $$
-
-It can be written in three cases
-
-$$ w_2(x) = \begin{cases} \displaystyle
-m - \frac{am+a-b}{4ab} e^x & x <\log(2a) \\
-\displaystyle
-m + 1 - \frac{m+1}{4b} e^x - ae^{-x} & \log(2a) \leq x \leq \log(2b) \\
-\displaystyle
-(mb+b-a) e^{-x}  & x > \log(2b)
-\end{cases} $$
-
-Since $w_2$ is increasing for $x<\log(2a)$, we know the solution to $w_2(x)=a$ must lie on the second or third pieces.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%They are given explicitly by
+%
+%\renewcommand{\Conecaseone}{\b\m'-\a}
+%\renewcommand{\Conecasetwo}{\frac{\m'-4\a\b'}{4\b'}}
+%\renewcommand{\Conecasethree}{- \frac{\b'+\m\a'}{4\a'\b'} }
+%
+%\begin{equation}
+%C_1 = \begin{cases}
+%\Conecaseone & \a,\b < \frac{1}{2} \\
+%\Conecasetwo & \a<\frac{1}{2}<\b \\
+%\Conecasethree & \frac{1}{2}<a,b
+%\end{cases} \end{equation}
+%
+%\renewcommand{\Ctwocaseone}{\a}
+%\renewcommand{\Ctwocasetwo}{\frac{1}{4\a'}}
+%
+%\begin{equation}
+%C_2 = \begin{cases}
+%\Ctwocaseone & \a < \frac{1}{2} \\
+%\Ctwocasetwo & \a > \frac{1}{2}
+%\end{cases} \end{equation}
+%
+%\renewcommand{\Cthreecaseone}{\frac{\m'}{4\b}}
+%\renewcommand{\Cthreecasetwo}{\m'\b'}
+%
+%\begin{equation}
+%C_3 = \begin{cases}
+%\Cthreecaseone & \b < \frac{1}{2} \\
+%\Cthreecasetwo & \b > \frac{1}{2}
+%\end{cases} \end{equation}
+%
+%\renewcommand{\Cfourcaseone}{\frac{\b-\a\m'}{4\a\b}}
+%\renewcommand{\Cfourcasetwo}{\frac{1-4\a\m'\b'}{4\a}}
+%\renewcommand{\Cfourcasethree}{\a'-\m'\b'}
+%
+%\begin{equation}
+%C_4 = \begin{cases}
+%\Cfourcaseone & \a,\b < \frac{1}{2} \\
+%\Cfourcasetwo & \a<\frac{1}{2}<\b \\
+%\Cfourcasethree & \frac{1}{2}<a,b
+%\end{cases} \end{equation}
+%
+%To find $c^*$, we can now condition on the values of $w_2(\alpha)$ and $w_2(\beta)$.
+% If $w_2(\alpha)=C_4e^{-\alpha}>a$, then we know $x_a>\alpha$, so that $C_4e^{-x_a}=C_4e^{-2c^*}=a$ implies $c^*=\frac{1}{2}\ln(\frac{C_4}{a})$.
+%
+%If $w_2(\alpha)<a$ and $w_2(\beta)>a$, then we solve the equation
+%
+%$$ 1 - C_2e^x - C_3e^{-x} = a $$
+%
+%Multiplying through by $e^x$ yields a quadratic in $e^x$:
+%
+%$$ e^x - C_2e^{2x} - C_3 = ae^x $$
+%
+%$$ C_2 e^{2x} + (a-1) e^x + C_3 = 0 $$
+%
+%$$ e^x = \frac{1-a \pm \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} $$
+%
+%Since $C_2,C_3$ are negative, we know the function is concave down on this piece.
+Therefore, we take the rightmost solution, since the curve must be increasing through this point since the solution is unique.
+%
+%$$ c^* = \frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} \right) $$
+%
+%In the final case where $w_2(\beta)<a$, we have
+%
+%$$ m + C_1 e^{x_a} = a $$
+%implies
+%$$ C_1e^{x_a} = a-m$$
+%$$ x_a = \ln \frac{a-m}{C_1} $$
+%$$ c^* = \frac{1}{2} \ln \frac{a-m}{C_1} $$
+%
+%%Our general formula is thus
+%\begin{equation}
+%c^* = \begin{cases}
+%\frac{1}{2} \ln \left( \frac{C_4}{a} \right) & a<w_2(\alpha) \\
+%\frac{1}{2} \ln \left( \frac{\a' + \sqrt{\a'^2 - 4C_2C_3}}{2C_2} \right) & w_2(\alpha)<a<w_2(\beta) \\
+%\frac{1}{2} \ln \left( \frac{a-m}{C_1}\right) & a>w_2(\beta)
+%\end{cases}
+%\end{equation}
+%
+%Since the form of $w_2(x)$, and thus of $c^*$, depends on the values of $\a$ and $\b$; thus we will split into three cases for further analysis.
+%
+%\begin{enumerate}[{Case} 1.]
+%
+%\item $\a<\frac{1}{2}$, $\b<\frac{1}{2}$.
+%\begin{equation}
+%w_2(x) = \begin{cases}
+%\m + (\Conecaseone) e^x  & x < -\ln(2\b) \\
+%1 - \Ctwocaseone e^x - \Cthreecaseone e^{-x} & -\ln(2\b) < x < -\ln(2\a) \\
+%\Cfourcaseone e^{-x} & x > -\ln(2\a)
+%\end{cases}
+%\end{equation}
+%
+%We have $w_2(\alpha)=\frac{\b-\a\m'}{2\b}$ and $w_2(\beta)=\m + \frac{\b\m'-\a}{2\b}$. Thus,
+%\begin{equation}
+%c^* = \begin{cases}
+%\frac{1}{2} \ln \left( \frac{\b-\a\m'}{4\a^2\b} \right) & \a < \frac{\b-\a\m'}{2\b} \\
+%\frac{1}{2} \ln \left( \frac{\a'+ \sqrt{\a'^2 - \frac{\a\m'}{b}}}{2\a} \right) & \frac{\b-\a\m'}{2\b} < a < \m + \frac{\b\m'-\a}{2\b} \\
+%\frac{1}{2} \ln \left( \frac{a-m}{\b\m'-\a}\right) & a > \m + \frac{\b\m'-\a}{2\b}
+%\end{cases}
+%\end{equation}
+%
+%
+%\item $\a<\frac{1}{2}$, $\b>\frac{1}{2}$.
+%\begin{equation}
+%w_2(x) = \begin{cases}
+%\m + \Conecasetwo e^x  & x < \ln(2\b') \\
+%1 - \Ctwocaseone e^x - \Cthreecasetwo e^{-x} & \ln(2\b') < x < -\ln(2\a) \\
+%\Cfourcasetwo e^{-x} & x > -\ln(2\a)
+%\end{cases}
+%\end{equation}
+%
+%We have $w_2(\alpha)=\frac{1-4\a\b'\m'}{2}$ and $w_2(\beta)=\frac{1+\m-4\a\b'}{2}$. Thus,
+%\begin{equation}
+%c^* = \begin{cases}
+%\frac{1}{2} \ln \left( \frac{1-4\a\b'\m'}{4\a^2} \right) & a<\frac{1-4\a\b'\m'}{2} \\
+%\frac{1}{2} \ln \left( \frac{\a' + \sqrt{\a'^2 - 4\a\b'\m'}}{2\a} \right) & \frac{1-4\a\b'\m'}{2}<a<\frac{1+\m-4\a\b'}{2} \\
+%\frac{1}{2} \ln \left( \frac{4\b'(a-m))}{\m'-4\a\b'}\right) & a>\frac{1+\m-4\a\b'}{2}
+%\end{cases}
+%\end{equation}
+%
+%
+%\item $\a>\frac{1}{2}$, $\b>\frac{1}{2}$.
+%\begin{equation}
+%w_2(x) = \begin{cases}
+%\m \Conecasethree e^x  & x < \ln(2\b') \\
+%1 - \Ctwocasetwo e^x - \Cthreecasetwo e^{-x} & \ln(2\b') < x < \ln(2\a') \\
+%(\Cfourcasethree) e^{-x} & x > \ln(2\a')
+%\end{cases}
+%\end{equation}
+%
+%Thus, $w_2(\alpha)=\frac{\a'-\b'\m'}{2\a'}$ and $w_2(\beta)=\m - \frac{\b'+\a'\m}{2\a'}$
+%
+%\begin{equation}
+%c^* = \begin{cases}
+%\frac{1}{2} \ln \left( \frac{\a'-\b'\m'}{a} \right) & a<\frac{\a'-\b'\m'}{2\a'} \\
+%\frac{1}{2} \ln \left( 2\a'^2 + 2\a'\sqrt{\a'^2 - \frac{\b'\m'}{\a'}} \right) & \frac{\a'-\b'\m'}{2\a'}<a<\m - \frac{\b'+\a'\m}{2\a'} \\
+%\frac{1}{2} \ln \left( \frac{4\a'\b'(m-a)}{\b'+\a'\m}\right) & a>\m - \frac{\b'+\a'\m}{2\a'}
+%\end{cases}
+%\end{equation}
+%
+%\end{enumerate}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%Each of the preceding cases can be generalized as follows:
+%
+%\begin{equation}
+%w_2(x) = \begin{cases}
+%m + C_1 e^x & x < \beta \\
+%1 - C_2 e^x - C_3 e^{-x} & \beta < x < \alpha \\
+%C_4 e^{-x} & \alpha < x 
+%\end{cases} \end{equation}
+%with 
+%
+%Note that $C_2$ and $C_3$ are strictly negative. 
+%
+%To find $c^*$, we can now condition on the values of $w_2(\alpha)$ and $w_2(\beta)$.
+If $w_2(\alpha)=C_4e^{-\alpha}>a$, then we know $x_a>\alpha$, so that $C_4e^{-x_a}=C_4e^{-2c^*}=a$ implies $c^*=\frac{1}{2}\ln(\frac{C_4}{a})$.
+%
+%If $w_2(\alpha)<a$ and $w_2(\beta)>a$, then we solve the equation
+%
+%$$ 1 - C_2e^x - C_3e^{-x} = a $$
+%
+%Multiplying through by $e^x$ yields a quadratic in $e^x$:
+%
+%$$ e^x - C_2e^{2x} - C_3 = ae^x $$
+%
+%$$ C_2 e^{2x} + (a-1) e^x + C_3 = 0 $$
+%
+%$$ e^x = \frac{1-a \pm \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} $$
+%
+%Since $C_2,C_3$ are negative, we know the function is concave down on this piece.
+Therefore, we take the rightmost solution, since the curve must be increasing through this point since the solution is unique.
+%
+%$$ c^* = \frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} \right) $$
+%
+%In the final case where $w_2(\beta)<a$, we have
+%
+%$$ m + C_1 e^{x_a} = a $$
+%implies
+%$$ C_1e^{x_a} = a-m$$
+%$$ x_a = \ln \frac{a-m}{C_1} $$
+%$$ c^* = \frac{1}{2} \ln \frac{a-m}{C_1} $$
+%
+%Our general formula is thus
+%\begin{equation}
+%c^* = \begin{cases}
+%\frac{1}{2} \ln \left( \frac{C_4}{a} \right) & a<w_2(\alpha) \\
+%\frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} \right) & w_2(\alpha)<a<w_2(\beta) \\
+%\frac{1}{2} \ln \left( \frac{a-m}{C_1}\right) & a>w_2(\beta)
+%\end{cases}
+%\end{equation}
+%
+%Let $x_a=w_2^{-1}(a)$ (well-defined by Lemma 1.2). We can check which piece $x_a$ lies on by evaluating $w_2(x)$ at $x=\alpha$ and $x=\beta$.
+%
+%
+%Since $w_2$ is increasing for $x<\log(2a)$, we know the solution to $w_2(x)=a$ must lie on the second or third pieces.
 This can be determined by checking the sign of $w_2(\log(2b))-a$.
@@
 Otherwise, if the sign is negative, the solution occurs on the second piece as the solution to the equation
-
-$$ w_2(x)=a \iff m + 1 - \frac{m+1}{4b} e^x - ae^{-x} = a $$
-
-First let us group like terms and multiply by $4b$:
-
-$$ (m+1) e^x + (m + 1 - a) - 4abe^{-x} = 0 $$
-
-Using the substitution $y=e^x$, this equation becomes a quadratic in $y$:
-
-$$ (m+1) y^2 + (m + 1 - a) y - 4ab = 0 $$
-
-The solution is
-
-$$ y = \frac{a-m-1 \pm \sqrt{(m+1-a)^2 + 16ab(m+1)}}{2m+2}$$
-
-We know the global maximum of $w_2(x)$ lies somewhere in the open interval $(\log(2a),\log(2b))$, therefore we take the greater solution so that
-
-$$ c^* = \frac{1}{2} \log\left(  \frac{a-m-1 + \sqrt{(m+1-a)^2 + 16ab(m+1)}}{2m+2} \right) $$
-
-Then we can obtain the critical wave speed in two cases:
-$$ c^* = \begin{cases} \displaystyle
-\frac{1}{2} \log \left( \frac{mb+b-a}{a} \right) & m \geq \frac{2ab+a-b}{b} \\
-\displaystyle
- \frac{1}{2} \log\left(  \frac{a-m-1 + \sqrt{(m+1-a)^2 + 16ab(m+1)}}{2m+2} \right) & m < \frac{2ab+a-b}{b}
-\end{cases} $$
-
-Case 2: $a<\frac{1}{2}<b$. Then
-$$ w_2(x) = \int_{x+\log(2-2b)}^{\infty} \frac{m}{2}e^{-|y|}\,dy + \int_{x+\log(2-2b)}^{x-\log(2a)} \frac{1}{2}e^{-|y|} \,dy $$
-
-Then
-
-$$ w_2(x) = \frac{m}{2} - \frac{m+1}{2}\left( \min(\frac{e^{-x}}{2-2b},1) - \min((2-2b)e^{x},1) \right) - \frac{1}{2} \left( \min(2ae^{-x},1) - \min(\frac{1}{2a}e^{x},1) \right) $$
-
-so
-
-$$ w_2(x) = \begin{cases}
-\displaystyle
-m - \frac{4a(m+1)(1-b)-1}{4a} e^x & x <\log(2a) \\
-\displaystyle
-m+1 - (m+1)(a-b) e^x - ae^{-x} & \log(2a) \leq x \leq -\log(2-2b) \\
-\displaystyle
-\frac{m+1-4a(1-b)}{4(1-b)} e^{-x}  & x > -\log(2-2b)
-\end{cases} $$
+%
+%$$ w_2(x)=a \iff m + 1 - \frac{m+1}{4b} e^x - ae^{-x} = a $$
+%
+%First let us group like terms and multiply by $4b$:
+%
+%$$ (m+1) e^x + (m + 1 - a) - 4abe^{-x} = 0 $$
+%
+%Using the substitution $y=e^x$, this equation becomes a quadratic in $y$:
+%
+%$$ (m+1) y^2 + (m + 1 - a) y - 4ab = 0 $$
+%
+%The solution is
+%
+%$$ y = \frac{a-m-1 \pm \sqrt{(m+1-a)^2 + 16ab(m+1)}}{2m+2}$$
+%
+%We know the global maximum of $w_2(x)$ lies somewhere in the open interval $(\log(2a),\log(2b))$, therefore we take the greater solution so that
+%
+%$$ c^* = \frac{1}{2} \log\left(  \frac{a-m-1 + \sqrt{(m+1-a)^2 + 16ab(m+1)}}{2m+2} \right) $$
+%
+%Then we can obtain the critical wave speed in two cases:
+%$$ c^* = \begin{cases} \displaystyle
+%\frac{1}{2} \log \left( \frac{mb+b-a}{a} \right) & m \geq \frac{2ab+a-b}{b} \\
+%\displaystyle
+% \frac{1}{2} \log\left(  \frac{a-m-1 + \sqrt{(m+1-a)^2 + 16ab(m+1)}}{2m+2} \right) & m < \frac{2ab+a-b}{b}
+%\end{cases} $$
+%
+%Case 2: $a<\frac{1}{2}<b$. Then
+%$$ w_2(x) = \int_{x+\log(2-2b)}^{\infty} \frac{m}{2}e^{-|y|}\,dy + \int_{x+\log(2-2b)}^{x-\log(2a)} \frac{1}{2}e^{-|y|} \,dy $$
+%
+%Then
+%
+%$$ w_2(x) = \frac{m}{2} - \frac{m+1}{2}\left( \min(\frac{e^{-x}}{2-2b},1) - \min((2-2b)e^{x},1) \right) - \frac{1}{2} \left( \min(2ae^{-x},1) - \min(\frac{1}{2a}e^{x},1) \right) $$
+%
+%so
+%
+%$$ w_2(x) = \begin{cases}
+%\displaystyle
+%m - \frac{4a(m+1)(1-b)-1}{4a} e^x & x <\log(2a) \\
+%\displaystyle
+%m+1 - (m+1)(a-b) e^x - ae^{-x} & \log(2a) \leq x \leq -\log(2-2b) \\
+%\displaystyle
+%\frac{m+1-4a(1-b)}{4(1-b)} e^{-x}  & x > -\log(2-2b)
+%\end{cases} $$
 
@@
 $$ k(x) = \frac{1}{\sqrt{2\pi}} e^{-\frac{x^2}{2}} $$
-$k$ is symmetric, strictly increasing on $(-\infty,0)$ and strictly decreasing on $(0,\infty)$, hence conditions i.-iii.
-of Hypothesis \ref{hypothesis1} are satisfied.
-For condition iv., let $y \in \mathbb R$ and $\mu\in(0,1)$.
-It can be shown that $k(x) - \mu k(x-y) = B(x)(1-Ce^{-xy})$ where $B(x)$ is a strictly positive function of $x$, and $C>0$.
-This quantity decreases monotonically from $1$ to $-\infty$ with a unique zero-crossing at $x=\frac{y}{2}-\frac{\ln \mu}{y}$.
-Thus, Hypothesis \ref{hypothesis1} is satisfied.
+The kernel is symmetric and has connected support, hence it satisfies hypotheses (H1)-(H3); the proof for hypothesis (H4) is left in the appendix.
 
+Let $\Phi(x)=\int_{-\infty}^{x}k(y)\,dy$ denote the cumulative density function of the standard normal distribution, and $\Phi^{-1}$ be its inverse.
 The periodic traveling wave solutions $w_1(x)$ and $w_2(x)$ are given by
 \begin{equation}
-w_1(x) = \frac{1}{2} - \frac{1}{2}\erf\left(\frac{x}{\sqrt{2}}\right)
+w_1(x) = \Phi(-x)
 \end{equation}
@@
 \begin{equation}
-w_2(x)=  \frac{m}{2} + \frac{1-m}{2} \erf \left( \frac{x-\beta}{\sqrt 2}\right) - \frac{1}{2} \erf \left( \frac{x-\alpha}{\sqrt2} \right)
+w_2(x)=  m - \Phi(x-\Phi^{-1}(a)) + (1-m)\Phi(x-\Phi^{-1}(b))
 \end{equation}
-where $\alpha=\sqrt{2}\erf^{-1}\left(1-2a\right)$, and $\beta=\sqrt{2}\erf^{-1}\left(1-2b\right)$, and $\erf$ is the error function defined by $\erf(x) =\frac{2}{\sqrt\pi}\int_0^x e^{-y^2}\,dy$.
+where $\alpha=\Phi^{-1}(a)$ and $\beta=\Phi^{-1}(b)$.
 
@@
 Then $w_1$ is given by
-\begin{equation}  \label{w1}
+\begin{equation}  \label{uniformw1}
 \begin{aligned}
@@
 with inverse $w_1^{-1}(p)=1-2p$ for $0<p<1$. Let $\alpha=1-2a$ and $\beta=1-2b$. Then
-\begin{equation} \label{w2}
+\begin{equation} \label{uniformw2}
 \begin{aligned}
@@
 
-\end{document}
+\appendix
+
+\section{Example calculations}
+
+\begin{lem}
+The Laplace kernel \eqref{laplacekernel} satisfies hypothesis (H4).
+\end{lem}
+
+\begin{proof}
+let $f=f_{m,y}$ be the scalar function of $x$ with two parameters $y\in\mathbb R$ and $\mu\in(0,1)$ defined by
+$$ f(x)= f_{m,y}(x) = \frac{1}{2} e^{-|x|} - \frac{\mu}{2}e^{-|x-y|} $$
+
+If $y=0$, then $f$ has no zero-crossings, since $f_{m,0}(x)=\frac{1-\mu}{2}e^{-|x|}$ is strictly positive.
+If $y$ is nonzero, then one can easily check the symmetry relation $f_{m,-y}(x)=f_{m,y}(-x)$.
+Since the number of zero-crossings are invariant with respect to a reflection about the vertical axis, we can assume without loss of generality $y>0$.
+
+Under this assumption, $f$ is strictly increasing on $(-\infty,0)$, and strictly decreasing on $(0,y)$. The behavior on $(y,\infty)$ is determined by the sign of $e^{-y}-m$. There are three cases:
+
+\begin{enumerate}
+\item if $y<\ln\frac{1}{m}$, then $f$ is decreasing on $(0,\infty)$, hence has no zero-crossings;
+\item if $y>\ln\frac{1}{m}$, then $f$ has a unique zero-crossing at $x=\frac{1}{2}(y-\ln(m))$;
+\item if $y=\ln\frac{1}{m}$, then $f$ vanishes on $(y,\infty)$, hence it has no zero-crossings.
+\end{enumerate}
+In each case, the number of zero-crossings does not exceed one.
+\end{proof}
+
+\begin{lem}
+If $k(x)$ is given by the Laplace kernel, then $w_1$ and $w_2$ form a periodic traveling wave solution if $C_1\leq 0$, or if $C_1>0$ and $w_2\left(\ln\sqrt\frac{C_3}{C_2}\right)\leq b$.
+\end{lem}
+
+\begin{proof}
+We can proceed in cases.
+If $C_1\leq 0$, then $w_2(x)$ is monotone decreasing, hence $w_2(x)<w_2(-\infty)=m<b$ everywhere.
+Otherwise, if $C_1>0$, then $w_2(x)$ is increasing on $(-\infty,\beta)$ and decreasing on $(\alpha,\infty)$.
+Since $w_2(x)$ is concave-down on $(\beta,\alpha)$, this implies there is a unique global maximum somewhere in this interval.
+To find it, we can differentiate:
+$$ \frac{dw_2}{dx}\Big|_{\beta<x<\alpha}=C_3e^{-x}-C_2e^x $$
+Setting this expression equal to zero and multiplying by $e^x$, we obtain $C_3-C_2e^{2x}=0$, which has a unique solution at $x=\ln\sqrt\frac{C_3}{C_2}$.
+\end{proof}
+
+\begin{lem}
+The Gaussian kernel satisfies hypothesis H4.
+\end{lem}
+
+\begin{proof}
+Let $y\in\mathbb R$ and $\mu\in(0,1)$. Then
+\begin{equation} \begin{aligned}
+k(x)-\mu k(x-y) &= \frac{1}{\sqrt{2\pi}} \left( e^{-\frac{x^2}{2}} - \mu e^{-\frac{-(x-y)^2}{2}} \right) \\
+&= \frac{1}{\sqrt{2\pi}} e^{-\frac{x^2}{2}} \left( 1 - \mu e^{\frac{2xy-y^2}{2}} \right)
+\end{aligned} \end{equation}
+This expression has a unique zero at $x=\frac{y^2-2\ln(\mu)}{2y}$, so the number of zero-crossings is at most one.
+\end{proof}
+
+\begin{lem}
+For the Gaussian kernel, $w_2(x)$ has a unique local extrema which is a global maxium at $x=\frac{2\ln(1-m)}{\alpha-\beta}+\alpha+\beta$.
+\end{lem}
+
+\begin{proof}
+The derivative of $w_2(x)$ is given by
+$$ 
+\frac{dw_2}{dx} = -\frac{1}{\sqrt{2\pi}}e^{-\frac{(x-\alpha)^2}{2}} + \frac{1-m}{\sqrt{2\pi}}e^{-\frac{(x-\beta)^2}{2}}
+$$
+Setting this quantity equal to zero, we obtain the equation
+$$ 
+e^{-\frac{(x-\alpha)^2}{2}} = (1-m)e^{-\frac{(x-\beta)^2}{2}}
+$$
+Taking logarithm on both sides, and rearrange terms,
+$$ 
+(x-\beta)^2 = 2\ln(1-m) + (x-\alpha)^2
+$$
+Distributing both sides and cancelling the quadratic term, we get the solution
+$$
+x = \frac{2\ln(1-m)}{\alpha-\beta} + \alpha + \beta
+$$
+\end{proof}
 

### 2021-06-14 paper_draft3.tex
continued edits

@@
 
-\theoremstyle{definition}
+%\theoremstyle{definition}
 \newtheorem{thm}{Theorem}
@@
 \newtheorem{prop}[thm]{Proposition}
+\theoremstyle{definition}
 \newtheorem{rem}[thm]{Remark}
-\newtheorem{hyp}[thm]{Hypothesis}
 \newtheorem{ex}[thm]{Example}
@@
 
-Under these assumptions, the cumulative density function $F(x)=\int_{-\infty}^{x}k(y)\,dy$ has a well-defined right inverse $F^{-1}$ satisfying $F(F^{-1}(p))=p$ for all $0<p<1$.
+\begin{prop} \label{prop1}
+Let $\mathcal B$ denote the space of bounded, continuous, non-negative functions $\mathbb R \to \mathbb R$.
+$Q$ is a bounded nonlinear operator $\mathcal B \to \mathcal B$, and satisfies the following properties for all $u \in \mathcal B$:
+
+\begin{enumerate}[(i.)]
+\item \it{(Translation invariance)} $Q[T^t[u]]=T^t[Q[u]]$ for any translation operator $T^t[u](x)=u(x+t)$.
+\item \it{(Limit-preserving)} If $u(x)\to\ell$ as $x\to\infty$, then $Q[u](x)\to g(\ell)$ as $x\to\infty$; likewise as $x\to-\infty$.
+\item \it{(Symmetry-preserving)} If $u(x-a)=u(x+a)$ then $Q[u](x-a)=Q[u](x+a)$.
+\end{enumerate}
+\end{prop}
+
+ the cumulative density function $F(x)=\int_{-\infty}^{x}k(y)\,dy$ has a well-defined right inverse $F^{-1}$ satisfying $F(F^{-1}(p))=p$ for all $0<p<1$.
 Furthermore, it satisfies the symmetry relation $F(-x)=1-F(x)$.
@@
 \begin{equation} \label{w1}
-w_1(x) = \int_x^\infty k(y) \, dy
+w_1(x) := \int_x^\infty k(y) \, dy
 \end{equation}
@@
 \begin{equation} \label{w2}
-w_2(x) = \int_{-\infty}^{\infty} k(y) g(w_1(x-y)) \, dy 
+w_2(x) := Q[w_1](x) = \int_{-\infty}^{\infty} k(y) g(w_1(x-y)) \, dy 
 \end{equation}
@@
 It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$.
-Thus, composing $w_1(x)$ with the growth function $g$ yields
-\begin{equation} \label{gw1}
-g(w_1(x)) = \begin{cases}
-\mu & x < x_\beta \\
-1 & x_\beta \leq x \leq x_\a \\
-0 & x > x_\a
-\end{cases} \end{equation}
-
-Applying the convolution operator yields a formula for $w_2(x)$:
-\begin{equation} \label{w2calculation}
+Applying the integro-difference operator to $w_1$ yields
+\begin{equation} \label{qw1calculation}
 \begin{aligned}
-w_2(x) &= \int_{-\infty}^{\infty} k(y) g(w_1(x-y)) \, dy \\
-&= \int_{x-x_\a}^{x-x_\b} k(y)\,dy + \m \int_{x-\beta}^{\infty} k(y)\,dy \\
-&= \int_{x-x_\a}^{\infty} k(y)\,dy - (1-\m) \int_{x-x_\b}^{\infty} k(y)\,dy
-\end{aligned}
-\end{equation}
+Q[w_1](x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
+&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \int_{x_\b}^{x_\a} k(x-y) \, dy \\
+&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
+&= \int_{x-x_\a}^{\infty} k(y) \, dy - (1-\m) \int_{x-x_\b}^{\infty} k(y) \, dy
+\end{aligned} \end{equation}
 
@@
 
-It follows that $w_2(x)\geq\a$ for $x\leq 2c^*$ and $w_2(x)<\alpha$ for $x>2c^*$. Along with the assumption that $\sup_{x\in\mathbb R}w_2(x)\leq\b$, we can compose with $g$ as follows:
-\begin{equation} \label{gw2}
-g(w_2(x)) = \begin{cases}
-1 & x \leq 2c^* \\
-0 & x > 2c^*
-\end{cases} \end{equation}
-
-Taking convolution with $k$, we obtain
-\begin{equation}
-Q[w_2](x) = \int_{x-x_0}^{\infty} k(y)\,dy = w_1(x-2c^*).
-\end{equation}
+It follows that $w_2(x)\geq\a$ for $x\leq 2c^*$ and $w_2(x)<\alpha$ for $x>2c^*$.
+Along with the assumption that $\sup_{x\in\mathbb R}w_2(x)\leq\b$, we can apply the integro-difference operator once more:
+\begin{equation} \begin{aligned}
+Q[w_2](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_2(y)) \, dy \\
+&= \int_{-\infty}^{2c^*} k(x-y) \, dy \\
+&= \int_{x-2c^*}^{\infty} k(y) \, dy &= w_1(x-2c^*).
+\end{aligned} \end{equation}
 %By defining $c^* = \frac{1}{2}x_0$, and applying the integro-difference operator, we can see that $w_1$ and $w_2$ are both solutions to the periodic traveling wave equation with mean speed $c^*$:
@@
 \begin{equation} \label{ptw}
-W_n(x) = \begin{cases}
+u_n(x) = \begin{cases}
 w_1(x-nc^*) & n \text{ even} \\
@@
 \begin{proof}
-DO THIS
+It suffices to show that $u_{n+1}=Q[u_n]$ for all $n\geq 0$; this can be done via induction. The basis case is
+\begin{equation}
+u_1(x) = w_2(x) = Q[w_1](x) = Q[u_0](x)
+\end{equation}
+For the inductive step, suppose $u_{n+1}=Q[u_n]$ for some $n\geq 0$. We can proceed in cases. If $n$ is even, then $u_n(x)=w_1(x-nc^*)$ and $u_{n+1}(x)=w_2(x-nc^*)$; we have
+\begin{equation}
+u_{n+1}(x) = w_2(x-nc^*) = Q[w_1](x-nc^*) = Q[u_n](x)
+\end{equation}
+If $n$ is odd, then $u_n(x)=w_2(x-nc^*)$, and $u_{n+1}(x)=w_1(x-(n+1)c^*)$. By Lemma \ref{lemma1}, we have
+\begin{equation}
+u_{n+1}(x) = w_1(x-(n+1)c^*) = Q[w_2](x-nc^*) = Q[u_n](x)
+\end{equation}
+This completes the proof.
 \end{proof}
@@
 \begin{thm}  \label{theorem2}
-For all $\epsilon>0$, the sequence $(u_n)_{n=0}^{\infty}$ defined in Theorem \ref{theorem1} satisfies
+If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then for all $\epsilon>0$, the sequence \ref{ptw} satisfies
 \begin{equation}
@@
 
+\begin{proof}
+\begin{equation} \begin{aligned}
+\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n}(x)
+&= \lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}w_1(x-2nc^*) \\
+&= \lim_{n\to\infty}\inf_{x<-2n\epsilon}w_1(x) \\
+&= \liminf_{x\to-\infty}w_1(x) &= 1.
+\end{aligned} \end{equation}
+
+\begin{equation} \begin{aligned}
+\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n+1}(x)
+&= \lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}w_2(x-2nc^*) \\
+&= \lim_{n\to\infty}\inf_{x<-2n\epsilon}w_2(x) \\
+&= \liminf_{x\to-\infty}w_2(x) &= m.
+\end{aligned} \end{equation}
+
+\begin{equation} \begin{aligned}
+\lim_{n\to\infty} \sup_{x>n(c^*+\epsilon)} u_n(x) 
+&\leq \lim_{n\to\infty} \sup_{x>n(c^*+\epsilon)} \max\{w_1(x-nc^*),w_2(x-nc^*)\} \\
+&= \lim_{n\to\infty} \sup_{x>n\epsilon} \max\{w_1(x),w_2(x)\} \\
+&= \limsup_{x\to\infty} \max\{w_1(x),w_2(x)\} &= 0.
+\end{aligned} \end{equation}
+Since the left hand side must also be non-negative, equality follows.
+\end{proof}
+
 The next theorem concerns the spreading behavior of solutions to the IDE \eqref{q} with compactly supported initial data. We also assume the disperal kernel is compactly supported.
 
-\begin{thm} Suppose $||w_2||_\infty \leq b$ and $k(x)$ has compact support. Assume the following hold:
-
-\begin{enumerate}[i.)]
-\item $c^*$ is positive,\
-\item the initial condition $u_0$ has compact support;
-\item the set $A=\{x\in\mathbb R:a\leq u_0(x)\leq b\}$  is connected and sufficiently large.
-\end{enumerate}
- Then the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$, satisfies
-\begin{equation}
-\lim_{n\to\infty}\inf_{|x|<2nc}u_{2n}(x)=1, \quad \forall c\in(0,c^*)
+\begin{thm} Let $u_0(x)$ be a non-negative continuous function with compact support such that the set $A=\{x\in\mathbb R:\a\leq u_0(x)\leq \b\}$ is connected.
+Suppose $k(x)$ has compact support, $\sup_{x\in\mathbb R}w_2(x)\leq \b$, and $c^* > 0$.
+Then, for $A$ sufficiently large, the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$ spreads with speed $c^*$, i.e.,
+\begin{equation}
+\lim_{n\to\infty}\inf_{|x|<n(c^*-\epsilon)}u_{n}(x)>0,
 \end{equation}
@@
 \begin{equation}
-\lim_{n\to\infty}\inf_{|x|<2nc}u_{2n+1}(x)=m, \quad \forall c\in(0,c^*)
-\end{equation}
-and 
-\begin{equation}
-\lim_{n\to\infty}\sup_{|x|>nc}u_n(x)=0, \quad \forall c\in(c^*,\infty).
-\end{equation}
+\lim_{n\to\infty}\sup_{|x|>n(c^*+\epsilon)}u_n(x)=0.
+\end{equation}
+for all $\epsilon>0$.
 \end{thm}
@@
 \begin{proof}
+By the translation invariance property of $Q$, we may assume without loss of generality $A=[-r,r]$, for some $r>0$.
+It follows that $u_0(x)<\a$ for $|x|>r$ and $\a\leq u_0(x)\leq\b$ for $|x|$Furthermore, there exists $\sigma>0$ such that $k(x)>0$ if and only if $|x|<\sigma$.
+
 Let $(-\sigma,\sigma)$ be the support of $k$, for $0<\sigma<\infty$.
@@
 
-\section{Example calculations}
+\section{Appendix}
+
+\begin{proof}[Proof of Proposition \ref{prop1}]
+
+Let $u(x)$ be non-negative, continuous, and bounded.
+
+\begin{enumerate}[(i.)]
+\item For $t\in\mathbb R$, let $T^t$ denote the translation operator defined $T^t[u](x) = u(x+t)$. Then,
+\begin{equation} \begin{aligned}
+Q[T^t[u]](x) &= 
+\int_{-\infty}^{\infty} k(x-y) g(T^t[u](y)) \, dy \\
+&= \int_{-\infty}^{\infty} k(x-y) g(u(y+t)) \, dy
+\end{aligned} \end{equation}
+Let $z=y+t$.
+\begin{equation} \begin{aligned}
+Q[T^t[u]](x)
+&= \int_{-\infty}^{\infty} k(x-z+t) g(u(z)) \, dz \\
+&= Q[u](x+t) \\
+&= T^t[Q[u]](x)
+\end{aligned} \end{equation}
+
+\item 
+Suppose $\lim_{x\to\infty}u(x)=\ell$.
+
+\end{enumerate}
+
+\end{proof}
 

### 2021-06-20 paper_draft3.tex
workworkwork

@@
 \usepackage{hyperref}
-%\usepackage{geometry}
+\usepackage{geometry}
 \usepackage{graphicx}
@@
 \newtheorem{thm}{Theorem}
+\newtheorem{cor}{Corollary}
 \newtheorem{lem}[thm]{Lemma}
@@
 
-{\bf Todo:} Proof of Theorem 2.2.
+{\bf Todo:} Double check Gaussian kernel proof.
 \newline
@@
 
+%\begin{rem}
+%Hypotheses (H1)-(H4) are scale-invariant, that is, if $k(x)$ satisfies (H1)-(H4), then so does $\hat{k}(x):=ak(ax)$ for any $a>0$.
+Thus, when checking the hypotheses for a particular dispersal kernel, we may rescale without loss of generality.
+%\end{rem}
+
 \begin{prop} \label{prop1}
-Let $\mathcal B$ denote the space of bounded, continuous, non-negative functions $\mathbb R \to \mathbb R$.
+%Let $\mathcal B$ denote the space of bounded, continuous, non-negative functions $\mathbb R \to \mathbb R$.
 $Q$ is a bounded nonlinear operator $\mathcal B \to \mathcal B$, and satisfies the following properties for all $u \in \mathcal B$:
+The operator $Q$ satisfies the following properties for all bounded continuous functions $u : \mathbb R \to \mathbb R_{\geq 0}$:
 
@@
 \item \it{(Translation invariance)} $Q[T^t[u]]=T^t[Q[u]]$ for any translation operator $T^t[u](x)=u(x+t)$.
+\item \it{(Symmetric)} If $u(x)=u(-x)$ then $Q[u](x)=Q[u](-x)$.
 \item \it{(Limit-preserving)} If $u(x)\to\ell$ as $x\to\infty$, then $Q[u](x)\to g(\ell)$ as $x\to\infty$; likewise as $x\to-\infty$.
-\item \it{(Symmetry-preserving)} If $u(x-a)=u(x+a)$ then $Q[u](x-a)=Q[u](x+a)$.
 \end{enumerate}
@@
 
- the cumulative density function $F(x)=\int_{-\infty}^{x}k(y)\,dy$ has a well-defined right inverse $F^{-1}$ satisfying $F(F^{-1}(p))=p$ for all $0<p<1$.
-Furthermore, it satisfies the symmetry relation $F(-x)=1-F(x)$.
-
- Let $w_1$ and $w_2$ be two functions belonging to $C(\mathbb R)$ defined by
+ Let $w_1$ and $w_2$ be two functions defined by
 \begin{equation} \label{w1}
@@
 \begin{proof} Let $x_\a=\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}$.
-It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$.
+Since $w_1$ is monotone, it follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$.
 Applying the integro-difference operator to $w_1$ yields
@@
 
+By Lemma \ref{lemma1}, the wave functions $w_1(x)$ and $w_2(x)$ satisfy $Q^2[w_1](x)=w_1(x-2c^*)$ and $Q^2[w_2](x)=w_2(x-2c^*)$.
+As a result, they can be used to construct a solution to the integral recurrence which spreads in space with a mean speed of $c^*$ and alternates in shape every two time steps.
+This is formalized in the following theorem:
+
+%\begin{cor} If $||w_2||_\infty \leq \beta$, then for all $x\in\mathbb R$,
+%\begin{equation}
+%Q^2[w_1](x) = w_1(x-2c^*)
+%\end{equation}
+%and
+%\begin{equation}
+%Q^2[w_2](x) = w_2(x-2c^*)
+%\end{equation}
+%\end{cor}
+
 \begin{thm} \label{theorem1}
-If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then the recurrence \eqref{q} has a periodic traveling wave solution given by
+If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then the recurrence \eqref{q} has a periodic traveling wave solution $(u_n)_{n=0}^{\infty}$ satisfying
+%\begin{equation} \label{ptw}
+%u_n(x) = \begin{cases}
+%w_1(x-nc^*) & n \text{ even} \\
+%w_2(x-nc^*) & n \text{ odd}
+%\end{cases}
+%\end{equation}
+
 \begin{equation} \label{ptw}
-u_n(x) = \begin{cases}
-w_1(x-nc^*) & n \text{ even} \\
-w_2(x-nc^*) & n \text{ odd}
-\end{cases}
-\end{equation}
+\begin{aligned}
+u_{2n}(x) &= w_1(x-2nc^*) \\
+u_{2n+1}(x) &= w_2(x-2nc^*)
+\end{aligned}
+\end{equation}
+for all $n \geq 0$.
 \end{thm}
@@
 \begin{proof}
-It suffices to show that $u_{n+1}=Q[u_n]$ for all $n\geq 0$; this can be done via induction. The basis case is
-\begin{equation}
-u_1(x) = w_2(x) = Q[w_1](x) = Q[u_0](x)
-\end{equation}
-For the inductive step, suppose $u_{n+1}=Q[u_n]$ for some $n\geq 0$. We can proceed in cases. If $n$ is even, then $u_n(x)=w_1(x-nc^*)$ and $u_{n+1}(x)=w_2(x-nc^*)$; we have
-\begin{equation}
-u_{n+1}(x) = w_2(x-nc^*) = Q[w_1](x-nc^*) = Q[u_n](x)
-\end{equation}
-If $n$ is odd, then $u_n(x)=w_2(x-nc^*)$, and $u_{n+1}(x)=w_1(x-(n+1)c^*)$. By Lemma \ref{lemma1}, we have
-\begin{equation}
-u_{n+1}(x) = w_1(x-(n+1)c^*) = Q[w_2](x-nc^*) = Q[u_n](x)
-\end{equation}
-This completes the proof.
+It suffices to show that equation \eqref{ptw} satisfies $u_{n+1}=Q[u_n]$ for all $n \geq 0$.
+For convenience, we will switch the index and consider the cases $u_{2n}$ and $u_{2n+1}$ separately.
+The basic case, $u_1 = Q[u_0]$, follows immediately from definition \ref{w2}.
+This proves the first half.
+Next, we have $u_2(x)=w_1(x-2c^*)$, which follows by Lemma \ref{lemma1}.
+
+For the inductive step, suppose $u_{2n+1}=Q[u_{2n}]$ and $u_{2n+2}=Q[u_{2n+1}]$ for some $n\geq 0$. We only need to show $u_{2n+3}=Q[u_{2n+2}]$. We have
+\begin{equation} \begin{aligned}
+u_{2n+3}(x) &= w_2(x-2nc^*-2c^*) \\
+&= Q^2[w_2](x-2nc^*) \\
+&= Q^2[u_{2n+1}](x) \\ 
+&= Q[u_{2n+2}](x)
+\end{aligned} \end{equation}
 \end{proof}
@@
 &= \lim_{n\to\infty}\inf_{x<-2n\epsilon}w_1(x) \\
-&= \liminf_{x\to-\infty}w_1(x) &= 1.
+&= \liminf_{x\to-\infty}w_1(x) \\ &= 1.
 \end{aligned} \end{equation}
@@
 &= \lim_{n\to\infty}\inf_{x<-2n\epsilon}w_2(x) \\
-&= \liminf_{x\to-\infty}w_2(x) &= m.
+&= \liminf_{x\to-\infty}w_2(x) \\ &= m.
 \end{aligned} \end{equation}
@@
 &= \lim_{n\to\infty} \sup_{x>n\epsilon} \max\{w_1(x),w_2(x)\} \\
-&= \limsup_{x\to\infty} \max\{w_1(x),w_2(x)\} &= 0.
+&= \limsup_{x\to\infty} \max\{w_1(x),w_2(x)\} \\ 
+&= \max\{\limsup_{x\to\infty} w_1(x),\limsup_{x\to\infty} w_2(x)\} \\
+&= 0.
 \end{aligned} \end{equation}
-Since the left hand side must also be non-negative, equality follows.
+In the last calculation, the left hand side is known to be non-negative; therefore the limit is exactly equal to zero.
 \end{proof}
 
-The next theorem concerns the spreading behavior of solutions to the IDE \eqref{q} with compactly supported initial data. We also assume the disperal kernel is compactly supported.
+The next theorem concerns the spreading behavior of solutions to the IDE \eqref{q} with compactly supported initial data.
+We also assume the disperal kernel is compactly supported.
+First, we introduce a useful lemma for compactly supported kernels.
+
+\begin{lem}\label{lemma2}
+Suppose $k(x)$ is compactly supported on $[-\sigma,\sigma]$, for some $\sigma>0$.
+Then for any continuous function $u(x)$, if $u(x)=0$ for $x \in \Omega \subseteq \mathbb R$, then $(k*u)(x)=0$ for $x\in\Omega$ such that $d(x,\mathbb R\setminus\Omega) \geq \sigma$, where $d(x,\mathbb R\setminus\Omega):= \inf \{d(x,y) \mid y\in \mathbb R\setminus\Omega\}$.
+\end{lem}
+
+\begin{proof}
+Let $x\in\Omega$ such that $d(x,\mathbb R\setminus\Omega) \geq \sigma$.
+Then $(x-\sigma,x+\sigma)$ is a subset of  $\Omega$ on which $u$ vanishes; thus $ (k*u)(x) = \int_{x-\sigma}^{x+\sigma}k(x-y)u(y)\,dy = 0.$
+\end{proof}
 
@@
 Suppose $k(x)$ has compact support, $\sup_{x\in\mathbb R}w_2(x)\leq \b$, and $c^* > 0$.
-Then, for $A$ sufficiently large, the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$ spreads with speed $c^*$, i.e.,
+For $A$ sufficiently large, the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$ spreads with speed $c^*$, i.e.
 \begin{equation}
@@
 By the translation invariance property of $Q$, we may assume without loss of generality $A=[-r,r]$, for some $r>0$.
-It follows that $u_0(x)<\a$ for $|x|>r$ and $\a\leq u_0(x)\leq\b$ for $|x|$Furthermore, there exists $\sigma>0$ such that $k(x)>0$ if and only if $|x|<\sigma$.
-
-Let $(-\sigma,\sigma)$ be the support of $k$, for $0<\sigma<\infty$.
-Since $A$ is connected, we may also assume by the translation invariance property that $A=[-r,r]$ for some $r \geq 0$.
-Furthermore, since $u_0$ has compact support we must have $u_0(x)=0$ outside a bounded interval $(r^-,r^+) \supset A$, where $r^- < -r \leq r < r^+$.
-
-Next, we will show that $0<u_0(x)<a$ for $x\in(r^-,r^+)\setminus A$.
-If we suppose to the contrary that $u_0(x)>b$ for some $x$ in this set, then suppose without loss of generality $x\in(r,r^+)$ such that $u_0(x)>b$.
-It follows by the intermediate value theorem that $u_0(x')=b$ for some $x' \in (x,r^+)$.
-But then $r\in A$, $x\notin A$, and $x'\in A$ with $r<x<x'$, violating the connectedness of $A$.
-
-The preceding argument shows
-\begin{equation}
-g(u_0(x)) = \begin{cases}
-1 & |x| < r \\
-0 & |x| \geq r
-\end{cases}
-\end{equation}
-
-To prove the theorem, we will show the spreading property is satisfied for all $r\geq2\sigma$. From $r\geq \sigma$ it follows,
-\begin{equation}
-u_1(x) = w_1(|x|-r)
-\end{equation}
-Then,
+It follows that $u_0(x)<\a$ for $|x|>r$ and $\a\leq u_0(x)\leq\b$ for $|x| \leq r$.
+Furthermore, there exists $\sigma>0$ such that $k(x)>0$ if and only if $|x|<\sigma$.
+
+Assuming $r \geq \frac{\sigma}{2}$, we have
+\begin{equation} \begin{aligned}
+u_1(x) = Q[u_0](x) &= \int_{-r}^{r} k(x-y) \, dy \\
+&= \begin{cases}
+w_1(x-r) & x \geq 0 \\
+w_1(-x+r) & x< 0
+\end{cases}
+\end{aligned}  \end{equation}
+
+Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. Then, applying the growth function, we have
 \begin{equation} g(u_1(x)) = \begin{cases}
-m & |x|<r+\beta \\
-1 & r+\beta\leq |x|\leq r+\alpha \\
-0 & |x|>r+\alpha
-\end{cases}
-\end{equation}
-where $\alpha$ and $\beta$ are defined as in Lemma \ref{lemma1}, and satisfy $-\sigma<\beta<\alpha<\sigma$.
-Note that $g(u_1(x))=g(Q[w](x))$ for all $x>-r-\beta$.
-Thus, $r\geq 2\sigma$ guarantees $r+\beta\geq\sigma$.
-It follows that
-\begin{equation}
-u_2(x) = Q[w_1](|x|-r) = w_2(|x|-r)
-\end{equation}
-Applying $g$, we get
+0 & x<-r-x_\a \\
+1 & -r-x_\a \leq x \leq -r-x_\b \\
+m & -r-x_\b < x < r+x_\b \\
+1 & r+x_\b \leq x \leq r+x_\a \\
+0 & x > r+x_\a
+\end{cases}
+\end{equation}
+Note that $g(u_1(x))=g(w_1(x))$ for all $x >-r-x_\b$.
+Thus, by Lemma \ref{lemma2}, $Q[u_1](x)=(k*(g\circ u_1))(x)=(k*(g\circ w_1))(x)=Q[w_1](x)$ for all $x>-r-x_\b+\sigma$.
+If we assume $r \geq x_\b+\sigma$, then $u_2(x)=Q[u_1](x)=Q[w_1](x-r)=w_2(x-r)$ for $x>0$.
+
+By symmetry of the integro-difference operator, $Q[u_1](x) = Q[w_1](-x+r)$ for $x<0$. Thus,
+
+\begin{equation}
+u_2(x) = Q[u_1](x) \begin{cases}
+w_2(x-r) & x \geq 0 \\
+w_2(-x+r) & x < 0 
+\end{cases}
+\end{equation}
+Since $c^*\geq 0$, we have
 \begin{equation}
 g(u_2(x)) = \begin{cases}
-1 & |x| \leq  r+2c^* \\
-0 & |x| >  r+2c^*
-\end{cases}
-\end{equation}
-Since $c^*>0$ we have $r+2c^*>r\geq\alpha$, so
-\begin{equation}
-u_3(x) = w_1(|x|-r-2c^*)
+0 & x < -r-2c^* \\
+1 & -r-2c^* \leq x \leq r+2c^* \\
+0 & x > r+2c^* 
+\end{cases}
+\end{equation}
+
+Thus,
+\begin{equation}
+u_3(x) = Q[u_2](x) = \begin{cases}
+w_1(x-r-2c^*) & x \geq 0 \\
+w_1(-x+r+2c^*) & x < 0 
+\end{cases}
 \end{equation}
@@
 %\end{equation}
-\begin{equation}
+\begin{equation} \label{w2laplace}
 w_2(x) = \begin{cases}
-m + C_1 e^x & x < \beta \\
-1 - C_2 e^x - C_3 e^{-x} & \beta < x < \alpha \\
-C_4 e^{-x} & \alpha < x 
+m + C_1 e^x & x < x_\b \\
+1 - C_2 e^x - C_3 e^{-x} & x_\b \leq x \leq x_\a \\
+C_4 e^{-x} & x_\a < x 
 \end{cases} \end{equation}
-where $\alpha=w_1^{-1}(\a)$, $\beta=w_1^{-1}(\b)$, with
-$$ w_1^{-1}(p) = \begin{cases} -\ln(2p) & p\leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases} $$
-The constants $C_1,C_2,C_3$, and $C_4$ are continuous functions of the growth parameters, with $C_2,C_3,C_4\geq0$, and they are given by
+where
+\begin{equation}
+x_\a = \begin{cases} -\ln(2\a) & \a\leq \frac{1}{2} \\ \ln(2-2\a) & \a > \frac{1}{2} \end{cases} \quad
+x_\b = \begin{cases} -\ln(2\b) & \b\leq \frac{1}{2} \\ \ln(2-2\b) & \b > \frac{1}{2} \end{cases} 
+\end{equation}
+%$x_\a=w_1^{-1}(\a)$, $x_\b=w_1^{-1}(\b)$, with
+%$$ w_1^{-1}(p) = \begin{cases} -\ln(2p) & p\leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases} $$
+The constants $C_1,C_2,C_3$, and $C_4$ are continuous functions of the growth parameters $\alpha$, $\beta$, and $\mu$, with $C_2,C_3,C_4\geq0$. They can be expressed as piecewise expressions:
 \newcommand{\Conecaseone}{\b(1-\m)-\a}
@@
 C_1 = \begin{cases}
-\Conecaseone & \a,\b < \frac{1}{2} \\
-\Conecasetwo & \a<\frac{1}{2}<\b \\
-\Conecasethree & \frac{1}{2}<a,b
+\Conecaseone & \a,\b \leq \frac{1}{2} \\
+\Conecasetwo & \a\leq\frac{1}{2}<\b \\
+\Conecasethree & \frac{1}{2}<\a,\b
 \end{cases} \end{equation}
@@
 C_2 = \begin{cases}
-\Ctwocaseone & \a < \frac{1}{2} \\
+\Ctwocaseone & \a \leq \frac{1}{2} \\
 \Ctwocasetwo & \a > \frac{1}{2}
@@
 C_3 = \begin{cases}
-\Cthreecaseone & \b < \frac{1}{2} \\
+\Cthreecaseone & \b \leq \frac{1}{2} \\
 \Cthreecasetwo & \b > \frac{1}{2}
@@
 C_4 = \begin{cases}
-\Cfourcaseone & \a,\b < \frac{1}{2} \\
-\Cfourcasetwo & \a<\frac{1}{2}<\b \\
-\Cfourcasethree & \frac{1}{2}<a,b
+\Cfourcaseone & \a,\b \leq \frac{1}{2} \\
+\Cfourcasetwo & \a\leq\frac{1}{2}<\b \\
+\Cfourcasethree & \frac{1}{2}<\a,\b
 \end{cases} \end{equation}
 
-To find $c^*$, we can now condition on the values of $w_2(\alpha)$ and $w_2(\beta)$.
-% If $w_2(\alpha)=C_4e^{-\alpha}>a$, then we know $x_a>\alpha$, so that $C_4e^{-x_a}=C_4e^{-2c^*}=a$ implies $c^*=\frac{1}{2}\ln(\frac{C_4}{a})$.
-%
-%If $w_2(\alpha)<a$ and $w_2(\beta)>a$, then we solve the equation
-%
-%$$ 1 - C_2e^x - C_3e^{-x} = a $$
-%
-%Multiplying through by $e^x$ yields a quadratic in $e^x$:
-%
-%$$ e^x - C_2e^{2x} - C_3 = ae^x $$
-%
-%$$ C_2 e^{2x} + (a-1) e^x + C_3 = 0 $$
-%
-%$$ e^x = \frac{1-a \pm \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} $$
-%
-%Since $C_2,C_3$ are negative, we know the function is concave down on this piece.
-Therefore, we take the rightmost solution, since the curve must be increasing through this point since the solution is unique.
-%
-%$$ c^* = \frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} \right) $$
-%
-%In the final case where $w_2(\beta)<a$, we have
-%
-%$$ m + C_1 e^{x_a} = a $$
-%implies
-%$$ C_1e^{x_a} = a-m$$
-%$$ x_a = \ln \frac{a-m}{C_1} $$
-%$$ c^* = \frac{1}{2} \ln \frac{a-m}{C_1} $$
-%
-%Our general formula is thus
-%\begin{equation}
-%c^* = \begin{cases}
-%\frac{1}{2} \ln \left( \frac{C_4}{a} \right) & a<w_2(\alpha) \\
-%\frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} \right) & w_2(\alpha)<a<w_2(\beta) \\
-%\frac{1}{2} \ln \left( \frac{a-m}{C_1}\right) & a>w_2(\beta)
-%\end{cases}
-%\end{equation}
-%Equivalently,
+To find $c^*$, we can now condition on the values of $w_2(x_\a)$ and $w_2(x_\b)$.
+
+\begin{enumerate}[{Case} 1.]
+\item If $w_2(x_\alpha)=C_4e^{-x_\a}>\a$, then $2c^*$ lies on the third piece of \eqref{w2laplace}. Hence the mean wave speed is given by $c^*=\frac{1}{2}\ln(\frac{C_4}{\a})$.
+
+\item If $w_2(x_\a)=C_4e^{-x_\a}\leq\a$ and $w_2(x_\b)=\m+C_1e^{x_\b}\geq\a$, then we solve the equation
+
+$$ 1 - C_2e^{2c^*} - C_3e^{-2c^*} = \a $$
+
+Multiplying through by $e^{2c^*}$ yields a quadratic in $e^{2c^*}$:
+
+$$ C_2 e^{4c^*} + (a-1) e^{2c^*} + C_3 = 0 $$
+
+Using the quadratic formula, we get two solutions to this equation.
+To determine which is correct, note that $w_2'(2c^*)$ must be negative.
+Since $C_2,C_3$ are negative, $w_2(x)$ is concave down on $[x_\b,x_\a]$, thus $w_2$ is increasing through the first solution and decreasing through the second.
+Clearly we must take the greater solution.
+Thus,
+$$ c^* = \frac{1}{2} \ln \left( \frac{1-\a + \sqrt{(1-\a)^2 - 4C_2C_3}}{2C_2} \right) $$
+
+\item If  $w_2(x_\b)=\m+C_1e^{x_\b}<\a$, we have
+
+$$ \m + C_1 e^{2c^*} = \a $$
+implies
+$$ c^* = \frac{1}{2} \ln \frac{\a-\m}{C_1} $$
+\end{enumerate}
+
+Our general formula is thus
 \begin{equation}
 c^* = \begin{cases}
-\frac{1}{2} \ln \left( \frac{C_4}{a} \right) & a<C_4e^{-\alpha} \\
-\frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} \right) & C_4e^{-\alpha}<a<m+C_1e^\alpha\\
-\frac{1}{2} \ln \left( \frac{a-m}{C_1}\right) & a>m+C_1e^\alpha
-\end{cases}
-\end{equation}
-
-Since the form of $w_2(x)$, and thus of $c^*$, depends on the values of $\a$ and $\b$; thus we will split into three cases for further analysis.
-
+\frac{1}{2} \ln \left( \frac{C_4}{\a} \right) & \a<C_4e^{-x_\a} \\
+\frac{1}{2} \ln \left( \frac{1-\a + \sqrt{(1-\a)^2 - 4C_2C_3}}{2C_2} \right) & C_4e^{-x_\a}<\a<\m+C_1e^{x_\b} \\
+\frac{1}{2} \ln \left( \frac{\a-\m}{C_1}\right) & \a>\m+C_1e^{x_\b}
+\end{cases}
+\end{equation}
+We can write this formula more explicitly depending on the signs of $\a-\frac{1}{2}$ and $\b-\frac{1}{2}$ respectively.
 %Let $c_1$ and $c_2$ denote the intermediate wave speeds measured at some threshold $0<h<m$.
@@
 
-\item $\a<\frac{1}{2}$, $\b<\frac{1}{2}$.
+\item $\a\leq\frac{1}{2}$, $\b\leq\frac{1}{2}$.
 \begin{equation}
@@
 
-We have $w_2(\alpha)=\frac{\b-\a(1-\m)}{2\b}$ and $w_2(\beta)=\m + \frac{\b(1-\m)-\a}{2\b}$. Thus,
+We have $w_2(x_\a)=\frac{\b-\a(1-\m)}{2\b}$ and $w_2(x_\b)=\m + \frac{\b(1-\m)-\a}{2\b}$. Thus,
 \begin{equation}
@@
 \frac{1}{2} \ln \left( \frac{\b-\a(1-\m)}{4\a^2\b} \right) & \a < \frac{\b-\a(1-\m)}{2\b} \\
-\frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - \frac{\a(1-m)}{b}}}{2\a} \right) & \frac{\b-\a(1-\m)}{2\b} < a < \frac{\b(1+\m)-\a}{2\b} \\
-\frac{1}{2} \ln \left( \frac{a-m}{\b(1-\m)-\a}\right) & a > \frac{\b(1+\m)-\a}{2\b}
-\end{cases}
-\end{equation}
-
-\item $\a<\frac{1}{2}$, $\b>\frac{1}{2}$.
+\frac{1}{2} \ln \left( \frac{1-\a + \sqrt{(1-\a)^2 - \frac{\a(1-\m)}{\b}}}{2\a} \right) & \frac{\b-\a(1-\m)}{2\b} \leq \a \leq \frac{\b(1+\m)-\a}{2\b} \\
+\frac{1}{2} \ln \left( \frac{\a-\m}{\b(1-\m)-\a}\right) & \a > \frac{\b(1+\m)-\a}{2\b}
+\end{cases}
+\end{equation}
+
+\item $\a\leq\frac{1}{2}$, $\b>\frac{1}{2}$.
 \begin{equation}
@@
 
-We have $w_2(\alpha)=\frac{1-4\a(1-\m)(1-\b)}{2}$ and $w_2(\beta)=\frac{1+\m-4\a(1-\b)}{2}$. Thus,
+We have $w_2(x_\a)=\frac{1-4\a(1-\m)(1-\b)}{2}$ and $w_2(x_\b)=\frac{1+\m-4\a(1-\b)}{2}$. Thus,
 \begin{equation}
@@
 \frac{1}{2} \ln \left( \frac{1-4\a(1-\m)(1-\b)}{4\a^2} \right) & a<\frac{1-4\a(1-\m)(1-\b)}{2} \\
-\frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4a(1-\m)(1-\b)}}{2a} \right) & \frac{1-4\a(1-\m)(1-\b)}{2}<a<\frac{1+\m-4\a(1-\b)}{2} \\
-\frac{1}{2} \ln \left( \frac{4(a-m)(1-b)}{1-\m-4\a(1-\b)}\right) & a>\frac{1+\m-4\a(1-\b)}{2}
+\frac{1}{2} \ln \left( \frac{1-\a + \sqrt{(1-\a)^2 - 4\a(1-\m)(1-\b)}}{2\a} \right) & \frac{1-4\a(1-\m)(1-\b)}{2}\leq\a\leq\frac{1+\m-4\a(1-\b)}{2} \\
+\frac{1}{2} \ln \left( \frac{4(\a-\m)(1-\b)}{1-\m-4\a(1-\b)}\right) & \a>\frac{1+\m-4\a(1-\b)}{2}
 \end{cases}
@@
 
-Thus, $w_2(\alpha)=\frac{1-\a-(1-\m)(1-\b)}{2(1-a)}$ and $w_2(\beta)=\m - \frac{1-\b+\m(1-\a)}{2(1-\a)}$
+Thus, $w_2(x_\a)=\frac{1-\a-(1-\m)(1-\b)}{2(1-\a)}$ and $w_2(x_\b)=\m - \frac{1-\b+\m(1-\a)}{2(1-\a)}$
 
@@
 c^* = \begin{cases}
-\frac{1}{2} \ln \left( \frac{1-\a-(1-\m)(1-\b)}{a} \right) & a<\frac{1-\a-(1-\m)(1-\b)}{2(1-a)} \\
-\frac{1}{2} \ln \Big( 2(1-a)\left[1-a + \sqrt{\frac{(1-a)^3-(1-\m)(1-\b) }{1-\a}}\right] \Big) & \frac{1-\a-(1-\m)(1-\b)}{2(1-a)}<a<\frac{\b-1+\m(1-\a)}{2(1-\a)} \\
-\frac{1}{2} \ln \left( \frac{4(m-a)(1-\a)(1-\b)}{1-\b+\m(1-\a)}\right) & a>\frac{\b-1+\m(1-\a)}{2(1-\a)}
+\frac{1}{2} \ln \left( \frac{1-\a-(1-\m)(1-\b)}{\a} \right) & \a<\frac{1-\a-(1-\m)(1-\b)}{2(1-\a)} \\
+\frac{1}{2} \ln \Big( 2(1-\a)\left[1-\a + \sqrt{\frac{(1-\a)^3-(1-\m)(1-\b) }{1-\a}}\right] \Big) & \frac{1-\a-(1-\m)(1-\b)}{2(1-\a)}\leq\a\leq\frac{\b-1+\m(1-\a)}{2(1-\a)} \\
+\frac{1}{2} \ln \left( \frac{4(\m-\a)(1-\a)(1-\b)}{1-\b+\m(1-\a)}\right) & \a>\frac{\b-1+\m(1-\a)}{2(1-\a)}
 \end{cases}
@@
 \begin{equation}
-w_2(x)=  m - \Phi(x-\Phi^{-1}(a)) + (1-m)\Phi(x-\Phi^{-1}(b))
-\end{equation}
-where $\alpha=\Phi^{-1}(a)$ and $\beta=\Phi^{-1}(b)$.
-
-$w_2$ has a unique global maximum at $x^*=\frac{\alpha+\beta}{2} + \frac{1}{\alpha-\beta}\ln\left(1-m\right)$.
-Thus, by Theorem \ref{theorem1}, $w_1$ and $w_2$ are a periodic traveling wave solution if $w_2(x^*)\leq b$.
+w_2(x)=  \m - \Phi(x-\Phi^{-1}(\a)) + (1-\m)\Phi(x-\Phi^{-1}(\b))
+\end{equation}
+
+$w_2$ has a unique global maximum at $x^*=\frac{x_\a+x_\b}{2} + \frac{1}{x_\a-x_\b}\ln\left(1-\m\right)$.
+Thus, by Theorem \ref{theorem1}, $w_1$ and $w_2$ are a periodic traveling wave solution if $w_2(x^*)\leq \b$.
 \end{ex}

### 2021-06-20 paper_draft3.tex
figures

@@
 %\usepackage{caption,subcaption}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 
+\begin{figure}[h!]
+\centering
+  \caption{Plot of the growth function $g(u)$ compared to the identity function with growth parameters $\alpha=0.33$, $\beta=0.66$, and $\mu=0.5$.}
+  \includegraphics{figures/fig1.png}
+\end{figure}
+
 Piecewise constant growth functions and uniform distributions have been used in the studies of integro-difference equations; see for example~\cite{kot1, lut,otto,  pnas}.
@@
 \begin{lem} \label{lemma1}
-If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then there exists unique $c^*\in\mathbb R$ such that $Q[w_2](x)=w_1(x-2c^*)$ for all $x\in\mathbb R$.
+If $\max_{x\in\mathbb R}w_2(x)\leq \b$, then there exists unique $c^*\in\mathbb R$ such that $Q[w_2](x)=w_1(x-2c^*)$ for all $x\in\mathbb R$.
 \end{lem}
 
-\begin{proof} Let $x_\a=\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}$.
+\begin{proof} Let $x_\a=\max\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\max\{x\in\mathbb R\mid w_1(x)\geq\b\}$.
 Since $w_1$ is monotone, it follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$.
@@
 \begin{equation}
-c^*=\frac{1}{2}\sup\{x\in\mathbb R\mid w_2(x)\geq\a\}
+c^*=\frac{1}{2}\max\{x\in\mathbb R\mid w_2(x)\geq\a\}
 \end{equation}
@@
 It follows that $w_2(x)\geq\a$ for $x\leq 2c^*$ and $w_2(x)<\alpha$ for $x>2c^*$.
-Along with the assumption that $\sup_{x\in\mathbb R}w_2(x)\leq\b$, we can apply the integro-difference operator once more:
+Along with the assumption that $\max_{x\in\mathbb R}w_2(x)\leq\b$, we can apply the integro-difference operator once more:
 \begin{equation} \begin{aligned}
@@
 
+\begin{figure}
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.8\linewidth]{figures/fig2A.png}
+  \label{fig:sub1}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.8\linewidth]{figures/fig2B.png}
+  \label{fig:sub2}
+\end{subfigure}
+\caption{Plots of $w_1(x)$ (left) and $w_2(x)$ (right) with the Laplace dispersal kernel and growth parameters $\alpha=0.3$, $\mu=0.5$, and $\beta=0.8$}
+\label{fig:test}
+\end{figure}
+
 By Lemma \ref{lemma1}, the wave functions $w_1(x)$ and $w_2(x)$ satisfy $Q^2[w_1](x)=w_1(x-2c^*)$ and $Q^2[w_2](x)=w_2(x-2c^*)$.
@@
 
+The condition that $\max_{x\in\mathbb R}w_2(x)\leq \b$ may be difficult to verify for some choices of dispersal kernel. Thus, we provide a sufficient condition for this assumption:
+\begin{lem} \label{lemma}
+Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. If $k(x)$ is unimodal and
+$$ \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy \leq \b $$
+then $\max_{x\in\mathbb R}w_2(x) \leq \b$.
+\end{lem}
+
+\begin{proof}
+We have
+\begin{equation} \begin{aligned}
+w_2(x) &= (k*(g\circ w_1))(x) \\
+&\leq (k*(m+(1-m)\mathbf 1_{[x_\b,x_a]}))(x) \\
+&= m + (1-m)(k*\mathbf 1_{[x_\b,x_a]})(x) \\
+&= \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy .
+\end{aligned}
+\end{equation}
+
+Taking the maximum over all $x$, we may shift the function horizontally so that the bounds of integration are symmetric. Since $k(x)$ is unimodal, the integral is then maximized for $x=0$.
+\begin{equation} \begin{aligned}
+\max_{x\in\mathbb R} w_2(x) &\leq \max_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy \right) \\
+&= \max_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (x-y) \, dy \right) \\
+&= \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy.
+\end{aligned}
+\end{equation}
+\end{proof}
+
 \begin{thm} \label{theorem1}
-If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then the recurrence \eqref{q} has a periodic traveling wave solution $(u_n)_{n=0}^{\infty}$ satisfying
+If $\max_{x\in\mathbb R}w_2(x)\leq \b$, then the recurrence \eqref{q} has a periodic traveling wave solution $(u_n)_{n=0}^{\infty}$ satisfying
 %\begin{equation} \label{ptw}
@@
 
+\begin{figure}[h!] 
+\centering
+  \caption{The periodic traveling wave solution \eqref{ptw} with a monotone initial condition for times $1 \leq n \leq 11$ using the Laplace dispersal kernel, $\alpha=0.2$, $\mu=0.3$, and $\beta=0.8$.
+Later timepoints are colored in red, with earlier timepoints colored in green.}
+\label{fig3}
+  \includegraphics{figures/fig3.png}
+\end{figure}
+
+Figure \ref{fig3} shows the propagation of the periodic traveling wave solution for a particular choice of dispersal kernel and growth parameters.
+
 \begin{thm}  \label{theorem2}
-If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then for all $\epsilon>0$, the sequence \ref{ptw} satisfies
+If $\max_{x\in\mathbb R}w_2(x)\leq \b$, then for all $\epsilon>0$, the sequence \ref{ptw} satisfies
 \begin{equation}
@@
 \begin{equation}
-\lim_{n\to\infty}\sup_{x>n(c^*+\epsilon)}u_n(x)=0.
+\lim_{n\to\infty}\max_{x>n(c^*+\epsilon)}u_n(x)=0.
 \end{equation}
@@
 \begin{equation} \begin{aligned}
-\lim_{n\to\infty} \sup_{x>n(c^*+\epsilon)} u_n(x) 
-&\leq \lim_{n\to\infty} \sup_{x>n(c^*+\epsilon)} \max\{w_1(x-nc^*),w_2(x-nc^*)\} \\
-&= \lim_{n\to\infty} \sup_{x>n\epsilon} \max\{w_1(x),w_2(x)\} \\
+\lim_{n\to\infty} \max_{x>n(c^*+\epsilon)} u_n(x) 
+&\leq \lim_{n\to\infty} \max_{x>n(c^*+\epsilon)} \max\{w_1(x-nc^*),w_2(x-nc^*)\} \\
+&= \lim_{n\to\infty} \max_{x>n\epsilon} \max\{w_1(x),w_2(x)\} \\
 &= \limsup_{x\to\infty} \max\{w_1(x),w_2(x)\} \\ 
@@
 \begin{lem}\label{lemma2}
-Suppose $k(x)$ is compactly supported on $[-\sigma,\sigma]$, for some $\sigma>0$.
-Then for any continuous function $u(x)$, if $u(x)=0$ for $x \in \Omega \subseteq \mathbb R$, then $(k*u)(x)=0$ for $x\in\Omega$ such that $d(x,\mathbb R\setminus\Omega) \geq \sigma$, where $d(x,\mathbb R\setminus\Omega):= \inf \{d(x,y) \mid y\in \mathbb R\setminus\Omega\}$.
+Suppose $k(x)$ is compactly supported on $[-\sigma,\sigma]$ for some $\sigma>0$, and let $u \in C(\mathbb R)$.
+If $u(x)=0$ for $x \in \Omega \subseteq \mathbb R$, then $(k*u)(x)=0$ if $d(x,\mathbb R\setminus\Omega):= \inf \{d(x,y) \mid y\in \mathbb R\setminus\Omega\}$.
 \end{lem}
@@
 \begin{thm} Let $u_0(x)$ be a non-negative continuous function with compact support such that the set $A=\{x\in\mathbb R:\a\leq u_0(x)\leq \b\}$ is connected.
-Suppose $k(x)$ has compact support, $\sup_{x\in\mathbb R}w_2(x)\leq \b$, and $c^* > 0$.
+Suppose $k(x)$ has compact support, $\max_{x\in\mathbb R}w_2(x)\leq \b$, and $c^* > 0$.
 For $A$ sufficiently large, the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$ spreads with speed $c^*$, i.e.
@@
 \begin{equation}
-\lim_{n\to\infty}\sup_{|x|>n(c^*+\epsilon)}u_n(x)=0.
+\lim_{n\to\infty}\max_{|x|>n(c^*+\epsilon)}u_n(x)=0.
 \end{equation}

### 2021-06-20 figures/fig1.py

@@ -1,0 +1,34 @@
+
+
+
+from pyide import *
+from scipy.stats import norm
+
+
+H = lambda x : np.heaviside(x, 1)
+
+alpha=0.33
+mu=0.5
+beta=0.66
+
+g = lambda u: H(u-alpha) + (mu-1) * H(u-beta)
+
+U = np.arange(0, 1, 0.01)
+
+import matplotlib.pyplot as plt
+
+#plt.plot(U, g(U))
+
+# horizontal lines
+plt.plot([0,alpha],[0,0], color='blue')
+plt.plot([alpha,beta],[1,1], color='blue')
+plt.plot([beta,1],[mu,mu], color='blue')
+# vertical lines
+plt.plot([alpha,alpha],[0,1], color='blue' , linestyle='dotted', label='g(u)')
+plt.plot([beta,beta],[1,mu], color='blue', linestyle='dotted')
+
+plt.plot([0,1],[0,1], color='black', linestyle='dashed', label='Identitfy function')
+
+plt.legend()
+
+plt.savefig('fig1.png')

### 2021-06-20 figures/fig2.py

@@ -1,0 +1,49 @@
+
+
+
+from pyide import *
+from scipy.stats import norm
+
+
+H = lambda x : np.heaviside(x, 1)
+
+K = lambda x : H(x) + 1/2 * (1-2*H(x)) * np.exp((2*H(x)-1)*(-x))
+
+w1 = lambda x : K(-x)
+X = np.arange(-5, 5, 0.01)
+
+import matplotlib.pyplot as plt
+
+plt.plot(X, w1(X), label='y=w1(x)')
+plt.ylim(0, 1.1)
+plt.legend()
+
+plt.savefig('fig2A.png')
+
+
+plt.clf()
+alpha=0.3
+beta = 0.8
+mu = 0.5
+
+# Find x_alpha and x_beta
+K_inv = lambda p : np.log(2*p)*H(1/2-p) - np.log(2-2*p)*H(p-1/2)
+P = np.arange(0, 1, 0.01)
+plt.plot(P, K_inv(P) ,label='y=K^(-1)(x)')
+
+plt.savefig('K.png')
+
+x_alpha = K_inv(1-alpha)
+x_beta =  K_inv(1-beta)
+print(x_alpha,x_beta)
+w2 = lambda x : 1 - K(x-x_alpha) - (1-mu) * (1-K(x-x_beta))
+
+plt.clf()
+plt.plot(X, w2(X), label='y = w2(x)')
+plt.ylim(0, 1.1)
+plt.legend()
+
+plt.savefig('fig2B.png')
+
+
+

### 2021-06-20 figures/fig3.py

@@ -1,0 +1,34 @@
+
+
+import pyide
+from scipy.stats import norm
+import numpy as np
+import matplotlib.pyplot as plt
+
+from imp import reload # for debugging
+alpha=0.2
+beta=0.8
+mu=0.3
+
+H = lambda x : np.heaviside(x, 1)
+
+g = lambda x : H(x-alpha) - (1-mu)*H(x-beta)
+
+import matplotlib.pyplot as plt
+
+U = np.arange(0, 1, 0.01)
+k = lambda x: 1/2 * np.exp(-np.abs(x))
+
+model = pyide.IDEModel(growthFunction=pyide.GrowthFunction(g),
+                  dispersalKernel=pyide.DisperalKernel(k))
+                  
+                
+sim = pyide.IDESimulation(model)
+sim.setDomain(xmin=-10, xmax=10, dx=0.01)
+sim.setInitialCondition(lambda x : H(-x))
+sim.setBoundaryCondition('static')
+
+n = 11
+sim.run(n)
+sim.plot(times=np.arange(1, n), file='fig3.png')
+

### 2021-06-20 figures/ide.py

@@ -1,0 +1,81 @@
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+class ide:
+
+    
+    
+    
+    def __init__(self, g, k, xmin, xmax, dx):
+        self.g = g
+        self.k = k
+        
+        N = int((xmax-xmin)/dx/2)
+        
+        self.domain = np.linspace(xmin,xmax,2*N+1)
+        
+        domain_large = np.linspace(2*xmin,2*xmax,4*N+1)
+        
+        k = self.dispersal_kernel
+        pdf_array_large = k(domain_large)
+        self.pdf_array = pdf_array_large[N:(3*N+1)]
+        
+        cdf_array_left = [0]
+        for i in range(2*N):
+            cdf_array_left.append(pdf_array_large[i]+cdf_array_left[i])
+        
+        cdf_array_right = [0]
+        for i in range(2*N):
+            cdf_array_right.append(pdf_array_large[4*N-i]+cdf_array_right[i])
+        cdf_array_right = cdf_array_right[::-1]
+        
+        self.cdf_array_left = dx*np.array(cdf_array_left)
+        self.cdf_array_right = dx*np.array(cdf_array_right)
+            
+        return
+    
+    def set_initial_density(self,u0):
+        X = self.domain
+        self.density_sequence = [u0(X)]
+        return
+
+    def iterate(self,U):
+        X = self.domain
+        step_size = X[1] - X[0]
+        
+        g = self.growth_function
+        
+        N = int((len(X)-1)/2)
+        
+        pdf = self.pdf_array
+        cdf_left = self.cdf_array_left
+        cdf_right = self.cdf_array_right
+        
+        U_center = step_size * np.convolve(pdf, g(U), mode='same')
+        U_left = g(U[-1]) * cdf_left
+        U_right = g(U[0]) * cdf_right
+        
+        return U_center + U_left + U_right
+    
+    def run(self,time_steps):
+        
+        U_sequence = self.density_sequence
+        
+        U = U_sequence[0]
+        
+        for t in range(time_steps):
+            U = self.iterate(U)
+            U_sequence.append(U)
+            
+        self.density_sequence = U_sequence
+    
+    def plot(self):
+        X = self.domain
+        U_seq = self.density_sequence
+        T = len(U_seq)
+        
+        for t in range(T):
+            U = U_seq[t]
+            plt.plot(X, U, color=(t/T,1-t/T,0))
+        plt.show()

### 2021-06-20 figures/pyide.py

@@ -305,7 +305,7 @@ class IDESimulation:
             
             self.timeSeries.append(U)
             
-    def plot(self, times=[], file):
+    def plot(self, times=[], file=None):
     
         X = self.domain
         U_seq = self.timeSeries

### 2021-06-21 paper_draft3.tex
more work

--- 2021-06-20 paper_draft3.tex
@@
 %\end{cor}
+
+The condition that $\sup_{x\in\mathbb R}w_2(x)\leq \b$ may be difficult to verify for some choices of dispersal kernel. Thus, we provide a sufficient condition for this assumption:
+\begin{lem} \label{lemma}
+Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. If $k(x)$ is unimodal and
+$$ \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy \leq \b $$
+then $\sup_{x\in\mathbb R}w_2(x) \leq \b$.
+\end{lem}
+
+\begin{proof}
+For all $x\in\mathbb R$, we have
+\begin{equation} \begin{aligned}
+w_2(x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy  \\
+&\leq\int_{-\infty}^{\infty} k(x-y) (\m + (\m-1) \mathbf 1_{[x_\b,x_\a]}(y) )\, dy \\
+&= \m + \int_{-\infty}^{\infty} k(x-y) (\m-1) \mathbf 1_{[x_\b,x_\a]}(y) \, dy \\
+&= \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy .
+\end{aligned}
+\end{equation}
+
+Taking the maximum over all $x$, we may shift the function horizontally so that the bounds of integration are symmetric. Since $k(x)$ is unimodal, the integral is then maximized for $x=0$.
+\begin{equation} \begin{aligned}
+\sup_{x\in\mathbb R} w_2(x) &\leq \sup_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy \right) \\
+&= \sup_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (x-y) \, dy \right) \\
+&= \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy.
+\end{aligned}
+\end{equation}
+\end{proof}
 
@@
 
+\begin{figure}[h!] 
+\centering
+  \caption{Numerical simulation of the integro-difference equation with Laplace dispersal kernel, $\alpha=0.2$, $\mu=0.3$, and $\beta=0.8$.
+Later timepoints are colored in red, with earlier timepoints colored in green.}
+\label{fig3}
+  \includegraphics{figures/fig3.png}
+\end{figure}
+
+Figure \ref{fig3} shows the propagation of the periodic traveling wave solution for a particular choice of dispersal kernel and growth parameters.
+
 \begin{thm}  \label{theorem2}
@@
 \begin{equation}
-\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n+1}(x)=m
+\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n+1}(x)=\m
 \end{equation}
@@
 \lim_{n\to\infty} \sup_{x>n(c^*+\epsilon)} u_n(x) 
-&\leq \lim_{n\to\infty} \sup_{x>n(c^*+\epsilon)} \max\{w_1(x-nc^*),w_2(x-nc^*)\} \\
-&= \lim_{n\to\infty} \sup_{x>n\epsilon} \max\{w_1(x),w_2(x)\} \\
-&= \limsup_{x\to\infty} \max\{w_1(x),w_2(x)\} \\ 
-&= \max\{\limsup_{x\to\infty} w_1(x),\limsup_{x\to\infty} w_2(x)\} \\
+&\leq \lim_{n\to\infty} \sup_{x>n(c^*+\epsilon)} \sup\{w_1(x-nc^*),w_2(x-nc^*)\} \\
+&= \lim_{n\to\infty} \sup_{x>n\epsilon} \sup\{w_1(x),w_2(x)\} \\
+&= \limsup_{x\to\infty} \sup\{w_1(x),w_2(x)\} \\ 
+&= \sup\{\limsup_{x\to\infty} w_1(x),\limsup_{x\to\infty} w_2(x)\} \\
 &= 0.
@@
 
-The reader can easily verify that the Laplace kernel satisfies hypotheses (H1) - (H3). The proof that is also satisfies (H4) is left in the appendix. The periodic traveling waves are given by
+The reader can easily verify that the Laplace kernel satisfies hypotheses (H1) - (H3); the proof of (H4) is left in the appendix.
+
+The periodic traveling wave profiles are given by
 
@@
 %\end{equation}
+%\begin{equation} \label{w2laplace}
+%w_2(x) = \begin{cases}
+%m + C_1 e^x & x < x_\b \\
+%1 - C_2 e^x - C_3 e^{-x} & x_\b \leq x \leq x_\a \\
+%C_4 e^{-x} & x_\a < x 
+%\end{cases} \end{equation}
+%or equivalently
+
 \begin{equation} \label{w2laplace}
 w_2(x) = \begin{cases}
-m + C_1 e^x & x < x_\b \\
-1 - C_2 e^x - C_3 e^{-x} & x_\b \leq x \leq x_\a \\
-C_4 e^{-x} & x_\a < x 
+m + \left( \frac{1-\m}{2}e^{-x_\b} - \frac{1}{2}e^{-x_\a} \right) e^x & x < x_\b \\
+1 - \left( \frac{1}{2} e^{-x_\a} \right) e^x - \left( \frac{1-\m}{2} e^{x_\b} \right)  e^{-x} & x_\b \leq x \leq x_\a \\
+\left( \frac{1}{2} e^{x_\a} - \frac{1-\m}{2} e^{x_\b} \right) e^{-x} & x_\a < x 
 \end{cases} \end{equation}
+
 where
 \begin{equation}
-x_\a = \begin{cases} -\ln(2\a) & \a\leq \frac{1}{2} \\ \ln(2-2\a) & \a > \frac{1}{2} \end{cases} \quad
+x_\a = \begin{cases} -\ln(2\a) & \a\leq \frac{1}{2} \\ \ln(2-2\a) & \a > \frac{1}{2} \end{cases}, \quad
 x_\b = \begin{cases} -\ln(2\b) & \b\leq \frac{1}{2} \\ \ln(2-2\b) & \b > \frac{1}{2} \end{cases} 
 \end{equation}
+This leads to an equation for the mean wave speed
+\begin{equation}
+c^* = \begin{cases}
+\frac{1}{2}x_\a  + \frac{1}{2}\log \left( \frac{1 - (1-\m) e^{x_\b-x_\a}}{2\a} \right) & \a \leq w_2(x_\a) \\
+\frac{1}{2}x_\a + \frac{1}{2} \log \left( 1-\a + \sqrt{(1-\a)^2 - (1-\mu) e^{x_\b-x_\a}} \right) & w_2(x_\a) < \a < w_2(x_\b) \\
+\frac{1}{2}x_\a + \frac{1}{2} \log \left( \frac{2(\a-\m)}{(1-\m)e^{x_\a-x_\b}-1} \right) & \a \geq w_2(x_\b)
+\end{cases} 
+\end{equation}
+and
+
+\begin{equation} \begin{aligned}
+C_1 &= \frac{1-\m}{2}e^{-x_\b} - \frac{1}{2}e^{-x_\a} \\
+C_2 &= \frac{1}{2} e^{-x_\a} \\
+C_3 &= \frac{1-\m}{2} e^{x_\b} \\
+C_4 &= \frac{1}{2} e^{x_\a} - \frac{1-\m}{2} e^{x_\b}
+\end{aligned} \end{equation}
+
 %$x_\a=w_1^{-1}(\a)$, $x_\b=w_1^{-1}(\b)$, with

### 2021-06-21 figures/pyide.py

@@ -3,7 +3,7 @@ import numpy as np
 import matplotlib.pyplot as plt
     
 # class for handling growth functions
-
+plt.rcParams.update({"text.usetex": True})
 class GrowthFunction:
     
     def __init__(self, g):

### 2021-06-23 paper_draft3.tex
more figures

@@
   \caption{Plot of the growth function $g(u)$ compared to the identity function with growth parameters $\alpha=0.33$, $\beta=0.66$, and $\mu=0.5$.}
-  \includegraphics{figures/fig1.png}
+  \includegraphics[width=.8\linewidth]{figures/fig1.png}
 \end{figure}
@@
 
-\item  for all $\lambda\in(0,1)$, for all $y\in\mathbb R$, the function $x \mapsto k(x)-\lambda k(x-y)$ has at most one zero-crossing in $\mathbb R$.
+\item  for all $\lambda\in(0,1)$, for all $a\in\mathbb R$, the function $x \mapsto k(x)-\lambda k(x-a)$ has at most one zero-crossing in $\mathbb R$.
 \end{enumerate}
@@
 
-\begin{prop} \label{prop1}
-%Let $\mathcal B$ denote the space of bounded, continuous, non-negative functions $\mathbb R \to \mathbb R$.
+%\begin{prop} \label{prop1}
+%%Let $\mathcal B$ denote the space of bounded, continuous, non-negative functions $\mathbb R \to \mathbb R$.
 $Q$ is a bounded nonlinear operator $\mathcal B \to \mathcal B$, and satisfies the following properties for all $u \in \mathcal B$:
-The operator $Q$ satisfies the following properties for all bounded continuous functions $u : \mathbb R \to \mathbb R_{\geq 0}$:
-
-\begin{enumerate}[(i.)]
-\item \it{(Translation invariance)} $Q[T^t[u]]=T^t[Q[u]]$ for any translation operator $T^t[u](x)=u(x+t)$.
-\item \it{(Symmetric)} If $u(x)=u(-x)$ then $Q[u](x)=Q[u](-x)$.
-\item \it{(Limit-preserving)} If $u(x)\to\ell$ as $x\to\infty$, then $Q[u](x)\to g(\ell)$ as $x\to\infty$; likewise as $x\to-\infty$.
-\end{enumerate}
-\end{prop}
+%The operator $Q$ satisfies the following properties for all bounded continuous functions $u : \mathbb R \to \mathbb R_{\geq 0}$:
+%
+%\begin{enumerate}[(i.)]
+%\item \it{(Translation invariance)} $Q[T^t[u]]=T^t[Q[u]]$ for any translation operator $T^t[u](x)=u(x+t)$.
+%\item \it{(Symmetric)} If $u(x)=u(-x)$ then $Q[u](x)=Q[u](-x)$.
+%\item \it{(Limit-preserving)} If $u(x)\to\ell$ as $x\to\infty$, then $Q[u](x)\to g(\ell)$ as $x\to\infty$; likewise as $x\to-\infty$.
+%\end{enumerate}
+%\end{prop}
 
@@
 
-The condition that $\sup_{x\in\mathbb R}w_2(x)\leq \b$ may be difficult to verify for some choices of dispersal kernel. Thus, we provide a sufficient condition for this assumption:
-\begin{lem} \label{lemma}
-Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. If $k(x)$ is unimodal and
-$$ \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy \leq \b $$
-then $\sup_{x\in\mathbb R}w_2(x) \leq \b$.
-\end{lem}
-
-\begin{proof}
-For all $x\in\mathbb R$, we have
-\begin{equation} \begin{aligned}
-w_2(x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy  \\
-&\leq\int_{-\infty}^{\infty} k(x-y) (\m + (\m-1) \mathbf 1_{[x_\b,x_\a]}(y) )\, dy \\
-&= \m + \int_{-\infty}^{\infty} k(x-y) (\m-1) \mathbf 1_{[x_\b,x_\a]}(y) \, dy \\
-&= \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy .
-\end{aligned}
-\end{equation}
-
-Taking the maximum over all $x$, we may shift the function horizontally so that the bounds of integration are symmetric. Since $k(x)$ is unimodal, the integral is then maximized for $x=0$.
-\begin{equation} \begin{aligned}
-\sup_{x\in\mathbb R} w_2(x) &\leq \sup_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy \right) \\
-&= \sup_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (x-y) \, dy \right) \\
-&= \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy.
-\end{aligned}
-\end{equation}
-\end{proof}
+%The condition that $\sup_{x\in\mathbb R}w_2(x)\leq \b$ may be difficult to verify for some choices of dispersal kernel. Thus, we provide a sufficient condition for this assumption:
+%\begin{lem} \label{lemma}
+%Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. If $k(x)$ is unimodal and
+%$$ \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy \leq \b $$
+%then $\sup_{x\in\mathbb R}w_2(x) \leq \b$.
+%\end{lem}
+%
+%\begin{proof}
+%For all $x\in\mathbb R$, we have
+%\begin{equation} \begin{aligned}
+%w_2(x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy  \\
+%&\leq\int_{-\infty}^{\infty} k(x-y) (\m + (\m-1) \mathbf 1_{[x_\b,x_\a]}(y) )\, dy \\
+%&= \m + \int_{-\infty}^{\infty} k(x-y) (\m-1) \mathbf 1_{[x_\b,x_\a]}(y) \, dy \\
+%&= \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy .
+%\end{aligned}
+%\end{equation}
+%
+%Taking the maximum over all $x$, we may shift the function horizontally so that the bounds of integration are symmetric. Since $k(x)$ is unimodal, the integral is then maximized for $x=0$.
+%\begin{equation} \begin{aligned}
+%\sup_{x\in\mathbb R} w_2(x) &\leq \sup_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy \right) \\
+%&= \sup_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (x-y) \, dy \right) \\
+%&= \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy.
+%\end{aligned}
+%\end{equation}
+%\end{proof}
 
@@
 The next theorem concerns the spreading behavior of solutions to the IDE \eqref{q} with compactly supported initial data.
-We also assume the disperal kernel is compactly supported.
-First, we introduce a useful lemma for compactly supported kernels.
-
-\begin{lem}\label{lemma2}
-Suppose $k(x)$ is compactly supported on $[-\sigma,\sigma]$ for some $\sigma>0$, and let $u \in C(\mathbb R)$.
+We also assume the disperal kernel is compactly supported.% First, we introduce a useful lemma for compactly supported kernels.
+
+%\begin{lem}\label{lemma2}
+%Suppose $k(x)$ is compactly supported on $[-\sigma,\sigma]$ for some $\sigma>0$, and let $u \in C(\mathbb R)$.
 If $u(x)=0$ for $x \in \Omega \subseteq \mathbb R$, then $(k*u)(x)=0$ if $d(x,\mathbb R\setminus\Omega):= \inf \{d(x,y) \mid y\in \mathbb R\setminus\Omega\}$.
-\end{lem}
-
-\begin{proof}
-Let $x\in\Omega$ such that $d(x,\mathbb R\setminus\Omega) \geq \sigma$.
+%\end{lem}
+%
+%\begin{proof}
+%Let $x\in\Omega$ such that $d(x,\mathbb R\setminus\Omega) \geq \sigma$.
 Then $(x-\sigma,x+\sigma)$ is a subset of  $\Omega$ on which $u$ vanishes; thus $ (k*u)(x) = \int_{x-\sigma}^{x+\sigma}k(x-y)u(y)\,dy = 0.$
-\end{proof}
-
-\begin{thm} Let $u_0(x)$ be a non-negative continuous function with compact support such that the set $A=\{x\in\mathbb R:\a\leq u_0(x)\leq \b\}$ is connected.
-Suppose $k(x)$ has compact support, $\sup_{x\in\mathbb R}w_2(x)\leq \b$, and $c^* > 0$.
-For $A$ sufficiently large, the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$ spreads with speed $c^*$, i.e.
+%\end{proof}
+
+\begin{thm} Suppose $k(x)$ has compact support and $\sup_{x\in\mathbb R}w_2(x)\leq \b$.
+Let $u_0(x)$ be a non-negative continuous function, and let $A=\{x\in\mathbb R:\a\leq u_0(x)\leq \b\}$.
+If $A$ is connected with sufficiently large radius and $c^* \geq 0$, then the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$ spreads with speed $c^*$, i.e.
 \begin{equation}
@@
 Note that $g(u_1(x))=g(w_1(x))$ for all $x >-r-x_\b$.
-Thus, by Lemma \ref{lemma2}, $Q[u_1](x)=(k*(g\circ u_1))(x)=(k*(g\circ w_1))(x)=Q[w_1](x)$ for all $x>-r-x_\b+\sigma$.
+Thus $Q[u_1](x)=(k*(g\circ u_1))(x)=(k*(g\circ w_1))(x)=Q[w_1](x)$ for all $x>-r-x_\b+\sigma$.
 If we assume $r \geq x_\b+\sigma$, then $u_2(x)=Q[u_1](x)=Q[w_1](x-r)=w_2(x-r)$ for $x>0$.
@@
 \begin{equation}
-u_2(x) = Q[u_1](x) \begin{cases}
+u_2(x) = Q[u_1](x) = \begin{cases}
 w_2(x-r) & x \geq 0 \\
@@
 
+\begin{figure}[h!] 
+\centering
+  \caption{Spreading behavior for a uniform dispersal kernel with $\alpha=0.3$, $\mu=0.6$, and $\beta=0.7$.
+The time steps corresponding to $w_1(x)$ are colored in blue, while time steps corresponding to $w_2(x)$ are colored in red.}
+\label{fig5}
+  \includegraphics[width=.8\linewidth]{figures/fig5.png}
+\end{figure}
+
 \begin{rem}
@@
 
-The reader can easily verify that the Laplace kernel satisfies hypotheses (H1) - (H3); the proof of (H4) is left in the appendix.
+The reader can easily verify that the Laplace kernel satisfies hypotheses (H1) - (H3); the proof of (H4) is left in the appendix \ref{laplaceproof}.
 
@@
 
-\begin{equation}
+\begin{equation} \label{w1laplace}
 w_1(x) =   \begin{cases} 
@@
 \end{equation}
+A necessary condition for formulas \eqref{w1laplace} and \eqref{w2laplace} to generate a periodic traveling wave solution are given in Lemma \ref{laplacebound}.
 This leads to an equation for the mean wave speed
@@
 \end{equation}
-and
-
-\begin{equation} \begin{aligned}
-C_1 &= \frac{1-\m}{2}e^{-x_\b} - \frac{1}{2}e^{-x_\a} \\
-C_2 &= \frac{1}{2} e^{-x_\a} \\
-C_3 &= \frac{1-\m}{2} e^{x_\b} \\
-C_4 &= \frac{1}{2} e^{x_\a} - \frac{1-\m}{2} e^{x_\b}
-\end{aligned} \end{equation}
-
-%$x_\a=w_1^{-1}(\a)$, $x_\b=w_1^{-1}(\b)$, with
-%$$ w_1^{-1}(p) = \begin{cases} -\ln(2p) & p\leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases} $$
-The constants $C_1,C_2,C_3$, and $C_4$ are continuous functions of the growth parameters $\alpha$, $\beta$, and $\mu$, with $C_2,C_3,C_4\geq0$. They can be expressed as piecewise expressions:
+%and
+%
+%\begin{equation} \begin{aligned}
+%C_1 &= \frac{1-\m}{2}e^{-x_\b} - \frac{1}{2}e^{-x_\a} \\
+%C_2 &= \frac{1}{2} e^{-x_\a} \\
+%C_3 &= \frac{1-\m}{2} e^{x_\b} \\
+%C_4 &= \frac{1}{2} e^{x_\a} - \frac{1-\m}{2} e^{x_\b}
+%\end{aligned} \end{equation}
+%
+%%$x_\a=w_1^{-1}(\a)$, $x_\b=w_1^{-1}(\b)$, with
+%%$$ w_1^{-1}(p) = \begin{cases} -\ln(2p) & p\leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases} $$
+%The constants $C_1,C_2,C_3$, and $C_4$ are continuous functions of the growth parameters $\alpha$, $\beta$, and $\mu$, with $C_2,C_3,C_4\geq0$. They can be expressed as piecewise expressions:
 \newcommand{\Conecaseone}{\b(1-\m)-\a}
@@
 \newcommand{\Conecasethree}{- \frac{1-\b+\m(1-\a)}{4(1-\a)(1-\b)} }
-
-\begin{equation}
-C_1 = \begin{cases}
-\Conecaseone & \a,\b \leq \frac{1}{2} \\
-\Conecasetwo & \a\leq\frac{1}{2}<\b \\
-\Conecasethree & \frac{1}{2}<\a,\b
-\end{cases} \end{equation}
-
+%
+%\begin{equation}
+%C_1 = \begin{cases}
+%\Conecaseone & \a,\b \leq \frac{1}{2} \\
+%\Conecasetwo & \a\leq\frac{1}{2}<\b \\
+%\Conecasethree & \frac{1}{2}<\a,\b
+%\end{cases} \end{equation}
+%
 \newcommand{\Ctwocaseone}{\a}
 \newcommand{\Ctwocasetwo}{\frac{1}{4(1-\a)}}
-
-\begin{equation}
-C_2 = \begin{cases}
-\Ctwocaseone & \a \leq \frac{1}{2} \\
-\Ctwocasetwo & \a > \frac{1}{2}
-\end{cases} \end{equation}
-
+%
+%\begin{equation}
+%C_2 = \begin{cases}
+%\Ctwocaseone & \a \leq \frac{1}{2} \\
+%\Ctwocasetwo & \a > \frac{1}{2}
+%\end{cases} \end{equation}
+%
 \newcommand{\Cthreecaseone}{\frac{1-\m}{4\b}}
 \newcommand{\Cthreecasetwo}{(1-\m)(1-\b)}
-
-\begin{equation}
-C_3 = \begin{cases}
-\Cthreecaseone & \b \leq \frac{1}{2} \\
-\Cthreecasetwo & \b > \frac{1}{2}
-\end{cases} \end{equation}
-
+%
+%\begin{equation}
+%C_3 = \begin{cases}
+%\Cthreecaseone & \b \leq \frac{1}{2} \\
+%\Cthreecasetwo & \b > \frac{1}{2}
+%\end{cases} \end{equation}
+%
 \newcommand{\Cfourcaseone}{\frac{\b-\a(1-m)}{4\a\b}}
@@
 \newcommand{\Cfourcasethree}{1-\a-(1-\m)(1-\b)}
-
-\begin{equation}
-C_4 = \begin{cases}
-\Cfourcaseone & \a,\b \leq \frac{1}{2} \\
-\Cfourcasetwo & \a\leq\frac{1}{2}<\b \\
-\Cfourcasethree & \frac{1}{2}<\a,\b
-\end{cases} \end{equation}
-
-To find $c^*$, we can now condition on the values of $w_2(x_\a)$ and $w_2(x_\b)$.
-
-\begin{enumerate}[{Case} 1.]
-\item If $w_2(x_\alpha)=C_4e^{-x_\a}>\a$, then $2c^*$ lies on the third piece of \eqref{w2laplace}. Hence the mean wave speed is given by $c^*=\frac{1}{2}\ln(\frac{C_4}{\a})$.
-
-\item If $w_2(x_\a)=C_4e^{-x_\a}\leq\a$ and $w_2(x_\b)=\m+C_1e^{x_\b}\geq\a$, then we solve the equation
-
-$$ 1 - C_2e^{2c^*} - C_3e^{-2c^*} = \a $$
-
-Multiplying through by $e^{2c^*}$ yields a quadratic in $e^{2c^*}$:
-
-$$ C_2 e^{4c^*} + (a-1) e^{2c^*} + C_3 = 0 $$
-
-Using the quadratic formula, we get two solutions to this equation.
+%
+%\begin{equation}
+%C_4 = \begin{cases}
+%\Cfourcaseone & \a,\b \leq \frac{1}{2} \\
+%\Cfourcasetwo & \a\leq\frac{1}{2}<\b \\
+%\Cfourcasethree & \frac{1}{2}<\a,\b
+%\end{cases} \end{equation}
+%
+%To find $c^*$, we can now condition on the values of $w_2(x_\a)$ and $w_2(x_\b)$.
+%
+%\begin{enumerate}[{Case} 1.]
+%\item If $w_2(x_\alpha)=C_4e^{-x_\a}>\a$, then $2c^*$ lies on the third piece of \eqref{w2laplace}. Hence the mean wave speed is given by $c^*=\frac{1}{2}\ln(\frac{C_4}{\a})$.
+%
+%\item If $w_2(x_\a)=C_4e^{-x_\a}\leq\a$ and $w_2(x_\b)=\m+C_1e^{x_\b}\geq\a$, then we solve the equation
+%
+%$$ 1 - C_2e^{2c^*} - C_3e^{-2c^*} = \a $$
+%
+%Multiplying through by $e^{2c^*}$ yields a quadratic in $e^{2c^*}$:
+%
+%$$ C_2 e^{4c^*} + (a-1) e^{2c^*} + C_3 = 0 $$
+%
+%Using the quadratic formula, we get two solutions to this equation.
 To determine which is correct, note that $w_2'(2c^*)$ must be negative.
@@
 Thus,
-$$ c^* = \frac{1}{2} \ln \left( \frac{1-\a + \sqrt{(1-\a)^2 - 4C_2C_3}}{2C_2} \right) $$
-
-\item If  $w_2(x_\b)=\m+C_1e^{x_\b}<\a$, we have
-
-$$ \m + C_1 e^{2c^*} = \a $$
-implies
-$$ c^* = \frac{1}{2} \ln \frac{\a-\m}{C_1} $$
-\end{enumerate}
-
-Our general formula is thus
-\begin{equation}
-c^* = \begin{cases}
-\frac{1}{2} \ln \left( \frac{C_4}{\a} \right) & \a<C_4e^{-x_\a} \\
-\frac{1}{2} \ln \left( \frac{1-\a + \sqrt{(1-\a)^2 - 4C_2C_3}}{2C_2} \right) & C_4e^{-x_\a}<\a<\m+C_1e^{x_\b} \\
-\frac{1}{2} \ln \left( \frac{\a-\m}{C_1}\right) & \a>\m+C_1e^{x_\b}
-\end{cases}
-\end{equation}
-We can write this formula more explicitly depending on the signs of $\a-\frac{1}{2}$ and $\b-\frac{1}{2}$ respectively.
+%$$ c^* = \frac{1}{2} \ln \left( \frac{1-\a + \sqrt{(1-\a)^2 - 4C_2C_3}}{2C_2} \right) $$
+%
+%\item If  $w_2(x_\b)=\m+C_1e^{x_\b}<\a$, we have
+%
+%$$ \m + C_1 e^{2c^*} = \a $$
+%implies
+%$$ c^* = \frac{1}{2} \ln \frac{\a-\m}{C_1} $$
+%\end{enumerate}
+%
+%Our general formula is thus
+%\begin{equation}
+%c^* = \begin{cases}
+%\frac{1}{2} \ln \left( \frac{C_4}{\a} \right) & \a<C_4e^{-x_\a} \\
+%\frac{1}{2} \ln \left( \frac{1-\a + \sqrt{(1-\a)^2 - 4C_2C_3}}{2C_2} \right) & C_4e^{-x_\a}<\a<\m+C_1e^{x_\b} \\
+%\frac{1}{2} \ln \left( \frac{\a-\m}{C_1}\right) & \a>\m+C_1e^{x_\b}
+%\end{cases}
+%\end{equation}
+%We can write this formula more explicitly depending on the signs of $\a-\frac{1}{2}$ and $\b-\frac{1}{2}$ respectively.
 %Let $c_1$ and $c_2$ denote the intermediate wave speeds measured at some threshold $0<h<m$.
@@
 
+Our formula can be written more explicitly based on the values of $\a$ and $\b$:
 \begin{enumerate}[{Case} 1.]
@@
 
+\begin{figure}[h!] 
+\centering
+  \caption{The shaded region $R$ indicates all pairs $(\a,\b)$ such that the condition in Theorem 2.1 holds for $\m=0.6$, and the line $\b=2\a$ is drawn in red.
+The region $R_1$ contains all pairs $(\a,\b)$ such that the traveling wave has constant speed, and $R_2$ contains all pairs such that the traveling wave has oscillating speed.}
+\label{fig4}
+  \includegraphics[width=.5\linewidth]{figures/fig4.png}
+\end{figure}
+
 The regions in the parameter space where oscillating spreading speed exists can be determined as follows: for any fixed choice of $(n_1,n_2)$, with $0<n_1<n_2$, let $R$ be the set of pairs $(a,b)\in\mathbf R^2$ such that the hypothesis of Theorem 2.1 holds.
@@
 
-\begin{proof}[Proof of Proposition \ref{prop1}]
-
-Let $u(x)$ be non-negative, continuous, and bounded.
-
-\begin{enumerate}[(i.)]
-\item For $t\in\mathbb R$, let $T^t$ denote the translation operator defined $T^t[u](x) = u(x+t)$. Then,
-\begin{equation} \begin{aligned}
-Q[T^t[u]](x) &= 
-\int_{-\infty}^{\infty} k(x-y) g(T^t[u](y)) \, dy \\
-&= \int_{-\infty}^{\infty} k(x-y) g(u(y+t)) \, dy
-\end{aligned} \end{equation}
-Let $z=y+t$.
-\begin{equation} \begin{aligned}
-Q[T^t[u]](x)
-&= \int_{-\infty}^{\infty} k(x-z+t) g(u(z)) \, dz \\
-&= Q[u](x+t) \\
-&= T^t[Q[u]](x)
-\end{aligned} \end{equation}
-
-\item 
-Suppose $\lim_{x\to\infty}u(x)=\ell$.
-
-\end{enumerate}
-
-\end{proof}
-
-\begin{lem}
+%\begin{proof}[Proof of Proposition \ref{prop1}]
+%
+%Let $u(x)$ be non-negative, continuous, and bounded.
+%
+%\begin{enumerate}[(i.)]
+%\item For $t\in\mathbb R$, let $T^t$ denote the translation operator defined $T^t[u](x) = u(x+t)$. Then,
+%\begin{equation} \begin{aligned}
+%Q[T^t[u]](x) &= 
+%\int_{-\infty}^{\infty} k(x-y) g(T^t[u](y)) \, dy \\
+%&= \int_{-\infty}^{\infty} k(x-y) g(u(y+t)) \, dy
+%\end{aligned} \end{equation}
+%Let $z=y+t$.
+%\begin{equation} \begin{aligned}
+%Q[T^t[u]](x)
+%&= \int_{-\infty}^{\infty} k(x-z+t) g(u(z)) \, dz \\
+%&= Q[u](x+t) \\
+%&= T^t[Q[u]](x)
+%\end{aligned} \end{equation}
+%
+%\item 
+%Suppose $\lim_{x\to\infty}u(x)=\ell$. 
+%
+%\end{enumerate}
+%
+%\end{proof}
+
+\begin{lem} \label{laplaceproof}
 The Laplace kernel \eqref{laplacekernel} satisfies hypothesis (H4).
@@
 \begin{proof}
-let $f=f_{m,y}$ be the scalar function of $x$ with two parameters $y\in\mathbb R$ and $\mu\in(0,1)$ defined by
-$$ f(x)= f_{m,y}(x) = \frac{1}{2} e^{-|x|} - \frac{\mu}{2}e^{-|x-y|} $$
-
-If $y=0$, then $f$ has no zero-crossings, since $f_{m,0}(x)=\frac{1-\mu}{2}e^{-|x|}$ is strictly positive.
-If $y$ is nonzero, then one can easily check the symmetry relation $f_{m,-y}(x)=f_{m,y}(-x)$.
-Since the number of zero-crossings are invariant with respect to a reflection about the vertical axis, we can assume without loss of generality $y>0$.
-
-Under this assumption, $f$ is strictly increasing on $(-\infty,0)$, and strictly decreasing on $(0,y)$. The behavior on $(y,\infty)$ is determined by the sign of $e^{-y}-m$. There are three cases:
-
-\begin{enumerate}
-\item if $y<\ln\frac{1}{m}$, then $f$ is decreasing on $(0,\infty)$, hence has no zero-crossings;
-\item if $y>\ln\frac{1}{m}$, then $f$ has a unique zero-crossing at $x=\frac{1}{2}(y-\ln(m))$;
-\item if $y=\ln\frac{1}{m}$, then $f$ vanishes on $(y,\infty)$, hence it has no zero-crossings.
+Let $k(x)=\frac{1}{2}e^{-|x|}$. For $a \in \mathbb R$ and $\lambda \in (0,1)$, define
+\begin{equation}
+f_{a,\lambda}(x)= \frac{1}{2} e^{-|x|} - \frac{\lambda}{2}e^{-|x-a|}.
+\end{equation}
+
+If $a=0$, then $f$ has no zero-crossings, since $f_{0,\lambda}(x)=\frac{1-\lambda}{2}e^{-|x|}$ is strictly positive.
+If $a$ is nonzero, then one can easily check the symmetry relation $f_{-a,\lambda}(x)=f_{\lambda,a}(-x)$.
+Since the number of zero-crossings are invariant with respect to a reflection about the vertical axis, we can assume without loss of generality $a>0$.
+
+Under this assumption, $f$ is strictly increasing on $(-\infty,0)$, and strictly decreasing on $(0,a)$. The behavior on $(a,\infty)$ can be determined in three cases:
+
+\begin{enumerate}[{Case} 1.)]
+\item if $a<\ln\frac{1}{\lambda}$, then $f$ is decreasing on $(0,\infty)$, hence has no zero-crossings;
+\item if $a>\ln\frac{1}{\lambda}$, then $f$ has a unique zero-crossing at $x=\frac{1}{2}(a-\ln\lambda)$;
+\item if $a=\ln\frac{1}{\lambda}$, then $f$ vanishes on $(a,\infty)$, hence it has no zero-crossings.
 \end{enumerate}
@@
 
-\begin{lem}
+\begin{lem}\label{laplacebound}
 If $k(x)$ is given by the Laplace kernel, then $w_1$ and $w_2$ form a periodic traveling wave solution if $C_1\leq 0$, or if $C_1>0$ and $w_2\left(\ln\sqrt\frac{C_3}{C_2}\right)\leq b$.
@@
 \begin{proof}
-Let $y\in\mathbb R$ and $\mu\in(0,1)$. Then
+Let $a\in\mathbb R$ and $\mu\in(0,1)$. Then
 \begin{equation} \begin{aligned}
-k(x)-\mu k(x-y) &= \frac{1}{\sqrt{2\pi}} \left( e^{-\frac{x^2}{2}} - \mu e^{-\frac{-(x-y)^2}{2}} \right) \\
-&= \frac{1}{\sqrt{2\pi}} e^{-\frac{x^2}{2}} \left( 1 - \mu e^{\frac{2xy-y^2}{2}} \right)
+k(x)-\mu k(x-a) &= \frac{1}{\sqrt{2\pi}} \left( e^{-\frac{x^2}{2}} - \mu e^{-\frac{-(x-a)^2}{2}} \right) \\
+&= \frac{1}{\sqrt{2\pi}} e^{-\frac{x^2}{2}} \left( 1 - \mu e^{\frac{2ax-a^2}{2}} \right)
 \end{aligned} \end{equation}
-This expression has a unique zero at $x=\frac{y^2-2\ln(\mu)}{2y}$, so the number of zero-crossings is at most one.
+This expression has a unique zero at $x=\frac{y^2-2\ln(\mu)}{2a}$, so the number of zero-crossings is at most one.
 \end{proof}

### 2021-07-04 paper_draft4.tex
updates

--- 2021-06-23 paper_draft3.tex
@@
 \usepackage{hyperref}
-\usepackage{geometry}
+%\usepackage{geometry}
 \usepackage{graphicx}
@@
 
-\section{Periodic traveling waves}
+\section{Results}
+
+\subsection{Periodic traveling waves}
 
@@
 \begin{enumerate}[(H1)]
-\item $k$ is a non-negative Lebesgue-integrable function with $\int_{-\infty}^{\infty} k(x) \, dx = 1$;
+\item $k$ is a non-negative, Lebesgue-integrable function with $\int_{-\infty}^{\infty} k(x) \, dx = 1$;
 
@@
 \end{enumerate}
+
+Hypothesis (H1) indicates that the dispersal kernel accounts for all individuals, while hypothesis (H2) guarantees the disperal process is symmetric.
+
 %\end{hyp}
@@
 \begin{equation} \label{w2}
-w_2(x) := Q[w_1](x) = \int_{-\infty}^{\infty} k(y) g(w_1(x-y)) \, dy 
-\end{equation}
-
-Hypothesis (H1) implies $w_1$ and $w_2$ have well-defined limits at $\pm\infty$ given by $w_1(\infty)=w_2(\infty)=0$, $w_1(-\infty)=1$, and $w_2(-\infty)=\m$.
-Furthermore, $w_1$ is monotonically decreasing, while $w_2$ may be non-monotonic.
-
-\begin{lem} \label{lemma1}
-If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then there exists unique $c^*\in\mathbb R$ such that $Q[w_2](x)=w_1(x-2c^*)$ for all $x\in\mathbb R$.
+w_2(x) := Q[w_1](x+c^*) = \int_{-\infty}^{\infty} k(y) g(w_1(x+c^*-y)) \, dy 
+\end{equation} 
+with $c^* \in \mathbb R$ a constant given by
+\begin{equation}
+c^*=\frac{1}{2}\sup\{x\in\mathbb R\mid Q[w_1](x)\geq\a\}
+\end{equation}
+
+Note that $c^*$ is finite by the intermediate value theorem since $Q[w_1](\infty)=0$ and $Q[w_1](-\infty)=\m$ with $0<\a<\m$.
+
+\begin{lem} \label{lemma0}
+$w_1(x)$ is monotone, while $w_2(x)$ has at most one turning point.
 \end{lem}
 
-\begin{proof} Let $x_\a=\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}$.
+\begin{proof}
+The monotonicity of $w_1$ follows since $w_1'(x)=-k(x)\leq 0$ by hypothesis (H1).
+To count the turning points of $w_2$, let $x_\a=\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}$.
 Since $w_1$ is monotone, it follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$.
@@
 \begin{aligned}
-Q[w_1](x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
+Q[w_1](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
 &= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \int_{x_\b}^{x_\a} k(x-y) \, dy \\
-&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
+%&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
 &= \int_{x-x_\a}^{\infty} k(y) \, dy - (1-\m) \int_{x-x_\b}^{\infty} k(y) \, dy
@@
 \begin{equation}\label{dw2dx}
-\frac{dw_2}{dx} = -k(x-x_\a) + (1-\m)k(x-x_\b)
-\end{equation}
-
-From hypothesis (H4), we can conclude that \eqref{dw2dx} has at most one zero-crossing, hence $w_2(x)$ has at most one turning point. This leaves two cases:
-\begin{enumerate}[{Case} 1.]
-\item If $w_2$ has no turning points, it must be monotonically decreasing.
-\item If $w_2$ has a single turning point $x^*$, then $w_2(x)$ is increasing on $(-\infty,x^*)$ and decreasing on $(x^*,\infty)$, with $\m \leq w_2(x^*)\leq \b$.
-\end{enumerate}
-
-In both cases, $w_2(x)$ has a well-defined right inverse on the open interval $(0,\m)$. Since $0<\a<\m$, let
-\begin{equation}
-c^*=\frac{1}{2}\sup\{x\in\mathbb R\mid w_2(x)\geq\a\}
-\end{equation}
-
-It follows that $w_2(x)\geq\a$ for $x\leq 2c^*$ and $w_2(x)<\alpha$ for $x>2c^*$.
+\frac{d}{dx}Q[w_1] = -k(x-x_\a) + (1-\m)k(x-x_\b)
+\end{equation}
+
+From hypothesis (H4), we can conclude that \eqref{dw2dx} has at most one zero-crossing, hence $w_2(x)$ has at most one turning point.
+\end{proof}
+
+%
+%Hypothesis (H1) implies $w_1$ and $w_2$ have well-defined limits at $\pm\infty$ given by $w_1(\infty)=w_2(\infty)=0$, $w_1(-\infty)=1$, and $w_2(-\infty)=\m$.
+Furthermore, $w_1$ is monotonically decreasing, while $w_2$ may be non-monotonic.
+
+%\begin{lem} \label{lemma1}
+%If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then $Q[w_2](x)=w_1(x-c^*)$ for all $x\in\mathbb R$.
+%\end{lem}
+
+\begin{lem} \label{lemma1}
+If $ ||w_2||_\infty \leq \b$, then $Q[w_2](x)=w_1(x-c^*)$ for all $x\in\mathbb R$.
+\end{lem}
+
+\begin{proof}
+By Lemma \ref{lemma0}, $w_2(x)$ has either zero or one turning point(s).
+In the first case, $w_2(x)$ is monotonically decreasing and satisfies $w_2(x) \geq \a$ for $x \leq c^*$ and $w_2(x) < \a$ for $x > c^*$.
+In the second case, $w_2(x)$ has a unique turning point $x_0 \in \mathbb R$; it follows that $w_2(x)$ is monotonically increasing on $(-\infty,x_0)$ and monotonically decreasing on $(x_0,\infty)$, and $x_0$ is a global maximum.
+By the assumption $w_2(x)\leq\beta$ for all $x$, we have $w_2(x_0)\leq\beta$.
+It follows that $c^* \in (x_0,\infty)$, and $w_2(x)$ satisfies $g(w_2(x))=1$ for $x<c^*$ and $g(w_2(x)) = 0$ for $x>c^*$.
+In both cases, we have
+
+%Let $x_\a=\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}$.
+Since $w_1$ is monotone, it follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$.
+Applying the integro-difference operator to $w_1$ yields
+%\begin{equation} \label{qw1calculation}
+%\begin{aligned}
+%Q[w_1](x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
+%&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \int_{x_\b}^{x_\a} k(x-y) \, dy \\
+%&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
+%&= \int_{x-x_\a}^{\infty} k(y) \, dy - (1-\m) \int_{x-x_\b}^{\infty} k(y) \, dy
+%\end{aligned} \end{equation}
+%
+%Taking the derivative with respect to $x$, we find
+%\begin{equation}\label{dw2dx}
+%\frac{d}{dx}Q[w_1] = -k(x-x_\a) + (1-\m)k(x-x_\b)
+%\end{equation}
+
+%From hypothesis (H4), we can conclude that \eqref{dw2dx} has at most one zero-crossing, hence $w_2(x)$ has at most one turning point. This leaves two cases:
+%\begin{enumerate}[{Case} 1.]
+%\item If $w_2$ has no turning points, it must be monotonically decreasing.
+%\item If $w_2$ has a single turning point $x^*$, then $w_2(x)$ is increasing on $(-\infty,x^*)$ and decreasing on $(x^*,\infty)$, with $\m \leq w_2(x^*)\leq \b$.
+%\end{enumerate}
+%
+%In both cases, $w_2(x)$ has a well-defined right inverse on the open interval $(0,\m)$. Since $0<\a<\m$, let
+%\begin{equation}
+%c^*=\frac{1}{2}\sup\{x\in\mathbb R\mid w_2(x)\geq\a\}
+%\end{equation}
+
+%It follows that $w_2(x)\geq\a$ for $x\leq 2c^*$ and $w_2(x)<\alpha$ for $x>2c^*$.
 Along with the assumption that $\sup_{x\in\mathbb R}w_2(x)\leq\b$, we can apply the integro-difference operator once more:
@@
 Q[w_2](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_2(y)) \, dy \\
-&= \int_{-\infty}^{2c^*} k(x-y) \, dy \\
-&= \int_{x-2c^*}^{\infty} k(y) \, dy &= w_1(x-2c^*).
+&= \int_{-\infty}^{c^*} k(x-y) \, dy \\
+&= \int_{x-c^*}^{\infty} k(y) \, dy \\
+&= w_1(x-c^*).
 \end{aligned} \end{equation}
@@
   \centering
-  \includegraphics[width=.8\linewidth]{figures/fig2A.png}
+  \includegraphics[width=.9\linewidth]{figures/fig2A.png}
   \label{fig:sub1}
@@
   \centering
-  \includegraphics[width=.8\linewidth]{figures/fig2B.png}
+  \includegraphics[width=.9\linewidth]{figures/fig2B.png}
   \label{fig:sub2}
 \end{subfigure}
-\caption{Plots of $w_1(x)$ (left) and $w_2(x)$ (right) with the Laplace dispersal kernel and growth parameters $\alpha=0.3$, $\mu=0.5$, and $\beta=0.8$}
+\caption{Plots of $w_1(x)$ (left) and $w_2(x)$ (right) with the Laplace dispersal kernel $k(x)=\frac{1}{2}e^{-|x|}$ and growth parameters $\alpha=0.3$, $\mu=0.5$, and $\beta=0.8$.}
 \label{fig:test}
@@
 \begin{thm} \label{theorem1}
-If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then the recurrence \eqref{q} has a periodic traveling wave solution $(u_n)_{n=0}^{\infty}$ satisfying
+If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then equation \eqref{q} has a periodic traveling wave solution given by %$(u_n)_{n=0}^{\infty}$ satisfying
 %\begin{equation} \label{ptw}
@@
 \begin{equation} \label{ptw}
-\begin{aligned}
-u_{2n}(x) &= w_1(x-2nc^*) \\
-u_{2n+1}(x) &= w_2(x-2nc^*)
-\end{aligned}
+u_n(x) = \begin{cases}
+w_1(x-nc^*) & n \text{ even} \\
+w_2(x-nc^*) & n \text{ odd}
+\end{cases}
 \end{equation}
@@
 It suffices to show that equation \eqref{ptw} satisfies $u_{n+1}=Q[u_n]$ for all $n \geq 0$.
-For convenience, we will switch the index and consider the cases $u_{2n}$ and $u_{2n+1}$ separately.
+If $n$ is even, then $n+1$ is odd, so $u_n(x)=w_1(x-nc^*)$ and $u_{n+1}(x)=w_2(x-nc^*-c^*)$.
+Applying the integro-difference operator, we obtain
+\begin{equation} \begin{aligned}
+Q[u_n](x) &= Q[w_1](x-nc^*) \\
+&= w_2(x-nc^*-c^*) \\
+&= u_{n+1}(x)
+\end{aligned} \end{equation}
+by \eqref{w2}. On the other hand, if $n$ is odd, then $n+1$ is even, so $u_n(x)=w_2(x-nc^*)$ and $u_{n+1}(x)=w_1(x-nc^*-c^*)$. Applying the operator, we get
+\begin{equation} \begin{aligned}
+Q[u_n](x) &= Q[w_2](x-nc^*) \\
+&= Q^2[w_1](x-nc^*+c^*) \\
+&= w_1(x-nc^*-c^*) \\
+&= u_{n+1}(x)
+\end{aligned} \end{equation}
+by Lemma \ref{lemma1}.
+\end{proof}
+
+%For convenience, we will switch the index and consider the cases $u_{2n}$ and $u_{2n+1}$ separately.
 The basic case, $u_1 = Q[u_0]$, follows immediately from definition \ref{w2}.
@@
 Next, we have $u_2(x)=w_1(x-2c^*)$, which follows by Lemma \ref{lemma1}.
-
-For the inductive step, suppose $u_{2n+1}=Q[u_{2n}]$ and $u_{2n+2}=Q[u_{2n+1}]$ for some $n\geq 0$. We only need to show $u_{2n+3}=Q[u_{2n+2}]$. We have
-\begin{equation} \begin{aligned}
-u_{2n+3}(x) &= w_2(x-2nc^*-2c^*) \\
-&= Q^2[w_2](x-2nc^*) \\
-&= Q^2[u_{2n+1}](x) \\ 
-&= Q[u_{2n+2}](x)
-\end{aligned} \end{equation}
-\end{proof}
+%
+%For the inductive step, suppose $u_{2n+1}=Q[u_{2n}]$ and $u_{2n+2}=Q[u_{2n+1}]$ for some $n\geq 0$. We only need to show $u_{2n+3}=Q[u_{2n+2}]$. We have
+%\begin{equation} \begin{aligned}
+%u_{2n+3}(x) &= w_2(x-2nc^*-2c^*) \\
+%&= Q^2[w_2](x-2nc^*) \\
+%&= Q^2[u_{2n+1}](x) \\ 
+%&= Q[u_{2n+2}](x)
+%\end{aligned} \end{equation}
+% \end{proof}
 
@@
 \label{fig3}
-  \includegraphics{figures/fig3.png}
+  \includegraphics[width=.8\linewidth]{figures/fig3.png}
 \end{figure}
@@
 &= \lim_{n\to\infty}\inf_{x<-2n\epsilon}w_2(x) \\
-&= \liminf_{x\to-\infty}w_2(x) \\ &= m.
+&= \liminf_{x\to-\infty}w_2(x) \\ &= \m.
 \end{aligned} \end{equation}
@@
 
+\subsection{Compactly supported kernels}
+
 The next theorem concerns the spreading behavior of solutions to the IDE \eqref{q} with compactly supported initial data.
@@
 
+\begin{lem}
+Suppose $k(x)$ has support $[-\sigma,\sigma]$ and $c^*\geq0$.
+
+\begin{enumerate}
+\item If $r \geq \sigma - x_\b$, then $Q[w_1](|x|-r) = w_2(|x|-r-c^*)$.
+
+\item 
+\end{enumerate}
+\end{lem}
+
+\begin{proof}
+\begin{enumerate}
+\item 
+Let $u(x) = w_1(|x|-r)$.
+Assuming $r+x_\b \geq 0$, i.e.
+$r \geq -x_\b$, we have $g(u(x)) = \m$ for $|x| < r+x_\b$, $g(u(x)) = 1$ for $r+x_\b \leq x \leq r+x_\a$, and $g(u(x)) = 0 $ for $x > r+x_\a$.
+Note that $g(u(x)) = g(w_1(x-r))$ for $x \geq -r-x_\b$.
+Applying the convolution operator, $Q[u](x) = Q[w_1](x-r)$ for $x \geq -r-x_\b+\sigma$.
+Assuming $r \geq \sigma - x_\b$, this shows $Q[u](x) = w_2(x-r-c^*)$ for $x \geq 0$.
+By the symmetry of $k(x)$, we have $Q[u](x) = w_2(|x|-r-c^*)$.
+
+\item 
+Let $u(x) = w_2(|x|-r)$.
+Assuming $r+x_\b \geq 0$, i.e.
+$r \geq -x_\b$, we have $g(u(x)) = \m$ for $|x| < r+x_\b$, $g(u(x)) = 1$ for $r+x_\b \leq x \leq r+x_\a$, and $g(u(x)) = 0 $ for $x > r+x_\a$.
+Note that $g(u(x)) = g(w_1(x-r))$ for $x \geq -r-x_\b$.
+Applying the convolution operator, $Q[u](x) = Q[w_1](x-r)$ for $x \geq -r-x_\b+\sigma$.
+Assuming $r \geq \sigma - x_\b$, this shows $Q[u](x) = w_2(x-r-c^*)$ for $x \geq 0$.
+By the symmetry of $k(x)$, we have $Q[u](x) = w_2(|x|-r-c^*)$.
+\end{enumerate}
+\end{proof}
+
 \begin{thm} Suppose $k(x)$ has compact support and $\sup_{x\in\mathbb R}w_2(x)\leq \b$.
-Let $u_0(x)$ be a non-negative continuous function, and let $A=\{x\in\mathbb R:\a\leq u_0(x)\leq \b\}$.
-If $A$ is connected with sufficiently large radius and $c^* \geq 0$, then the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$ spreads with speed $c^*$, i.e.
+Let $u_0(x)$ be non-negative and continuous function, and suppose $\a \leq u_0(x) \leq \b$ for $|x| \leq r$ and $u_0(x) < \a$ otherwise, for some $r > 0$.
+If $r$ is sufficiently large and $c^* \geq 0$, then the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$ spreads with speed $c^*$, i.e.
 \begin{equation}
@@
 
+\begin{thm} Suppose $k(x)$ has compact support and $||w_2||_\infty \leq \b$. If $c^* \geq 0$ and $r$ is sufficiently large, then equation \eqref{q} has a periodic spreading solution given by
+\begin{equation} \label{compactptw}
+u_n(x) = \begin{cases}
+w_1(|x|-r-nc^*) & n \text{ even} \\
+w_2(|x|-r-nc^*) & n \text{ odd}
+\end{cases}
+\end{equation}
+for all $n\geq 0$.
+\end{thm}
+
 \begin{proof}
-By the translation invariance property of $Q$, we may assume without loss of generality $A=[-r,r]$, for some $r>0$.
+As in the proof of Theorem \ref{theorem1}, it suffices to show $u_{n+1}=Q[u_n]$ for all $n\geq 0$.
+If $n$ is even, we have $u_n(x)=w_1(|x|-r-nc^*)$.
+Assuming $r \geq \sigma$ and $c^* \geq 0$, this implies $g(u_n(x)) = 0$ for $|x| > r+nc^*+x_\a$, $g(u_n(x))=1$ for $r+nc^*+x_\b\leq |x|\leq r+nc^*+x_\a$, and $g(u_n(x))=\m$ for $|x|<r+nc^*+x_\b$.
+Note that $g(u_n(x)) = g(w_1(x-r-nc^*))$ for $x \geq -r-nc^*-x_\b$.
+Applying the convolution operator, we have $Q[u_n](x) = Q[w_1](x-r-nc^*)$ for $x \geq -r-nc^*-x_\b+\sigma$.
+Assuming $r \geq \sigma - x_\b$, it follows that $Q[u_n](x) = Q[w_1](x-r-nc^*)$ for $x \geq 0$.
+By hypothesis (H2), $k(x)$ is an even function, thus $Q[u_n](-x) = Q[u_n](x)$, hence $Q[u_n](x) = Q[w_1](|x|-r-nc^*)$ for all $x \in \mathbb R$, i.e.
+$u_{n+1}(x) = w_2(|x|-r-nc^*-c^*)$.
+Note that the preceding calculation requires $r \geq \max\{\sigma,\sigma-x_\b\}$; a sufficient condition is $r \geq 2\sigma$.
+
+If $n$ is odd, then $u_n(x)=w_2(|x|-r-nc^*)$, and for $r\geq0$ and $c^*\geq 0$ it follows that $g(u_n(x)) = 0$ for $|x| > r+nc^*+c^*$ and $g(u_n(x))=1$ for $|x| \leq r+nc^*+c^*$.
+
+UNFIN
+\end{proof}
+
+%
+%We apply induction on $n$.
+For the basis case, it is sufficient to show $u_1(x) = w_1(|x|-r)$ for all $x$.
+It follows from the definition of $u_0(x)$ that $g(u_0(x))=1$ for $|x|\leq r$ and $g(u_0(x))=0$ otherwise.
+Assuming $r \geq \frac{\sigma}{2}$, we have $u_1(x)=Q[u_0](x)=w_1(x-r)$ for $x\geq 0$.
+By hypothesis (H2), $k(x)$ is an even function, so $u_1(x)=u_1(-x)$, i.e.
+$u_1(x)=w_1(-x+r)=w_1(x-r)$ for $x<0$.
+This proves $u_1(x)=w_1(|x|-r)$ for all $x$.
+%
+%For the inductive step, suppose equation \eqref{compactptw} holds for some $n\geq0$. If $n$ is even, the inductive hypothesis yields $u_{n+1}(x)=w_1(|x|-r-nc^*)$.
+%\end{proof}
+%
+%\begin{proof}
+%By the translation invariance property of $Q$, we may assume without loss of generality $A=[-r,r]$, for some $r>0$.
 It follows that $u_0(x)<\a$ for $|x|>r$ and $\a\leq u_0(x)\leq\b$ for $|x| \leq r$.
 Furthermore, there exists $\sigma>0$ such that $k(x)>0$ if and only if $|x|<\sigma$.
-
 Assuming $r \geq \frac{\sigma}{2}$, we have
-\begin{equation} \begin{aligned}
-u_1(x) = Q[u_0](x) &= \int_{-r}^{r} k(x-y) \, dy \\
-&= \begin{cases}
-w_1(x-r) & x \geq 0 \\
-w_1(-x+r) & x< 0
-\end{cases}
-\end{aligned}  \end{equation}
-
-Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. Then, applying the growth function, we have
-\begin{equation} g(u_1(x)) = \begin{cases}
-0 & x<-r-x_\a \\
-1 & -r-x_\a \leq x \leq -r-x_\b \\
-m & -r-x_\b < x < r+x_\b \\
-1 & r+x_\b \leq x \leq r+x_\a \\
-0 & x > r+x_\a
-\end{cases}
-\end{equation}
-Note that $g(u_1(x))=g(w_1(x))$ for all $x >-r-x_\b$.
+%\begin{equation} \begin{aligned}
+%u_1(x) = Q[u_0](x) &= \int_{-r}^{r} k(x-y) \, dy \\
+%&= \begin{cases}
+%w_1(x-r) & x \geq 0 \\
+%w_1(-x+r) & x< 0
+%\end{cases}
+%\end{aligned}  \end{equation}
+%
+%Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. Then, applying the growth function, we have
+%\begin{equation} g(u_1(x)) = \begin{cases}
+%0 & x<-r-x_\a \\
+%1 & -r-x_\a \leq x \leq -r-x_\b \\
+%m & -r-x_\b < x < r+x_\b \\
+%1 & r+x_\b \leq x \leq r+x_\a \\
+%0 & x > r+x_\a
+%\end{cases}
+%\end{equation}
+%Note that $g(u_1(x))=g(w_1(x))$ for all $x >-r-x_\b$.
 Thus $Q[u_1](x)=(k*(g\circ u_1))(x)=(k*(g\circ w_1))(x)=Q[w_1](x)$ for all $x>-r-x_\b+\sigma$.
 If we assume $r \geq x_\b+\sigma$, then $u_2(x)=Q[u_1](x)=Q[w_1](x-r)=w_2(x-r)$ for $x>0$.
-
-By symmetry of the integro-difference operator, $Q[u_1](x) = Q[w_1](-x+r)$ for $x<0$. Thus,
-
-\begin{equation}
-u_2(x) = Q[u_1](x) = \begin{cases}
-w_2(x-r) & x \geq 0 \\
-w_2(-x+r) & x < 0 
-\end{cases}
-\end{equation}
-Since $c^*\geq 0$, we have
-\begin{equation}
-g(u_2(x)) = \begin{cases}
-0 & x < -r-2c^* \\
-1 & -r-2c^* \leq x \leq r+2c^* \\
-0 & x > r+2c^* 
-\end{cases}
-\end{equation}
-
+By symmetry of the integro-difference operator, $Q[u_1](x) = Q[w_1](-x+r)$ for $x<0$.
 Thus,
-\begin{equation}
-u_3(x) = Q[u_2](x) = \begin{cases}
-w_1(x-r-2c^*) & x \geq 0 \\
-w_1(-x+r+2c^*) & x < 0 
-\end{cases}
-\end{equation}
-
-The preceding argument can be repeated inductively to obtain
-\begin{equation}
-u_{2n+1}(x) = w_1(|x|-r-2nc^*)
-\end{equation}
-and
-\begin{equation}
-u_{2n+2}(x) = w_2(|x|-r-2nc^*)
-\end{equation}
-for all $n\geq 0$.
-\end{proof}
+%
+%\begin{equation}
+%u_2(x) = Q[u_1](x) = \begin{cases}
+%w_2(x-r) & x \geq 0 \\
+%w_2(-x+r) & x < 0 
+%\end{cases}
+%\end{equation}
+%Since $c^*\geq 0$, we have
+%\begin{equation}
+%g(u_2(x)) = \begin{cases}
+%0 & x < -r-2c^* \\
+%1 & -r-2c^* \leq x \leq r+2c^* \\
+%0 & x > r+2c^* 
+%\end{cases}
+%\end{equation}
+%
+%Thus,
+%\begin{equation}
+%u_3(x) = Q[u_2](x) = \begin{cases}
+%w_1(x-r-2c^*) & x \geq 0 \\
+%w_1(-x+r+2c^*) & x < 0 
+%\end{cases}
+%\end{equation}
+%
+%The preceding argument can be repeated inductively to obtain
+%\begin{equation}
+%u_{2n+1}(x) = w_1(|x|-r-2nc^*)
+%\end{equation}
+%and
+%\begin{equation}
+%u_{2n+2}(x) = w_2(|x|-r-2nc^*)
+%\end{equation}
+%for all $n\geq 0$.
+%\end{proof}
 
@@
 \end{rem}
+
+\subsection{Variability in wave speed}
 

### 2021-07-04 paper_draft_bare.tex
updates

--- 2021-07-04 paper_draft4.tex
@@
 \usepackage{subcaption}
+
+%\usepackage{newpxtext,newpxmath}
+\usepackage{multicol}
 
@@
 {\bf AMS Subject Classification:} 92D40, 92D25.
+
+%\begin{multicols}{1}
 
@@
 
-Piecewise constant growth functions and uniform distributions have been used in the studies of integro-difference equations; see for example~\cite{kot1, lut,otto,  pnas}.
+Piecewise constant growth functions have been used in the studies of integro-difference equations; see for example~\cite{kot1, lut,otto,  pnas}.
 We rigorously construct periodic traveling waves with periodic speeds for (\ref{q}).
@@
 
-\section{Results}
-
-\subsection{Periodic traveling waves}
+%\section{Results}
+\section{Periodic traveling waves}
+%\subsection{Periodic traveling waves}
 
@@
 
-\item  for all $\lambda\in(0,1)$, for all $a\in\mathbb R$, the function $x \mapsto k(x)-\lambda k(x-a)$ has at most one zero-crossing in $\mathbb R$.
+\item  for all $\lambda\in(0,1)$, for all $a\in\mathbb R$, the equation $k(x)=\lambda k(x-a)$ has at most one real solution.
 \end{enumerate}
@@
 \begin{equation} \label{w2}
-w_2(x) := Q[w_1](x+c^*) = \int_{-\infty}^{\infty} k(y) g(w_1(x+c^*-y)) \, dy 
-\end{equation} 
-with $c^* \in \mathbb R$ a constant given by
+w_2(x) = \int_x^\infty \left( k(y-x_\a) - (1-\mu)k(y-x_\b)\right) \, dy 
+\end{equation} 
+where $x_\a,x_\b$ and $c^* \in \mathbb R$ are constants given by
+\begin{equation}
+x_\a =\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}, \quad
+x_\b =\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}
+\end{equation}
+and
 \begin{equation}
@@
 
-\begin{lem} \label{lemma0}
-$w_1(x)$ is monotone, while $w_2(x)$ has at most one turning point.
+\begin{lem} \label{lemma0.5}
+$Q[w_1](x) = w_2(x)$ for all $x\in\mathbb R$.
 \end{lem}
@@
 \begin{proof}
-The monotonicity of $w_1$ follows since $w_1'(x)=-k(x)\leq 0$ by hypothesis (H1).
-To count the turning points of $w_2$, let $x_\a=\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}$.
-Since $w_1$ is monotone, it follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$.
-Applying the integro-difference operator to $w_1$ yields
+$w_1$ is monotonically decreasing with $w_1(-\infty)=1$ and $w_1(\infty)=0$.
+It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$.
+Applying the integro-difference operator yields
 \begin{equation} \label{qw1calculation}
@@
 %&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
-&= \int_{x-x_\a}^{\infty} k(y) \, dy - (1-\m) \int_{x-x_\b}^{\infty} k(y) \, dy
+&= \int_{x-x_\a}^{\infty} k(y) \, dy - (1-\m) \int_{x-x_\b}^{\infty} k(y) \, dy \\
+&= \int_{x}^{\infty} \left(k(y-x_\a)  - (1-\m)k(y-x_\b)\right) \, dy
 \end{aligned} \end{equation}
-
-Taking the derivative with respect to $x$, we find
-\begin{equation}\label{dw2dx}
-\frac{d}{dx}Q[w_1] = -k(x-x_\a) + (1-\m)k(x-x_\b)
-\end{equation}
-
-From hypothesis (H4), we can conclude that \eqref{dw2dx} has at most one zero-crossing, hence $w_2(x)$ has at most one turning point.
+%It can now be seen that replacing $x$ with $x-c^*$ in equation \eqref{w2} produces \eqref{qw1calculation}.
 \end{proof}
+
+%
+%\begin{lem} \label{lemma0}
+%$w_1(x)$ is monotone, while $w_2(x)$ has at most one turning point.
+%\end{lem}
+%
+%
+%
+%
+%\begin{proof}
+%The monotonicity of $w_1$ follows since $w_1'(x)=-k(x)\leq 0$ by hypothesis (H1).
+To count the turning points of $w_2$, let $x_\a=\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}$.
+Since $w_1$ is monotone, it follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$.
+Applying the integro-difference operator to $w_1$ yields
+%\begin{equation} \label{qw1calculation}
+%\begin{aligned}
+%Q[w_1](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
+%&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \int_{x_\b}^{x_\a} k(x-y) \, dy \\
+%%&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
+%&= \int_{x-x_\a}^{\infty} k(y) \, dy - (1-\m) \int_{x-x_\b}^{\infty} k(y) \, dy
+%\end{aligned} \end{equation}
+%
+%Taking the derivative with respect to $x$, we find
+%\begin{equation}\label{dw2dx}
+%\frac{d}{dx}Q[w_1] = -k(x-x_\a) + (1-\m)k(x-x_\b)
+%\end{equation}
+%
+%From hypothesis (H4), we can conclude that \eqref{dw2dx} has at most one zero-crossing, hence $w_2(x)$ has at most one turning point.
+%\end{proof}
 
@@
 \end{subfigure}
-\caption{Plots of $w_1(x)$ (left) and $w_2(x)$ (right) with the Laplace dispersal kernel $k(x)=\frac{1}{2}e^{-|x|}$ and growth parameters $\alpha=0.3$, $\mu=0.5$, and $\beta=0.8$.}
+\caption{The shape of the two periodic traveling wave profiles with Laplace dispersal kernel and growth parameters $\alpha=0.3$, $\mu=0.5$, and $\beta=0.8$.}
 \label{fig:test}
@@
 
+%\end{multicols}
+
 \begin{thebibliography}{9}

### 2021-07-04 paper_draftver6.tex
updates

--- 2021-07-04 paper_draft_bare.tex
@@
 \newcommand{\winvb}{{w_1^{-1}(b)}}
-\renewcommand{\a}{\alpha}
-\renewcommand{\b}{\beta}
-\newcommand{\m}{\mu}
+\renewcommand{\a}{a}
+\renewcommand{\b}{b}
+\newcommand{\m}{n_1}
+\newcommand{\mtwo}{n_2}
 
@@
 0, & \text{if } u < \a, \\
-1, & \text{if } \a \leq u \leq \b, \\
+\mtwo, & \text{if } \a \leq u \leq \b, \\
 \m, & \text{if } u > \b,
@@
 \centering
-  \caption{Plot of the growth function $g(u)$ compared to the identity function with growth parameters $\alpha=0.33$, $\beta=0.66$, and $\mu=0.5$.}
+  \caption{Plot of the growth function $g(u)$ compared to the identity function with growth parameters $\a=0.33$, $\b=0.66$, and $\m=0.5$, and $\mtwo=1.0$.}
   \includegraphics[width=.8\linewidth]{figures/fig1.png}
@@
 
-Hypothesis (H1) indicates that the dispersal kernel accounts for all individuals, while hypothesis (H2) guarantees the disperal process is symmetric.
-
 %\end{hyp}
@@
 \begin{equation} \label{w1}
-w_1(x) := \int_x^\infty k(y) \, dy
+w_1(x) := \int_x^\infty \mtwo k(y) \, dy
 \end{equation}
@@
 \begin{equation} \label{w2}
-w_2(x) = \int_x^\infty \left( k(y-x_\a) - (1-\mu)k(y-x_\b)\right) \, dy 
-\end{equation} 
-where $x_\a,x_\b$ and $c^* \in \mathbb R$ are constants given by
-\begin{equation}
-x_\a =\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}, \quad
-x_\b =\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}
+w_2(x) = \int_x^\infty \left( \mtwo k(y-x_\a) - (\mtwo-\m)k(y-x_\b)\right) \, dy 
+\end{equation} 
+where $x_\a$ and $x_\b$ constants constants given by
+\begin{equation}
+x_\a =\sup\left\{x\in\mathbb R\mid \int_{-\infty}^{x} k(y) \, dy \leq \frac{\a}{\mtwo} \right\}, \quad
+x_\b =\sup\left\{x\in\mathbb R\mid \int_{-\infty}^{x} k(y) \, dy \leq \frac{\b}{\mtwo} \right\}
+\end{equation}
+
+\begin{lem} \label{lemmamain}
+If $ || w_2 ||_\infty \leq \b $, then $w_1$ and $w_2$ satisfy
+\begin{equation}
+Q[w_1](x) = w_2(x)
 \end{equation}
@@
 \begin{equation}
-c^*=\frac{1}{2}\sup\{x\in\mathbb R\mid Q[w_1](x)\geq\a\}
-\end{equation}
-
-Note that $c^*$ is finite by the intermediate value theorem since $Q[w_1](\infty)=0$ and $Q[w_1](-\infty)=\m$ with $0<\a<\m$.
-
-\begin{lem} \label{lemma0.5}
-$Q[w_1](x) = w_2(x)$ for all $x\in\mathbb R$.
+Q[w_2](x) = w_1(x-2c^*)
+\end{equation}
+for all $x\in\mathbb R$, where $c^*$ is a constant given by
+\begin{equation}
+c^* = \frac{1}{2} \sup\{x\in\mathbb R\mid w_2(x)\geq \a\}
+\end{equation}
 \end{lem}
 
+%
+%
+%\begin{lem} \label{lemma0.5}
+%$Q[w_1](x) = w_2(x)$ for all $x\in\mathbb R$.
+%\end{lem}
+
 \begin{proof}
-$w_1$ is monotonically decreasing with $w_1(-\infty)=1$ and $w_1(\infty)=0$.
+$w_1$ is monotonically decreasing with $w_1(-\infty)=\mtwo$ and $w_1(\infty)=0$.
 It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$.
+This yields
+\begin{equation}
+g(w_1(x)) = \begin{cases}
+\m & x < x_\b \\
+\mtwo & x_\b \leq x \leq x_\a \\
+0 & x > x_\a
+\end{cases}
+\end{equation}
 Applying the integro-difference operator yields
@@
 \begin{aligned}
-Q[w_1](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
-&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \int_{x_\b}^{x_\a} k(x-y) \, dy \\
+Q[w_1](x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
+&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \mtwo \int_{x_\b}^{x_\a} k(x-y) \, dy \\
 %&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
-&= \int_{x-x_\a}^{\infty} k(y) \, dy - (1-\m) \int_{x-x_\b}^{\infty} k(y) \, dy \\
-&= \int_{x}^{\infty} \left(k(y-x_\a)  - (1-\m)k(y-x_\b)\right) \, dy
+&= \mtwo \int_{x-x_\a}^{\infty} k(y) \, dy - (\mtwo-\m) \int_{x-x_\b}^{\infty} k(y) \, dy \\
+&= \int_{x}^{\infty} \left( \mtwo k(y-x_\a)  - (\mtwo-\m)k(y-x_\b)\right) \, dy
 \end{aligned} \end{equation}
 %It can now be seen that replacing $x$ with $x-c^*$ in equation \eqref{w2} produces \eqref{qw1calculation}.
-\end{proof}
+%\end{proof}
 
@@
 
-\begin{lem} \label{lemma1}
-If $ ||w_2||_\infty \leq \b$, then $Q[w_2](x)=w_1(x-c^*)$ for all $x\in\mathbb R$.
-\end{lem}
-
-\begin{proof}
-By Lemma \ref{lemma0}, $w_2(x)$ has either zero or one turning point(s).
-In the first case, $w_2(x)$ is monotonically decreasing and satisfies $w_2(x) \geq \a$ for $x \leq c^*$ and $w_2(x) < \a$ for $x > c^*$.
+%\begin{lem} \label{lemma1}
+%If $ ||w_2||_\infty \leq \b$, then $Q[w_2](x)=w_1(x-c^*)$ for all $x\in\mathbb R$.
+%\end{lem}
+
+%'\begin{proof}
+By Hypothesis (H4), we have assumed that the integrand on the right hand side has at most one zero.
+We can now proceed in cases.
+$w_2(x)$ has either zero or one turning point(s).
+In the first case, $w_2(x)$ is monotonically decreasing and satisfies $w_2(x) \geq \a$ for $x \leq 2c^*$ and $w_2(x) < \a$ for $x > 2c^*$.
 In the second case, $w_2(x)$ has a unique turning point $x_0 \in \mathbb R$; it follows that $w_2(x)$ is monotonically increasing on $(-\infty,x_0)$ and monotonically decreasing on $(x_0,\infty)$, and $x_0$ is a global maximum.
 By the assumption $w_2(x)\leq\beta$ for all $x$, we have $w_2(x_0)\leq\beta$.
-It follows that $c^* \in (x_0,\infty)$, and $w_2(x)$ satisfies $g(w_2(x))=1$ for $x<c^*$ and $g(w_2(x)) = 0$ for $x>c^*$.
+It follows that $c^* \in (\frac{x_0}{2},\infty)$, and $w_2(x)$ satisfies $g(w_2(x))=1$ for $x<2c^*$ and $g(w_2(x)) = 0$ for $x>2c^*$.
 In both cases, we have
+
+\begin{equation}
+g(w_2(x)) = \begin{cases}
+1 & x \leq 2c^* \\
+0 & x > 2c^*
+\end{cases}
+\end{equation}
 
@@
 Along with the assumption that $\sup_{x\in\mathbb R}w_2(x)\leq\b$, we can apply the integro-difference operator once more:
+Thus,
 \begin{equation} \begin{aligned}
-Q[w_2](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_2(y)) \, dy \\
-&= \int_{-\infty}^{c^*} k(x-y) \, dy \\
-&= \int_{x-c^*}^{\infty} k(y) \, dy \\
-&= w_1(x-c^*).
+Q[w_2](x) &= \int_{-\infty}^{\infty} k(x-y) g(w_2(y)) \, dy \\
+&= \int_{-\infty}^{2c^*} k(x-y) \, dy \\
+&= \int_{x-2c^*}^{\infty} k(y) \, dy \\
+&= w_1(x-2c^*).
 \end{aligned} \end{equation}
@@
 \end{subfigure}
-\caption{The shape of the two periodic traveling wave profiles with Laplace dispersal kernel and growth parameters $\alpha=0.3$, $\mu=0.5$, and $\beta=0.8$.}
+\caption{The shape of the two periodic traveling wave profiles with Laplace dispersal kernel and growth parameters $\a=0.3$, $\m=0.5$, and $\b=0.8$.}
 \label{fig:test}
@@
 
-By Lemma \ref{lemma1}, the wave functions $w_1(x)$ and $w_2(x)$ satisfy $Q^2[w_1](x)=w_1(x-2c^*)$ and $Q^2[w_2](x)=w_2(x-2c^*)$.
+By Lemma \ref{lemmamain}, the wave functions $w_1(x)$ and $w_2(x)$ satisfy $Q^2[w_1](x)=w_1(x-2c^*)$ and $Q^2[w_2](x)=w_2(x-2c^*)$.
 As a result, they can be used to construct a solution to the integral recurrence which spreads in space with a mean speed of $c^*$ and alternates in shape every two time steps.
@@
 w_1(x-nc^*) & n \text{ even} \\
-w_2(x-nc^*) & n \text{ odd}
+w_2(x-nc^*+c^*) & n \text{ odd}
 \end{cases}
@@
 It suffices to show that equation \eqref{ptw} satisfies $u_{n+1}=Q[u_n]$ for all $n \geq 0$.
-If $n$ is even, then $n+1$ is odd, so $u_n(x)=w_1(x-nc^*)$ and $u_{n+1}(x)=w_2(x-nc^*-c^*)$.
+If $n$ is even, then $n+1$ is odd, so $u_n(x)=w_1(x-nc^*)$ and $u_{n+1}(x)=w_2(x-nc^*)$.
 Applying the integro-difference operator, we obtain
@@
 Q[u_n](x) &= Q[w_1](x-nc^*) \\
-&= w_2(x-nc^*-c^*) \\
+&= w_2(x-nc^*) \\
 &= u_{n+1}(x)
 \end{aligned} \end{equation}
-by \eqref{w2}. On the other hand, if $n$ is odd, then $n+1$ is even, so $u_n(x)=w_2(x-nc^*)$ and $u_{n+1}(x)=w_1(x-nc^*-c^*)$. Applying the operator, we get
+by \eqref{w2}. On the other hand, if $n$ is odd, then $n+1$ is even, so $u_n(x)=w_2(x-nc^*+c^*)$ and $u_{n+1}(x)=w_1(x-nc^*-c^*)$. Applying the operator, we get
 \begin{equation} \begin{aligned}
-Q[u_n](x) &= Q[w_2](x-nc^*) \\
-&= Q^2[w_1](x-nc^*+c^*) \\
+Q[u_n](x) &= Q[w_2](x-nc^*+c^*) \\
 &= w_1(x-nc^*-c^*) \\
@@
 \end{aligned} \end{equation}
-by Lemma \ref{lemma1}.
+by Lemma \ref{lemmamain}.
 \end{proof}
@@
 \centering
-  \caption{Numerical simulation of the integro-difference equation with Laplace dispersal kernel, $\alpha=0.2$, $\mu=0.3$, and $\beta=0.8$.
+  \caption{Numerical simulation of our model using the Laplace dispersal kernel.
+The parameters chosen for this simulation were $\a=0.2$, $\m=0.3$, and $\b=0.8$, and $\mtwo=1.0$.
 Later timepoints are colored in red, with earlier timepoints colored in green.}
@@
 
-Figure \ref{fig3} shows the propagation of the periodic traveling wave solution for a particular choice of dispersal kernel and growth parameters.
+The previous theorem shows that our model can exhibit a periodic traveling wave solution with alternating wave profiles.
+Furthermore, we derived a constant wave speed at which the oscillating pair of waves travels.
+We now turn our attention to the magnitude of the oscillation in the wave speed.
+For a sufficiently small $\ell > 0$, we may label the point of intersection of the curve $u=u_n(x)$ with the horizontal line $u=\ell$ by $\xi_{n,\ell}$, or simply $\xi_n$.
+It follows that $\xi_1,\xi_2,\xi_3,\dots\to\infty$ as $n\to\infty$; furthermore, the previous theorem implies that for any $\ell$, we have $\xi_{n+2}-\xi_n=2c^*$ for every $n\geq 1$.
+
+For every $n\geq 1$, let $c_n = \xi_n - \xi_{n-1}$.
 

### 2021-07-04 paper_draftver7.tex
updates
blossoming soln

--- 2021-07-04 paper_draftver6.tex
@@
 By Lemma \ref{lemmamain}, the wave functions $w_1(x)$ and $w_2(x)$ satisfy $Q^2[w_1](x)=w_1(x-2c^*)$ and $Q^2[w_2](x)=w_2(x-2c^*)$.
-As a result, they can be used to construct a solution to the integral recurrence which spreads in space with a mean speed of $c^*$ and alternates in shape every two time steps.
-This is formalized in the following theorem:
+As a result, they can be used to construct a solution which spreads in space with a mean speed of $c^*$ and alternates in shape every two time steps.
 
@@
 
+We now introduce an additional hypothesis for the spread of solutions with compactly supported initial condition.
+
+Hypothesis 2. For sufficiently large $r_b$, with $r_a > r_b > 0$ and $\lambda \in (0,1)$, the equation
+
+$$ k(x+r_a) - k(x-r_a) - \lambda k(x+r_b) + \lambda k(x-r_b) $$
+
+has at most 3 solutions.
+
 \begin{thm}  \label{theorem2}
@@
 
-\subsection{Compactly supported kernels}
+\subsection{Spreading solutions}
+
+In this section, we consider how the periodic traveling wave solutions in the preceding results correspond to solutions with a compactly supported initial population density.
+For simplicity, we restrict our attention to initial conditions where the maximum population value does not exceed the overcompensation threshold.
+
+Let $\mathbf 1_{[-r,r]}$ denote the indicator function on $[-r,r]$.
+Suppose $u_0$ is a continuous function with compact support, and suppose $u_0$ satisfies $\a \leq u_0(x) \leq \b$ for $|x| \leq r$ and $u_0(x) < \a$ otherwise.
+It follows that
+$$ g(u_0(x)) = \mathbf 1_{[-r_0,r_0]}(x) $$
+We have
+$$ Q[u_0](x) = (k*(g \circ u_0))(x) = K(x+r_0) - K(x-r_0) $$
+Assuming $r_0$ is large enough so that $ Q[u_0](x) = 2K(r_0)-1 \geq \b$, it follows that
+$$ g(Q[u_0](x)) = \begin{cases}
+n_1 & |x| < r_1 \\
+n_2 & r_1 \leq |x| \leq r_2 \\
+0 & |x| > r_2
+\end{cases} $$
+It follows that
+$$ Q^2 [u_0] (x) = n_2 \int_{-r_2}^{r_2} k(x-y)\,dy - (n_2-n_1) \int_{-r_1}^{r_1} k(x-y) \, dy $$
+$$ = n_2 K(x+r_2) - n_2K(x-r_2) - (n_2-n_1) K(x+r_1) + (n_2-n_1) K(x-r_1) $$
+Taking the derivative, we find
+$$ \frac{d}{dx} Q^2 [u_0](x) = n_2 k(x+r_2) - n_2k(x-r_2) - (n_2-n_1) k(x+r_1) + (n_2-n_1) k(x-r_1) $$
+
+We now require the following hypothesis on the disperal kernel:
+
+(H5) For all $r_2>r_1>0$ and $\lambda \in (0,1)$, the equation
+$$ k(x+r_2) - k(x-r_2) - \lambda k(x+r_1) + \lambda k(x-r_1) = 0 $$
+has at most 3 solutions.
+
+If hypothesis (H5) holds, we can then deduce that $\frac{d}{dx}Q^2[u_0]$ has at most 3 zero-crossings, hence, $Q^2[u_0]$ has at most 3 turning points.
+This leaves only two cases: either $Q^2[u_0]$ has a single turning point at $x=0$, or $Q^2[u_0]$ has 3 turning points, one at $x=0$, and two diametrically opposed turning points $+t$ and $-t$.
+In both cases, there is a unique $r_2>0$ satisfying $Q^2[u_0](x) \geq \a$ for $|x| \leq r_2$ and $Q^2[u_0](x) < \a$ otherwise.
+If $r_2 < r$, then the conclusion does not follow.
+But if $r_2 \geq r$, then the
 
 The next theorem concerns the spreading behavior of solutions to the IDE \eqref{q} with compactly supported initial data.
-We also assume the disperal kernel is compactly supported.% First, we introduce a useful lemma for compactly supported kernels.
-
-%\begin{lem}\label{lemma2}
-%Suppose $k(x)$ is compactly supported on $[-\sigma,\sigma]$ for some $\sigma>0$, and let $u \in C(\mathbb R)$.
-If $u(x)=0$ for $x \in \Omega \subseteq \mathbb R$, then $(k*u)(x)=0$ if $d(x,\mathbb R\setminus\Omega):= \inf \{d(x,y) \mid y\in \mathbb R\setminus\Omega\}$.
-%\end{lem}
-%
-%\begin{proof}
-%Let $x\in\Omega$ such that $d(x,\mathbb R\setminus\Omega) \geq \sigma$.
-Then $(x-\sigma,x+\sigma)$ is a subset of  $\Omega$ on which $u$ vanishes; thus $ (k*u)(x) = \int_{x-\sigma}^{x+\sigma}k(x-y)u(y)\,dy = 0.$
-%\end{proof}
-
-\begin{lem}
-Suppose $k(x)$ has support $[-\sigma,\sigma]$ and $c^*\geq0$.
-
-\begin{enumerate}
-\item If $r \geq \sigma - x_\b$, then $Q[w_1](|x|-r) = w_2(|x|-r-c^*)$.
-
-\item 
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-\begin{enumerate}
-\item 
-Let $u(x) = w_1(|x|-r)$.
-Assuming $r+x_\b \geq 0$, i.e.
-$r \geq -x_\b$, we have $g(u(x)) = \m$ for $|x| < r+x_\b$, $g(u(x)) = 1$ for $r+x_\b \leq x \leq r+x_\a$, and $g(u(x)) = 0 $ for $x > r+x_\a$.
-Note that $g(u(x)) = g(w_1(x-r))$ for $x \geq -r-x_\b$.
-Applying the convolution operator, $Q[u](x) = Q[w_1](x-r)$ for $x \geq -r-x_\b+\sigma$.
-Assuming $r \geq \sigma - x_\b$, this shows $Q[u](x) = w_2(x-r-c^*)$ for $x \geq 0$.
-By the symmetry of $k(x)$, we have $Q[u](x) = w_2(|x|-r-c^*)$.
-
-\item 
-Let $u(x) = w_2(|x|-r)$.
-Assuming $r+x_\b \geq 0$, i.e.
-$r \geq -x_\b$, we have $g(u(x)) = \m$ for $|x| < r+x_\b$, $g(u(x)) = 1$ for $r+x_\b \leq x \leq r+x_\a$, and $g(u(x)) = 0 $ for $x > r+x_\a$.
-Note that $g(u(x)) = g(w_1(x-r))$ for $x \geq -r-x_\b$.
-Applying the convolution operator, $Q[u](x) = Q[w_1](x-r)$ for $x \geq -r-x_\b+\sigma$.
-Assuming $r \geq \sigma - x_\b$, this shows $Q[u](x) = w_2(x-r-c^*)$ for $x \geq 0$.
-By the symmetry of $k(x)$, we have $Q[u](x) = w_2(|x|-r-c^*)$.
-\end{enumerate}
-\end{proof}
-
-\begin{thm} Suppose $k(x)$ has compact support and $\sup_{x\in\mathbb R}w_2(x)\leq \b$.
-Let $u_0(x)$ be non-negative and continuous function, and suppose $\a \leq u_0(x) \leq \b$ for $|x| \leq r$ and $u_0(x) < \a$ otherwise, for some $r > 0$.
-If $r$ is sufficiently large and $c^* \geq 0$, then the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$ spreads with speed $c^*$, i.e.
-\begin{equation}
-\lim_{n\to\infty}\inf_{|x|<n(c^*-\epsilon)}u_{n}(x)>0,
-\end{equation}
-and 
-\begin{equation}
-\lim_{n\to\infty}\sup_{|x|>n(c^*+\epsilon)}u_n(x)=0.
-\end{equation}
-for all $\epsilon>0$.
-\end{thm}
-
-\begin{thm} Suppose $k(x)$ has compact support and $||w_2||_\infty \leq \b$. If $c^* \geq 0$ and $r$ is sufficiently large, then equation \eqref{q} has a periodic spreading solution given by
-\begin{equation} \label{compactptw}
-u_n(x) = \begin{cases}
-w_1(|x|-r-nc^*) & n \text{ even} \\
-w_2(|x|-r-nc^*) & n \text{ odd}
-\end{cases}
-\end{equation}
-for all $n\geq 0$.
-\end{thm}
-
-\begin{proof}
-As in the proof of Theorem \ref{theorem1}, it suffices to show $u_{n+1}=Q[u_n]$ for all $n\geq 0$.
-If $n$ is even, we have $u_n(x)=w_1(|x|-r-nc^*)$.
-Assuming $r \geq \sigma$ and $c^* \geq 0$, this implies $g(u_n(x)) = 0$ for $|x| > r+nc^*+x_\a$, $g(u_n(x))=1$ for $r+nc^*+x_\b\leq |x|\leq r+nc^*+x_\a$, and $g(u_n(x))=\m$ for $|x|<r+nc^*+x_\b$.
-Note that $g(u_n(x)) = g(w_1(x-r-nc^*))$ for $x \geq -r-nc^*-x_\b$.
-Applying the convolution operator, we have $Q[u_n](x) = Q[w_1](x-r-nc^*)$ for $x \geq -r-nc^*-x_\b+\sigma$.
-Assuming $r \geq \sigma - x_\b$, it follows that $Q[u_n](x) = Q[w_1](x-r-nc^*)$ for $x \geq 0$.
-By hypothesis (H2), $k(x)$ is an even function, thus $Q[u_n](-x) = Q[u_n](x)$, hence $Q[u_n](x) = Q[w_1](|x|-r-nc^*)$ for all $x \in \mathbb R$, i.e.
-$u_{n+1}(x) = w_2(|x|-r-nc^*-c^*)$.
-Note that the preceding calculation requires $r \geq \max\{\sigma,\sigma-x_\b\}$; a sufficient condition is $r \geq 2\sigma$.
-
-If $n$ is odd, then $u_n(x)=w_2(|x|-r-nc^*)$, and for $r\geq0$ and $c^*\geq 0$ it follows that $g(u_n(x)) = 0$ for $|x| > r+nc^*+c^*$ and $g(u_n(x))=1$ for $|x| \leq r+nc^*+c^*$.
-
-UNFIN
-\end{proof}
-
-%
-%We apply induction on $n$.
-For the basis case, it is sufficient to show $u_1(x) = w_1(|x|-r)$ for all $x$.
-It follows from the definition of $u_0(x)$ that $g(u_0(x))=1$ for $|x|\leq r$ and $g(u_0(x))=0$ otherwise.
-Assuming $r \geq \frac{\sigma}{2}$, we have $u_1(x)=Q[u_0](x)=w_1(x-r)$ for $x\geq 0$.
-By hypothesis (H2), $k(x)$ is an even function, so $u_1(x)=u_1(-x)$, i.e.
-$u_1(x)=w_1(-x+r)=w_1(x-r)$ for $x<0$.
-This proves $u_1(x)=w_1(|x|-r)$ for all $x$.
-%
-%For the inductive step, suppose equation \eqref{compactptw} holds for some $n\geq0$. If $n$ is even, the inductive hypothesis yields $u_{n+1}(x)=w_1(|x|-r-nc^*)$.
-%\end{proof}
-%
-%\begin{proof}
-%By the translation invariance property of $Q$, we may assume without loss of generality $A=[-r,r]$, for some $r>0$.
-It follows that $u_0(x)<\a$ for $|x|>r$ and $\a\leq u_0(x)\leq\b$ for $|x| \leq r$.
-Furthermore, there exists $\sigma>0$ such that $k(x)>0$ if and only if $|x|<\sigma$.
-Assuming $r \geq \frac{\sigma}{2}$, we have
-%\begin{equation} \begin{aligned}
-%u_1(x) = Q[u_0](x) &= \int_{-r}^{r} k(x-y) \, dy \\
-%&= \begin{cases}
-%w_1(x-r) & x \geq 0 \\
-%w_1(-x+r) & x< 0
-%\end{cases}
-%\end{aligned}  \end{equation}
-%
-%Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. Then, applying the growth function, we have
-%\begin{equation} g(u_1(x)) = \begin{cases}
-%0 & x<-r-x_\a \\
-%1 & -r-x_\a \leq x \leq -r-x_\b \\
-%m & -r-x_\b < x < r+x_\b \\
-%1 & r+x_\b \leq x \leq r+x_\a \\
-%0 & x > r+x_\a
-%\end{cases}
-%\end{equation}
-%Note that $g(u_1(x))=g(w_1(x))$ for all $x >-r-x_\b$.
-Thus $Q[u_1](x)=(k*(g\circ u_1))(x)=(k*(g\circ w_1))(x)=Q[w_1](x)$ for all $x>-r-x_\b+\sigma$.
-If we assume $r \geq x_\b+\sigma$, then $u_2(x)=Q[u_1](x)=Q[w_1](x-r)=w_2(x-r)$ for $x>0$.
-By symmetry of the integro-difference operator, $Q[u_1](x) = Q[w_1](-x+r)$ for $x<0$.
-Thus,
-%
-%\begin{equation}
-%u_2(x) = Q[u_1](x) = \begin{cases}
-%w_2(x-r) & x \geq 0 \\
-%w_2(-x+r) & x < 0 
-%\end{cases}
-%\end{equation}
-%Since $c^*\geq 0$, we have
-%\begin{equation}
-%g(u_2(x)) = \begin{cases}
-%0 & x < -r-2c^* \\
-%1 & -r-2c^* \leq x \leq r+2c^* \\
-%0 & x > r+2c^* 
-%\end{cases}
-%\end{equation}
-%
-%Thus,
-%\begin{equation}
-%u_3(x) = Q[u_2](x) = \begin{cases}
-%w_1(x-r-2c^*) & x \geq 0 \\
-%w_1(-x+r+2c^*) & x < 0 
-%\end{cases}
-%\end{equation}
-%
-%The preceding argument can be repeated inductively to obtain
-%\begin{equation}
-%u_{2n+1}(x) = w_1(|x|-r-2nc^*)
-%\end{equation}
-%and
-%\begin{equation}
-%u_{2n+2}(x) = w_2(|x|-r-2nc^*)
-%\end{equation}
-%for all $n\geq 0$.
-%\end{proof}
 
@@
 
-\subsection{Variability in wave speed}
+\subsection{Blossoming solution}
+
+In addition to the behavior mentioned earlier, we noticed the phenomena of blossoming solution. Whenever
 
@@
 \begin{ex}
-The Laplace kernel,
+The Laplace kernel is given by
 \begin{equation}\label{laplacekernel}
@@
 w_1(x) =   \begin{cases} 
-1 - \frac{1}{2}e^{x} & x \leq 0 \\
-\frac{1}{2}e^{-x} & x > 0
+n_2 - \frac{1}{2} n_2 e^{x} & x \leq 0 \\
+\frac{1}{2} n_2 e^{-x} & x > 0
 \end{cases}
@@
 w_2(x) = \begin{cases}
-m + \left( \frac{1-\m}{2}e^{-x_\b} - \frac{1}{2}e^{-x_\a} \right) e^x & x < x_\b \\
-1 - \left( \frac{1}{2} e^{-x_\a} \right) e^x - \left( \frac{1-\m}{2} e^{x_\b} \right)  e^{-x} & x_\b \leq x \leq x_\a \\
-\left( \frac{1}{2} e^{x_\a} - \frac{1-\m}{2} e^{x_\b} \right) e^{-x} & x_\a < x 
+\m + \left( \frac{1}{2}(\mtwo-\m)e^{-x_\b} - \frac{1}{2}\mtwo e^{-x_\a} \right) e^x & x < x_\b \\
+\mtwo - \frac{1}{2} \mtwo e^{-x_\a} e^x - \frac{1}{2} (\mtwo-\m) e^{x_\b}   e^{-x} & x_\b \leq x \leq x_\a \\
+\left( \frac{1}{2} \mtwo e^{x_\a} - \frac{1}{2}\mtwo(\mtwo-\m) e^{x_\b} \right) e^{-x} & x_\a < x 
 \end{cases} \end{equation}
 
-where
-\begin{equation}
-x_\a = \begin{cases} -\ln(2\a) & \a\leq \frac{1}{2} \\ \ln(2-2\a) & \a > \frac{1}{2} \end{cases}, \quad
-x_\b = \begin{cases} -\ln(2\b) & \b\leq \frac{1}{2} \\ \ln(2-2\b) & \b > \frac{1}{2} \end{cases} 
+with $x_a = F(a)$, $x_b=F(b)$, and
+\begin{equation}
+F(p) = \begin{cases} -\ln(2p) &p \leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases}
 \end{equation}
@@
 c^* = \begin{cases}
-\frac{1}{2}x_\a  + \frac{1}{2}\log \left( \frac{1 - (1-\m) e^{x_\b-x_\a}}{2\a} \right) & \a \leq w_2(x_\a) \\
-\frac{1}{2}x_\a + \frac{1}{2} \log \left( 1-\a + \sqrt{(1-\a)^2 - (1-\mu) e^{x_\b-x_\a}} \right) & w_2(x_\a) < \a < w_2(x_\b) \\
-\frac{1}{2}x_\a + \frac{1}{2} \log \left( \frac{2(\a-\m)}{(1-\m)e^{x_\a-x_\b}-1} \right) & \a \geq w_2(x_\b)
+\frac{1}{2} \log \left( \frac{1}{2\a} \mtwo e^{x_\a} - \frac{1}{2\a}(\mtwo-\m)e^{x_\b} \right) & \a \leq w_2(x_\a) \\
+\frac{1}{2} \log \left( \frac{1}{\mtwo} e^{-x_\a} \left( \m - \a + \sqrt{(\m-\a)^2-\mtwo(\mtwo-\m)e^{x_\b-x_\a}}\right)\right) & w_2(x_\a) < \a < w_2(x_\b) \\
+\frac{1}{2} \log \left( \frac{2(\a-\m)}{(\mtwo-\m)\exp(-x_\b)-\mtwo \exp(-x_\a)}\right) & \a \geq w_2(x_\b)
 \end{cases} 

### 2021-07-04 figures/fig_accelerating_wave.py

@@ -1,0 +1,47 @@
+
+
+import  pyide
+import importlib
+importlib.reload(pyide)
+from scipy.stats import norm
+import numpy as np
+import matplotlib.pyplot as plt
+
+from imp import reload # for debugging
+alpha=0.2
+beta=0.8
+mu=0.3
+
+H = lambda x : np.heaviside(x, 1)
+
+g = lambda x : H(x-alpha) - (1-mu)*H(x-beta)
+
+import matplotlib.pyplot as plt
+
+U = np.arange(0, 1, 0.01)
+k = lambda x: 1/2 * np.exp(-np.abs(x))
+
+model = pyide.IDEModel(growthFunction=pyide.GrowthFunction(g),
+                  dispersalKernel=pyide.DisperalKernel(k))
+                  
+                
+sim = pyide.IDESimulation(model)
+sim.setDomain(xmin=-10, xmax=10, dx=0.005)
+r=.58
+sim.setInitialCondition(lambda x : H(x+r)-H(x-r))
+sim.setBoundaryCondition('static')
+
+n = 15
+sim.run(n)
+sim.plot(times=np.arange(1, n), file='fig_accelerating_wave1.png')
+plt1 = sim.plot_wavespeed(times=np.arange(1, n), 
+predictedcstar = 0.8568,
+predictedc1 = 2*0.8568 + np.log(2/5),
+predictedc2 = -np.log(2/5),
+level=0.2,
+file='fig_accelerating_wave2.png')
+plt1.show()
+import matplotlib.pyplot as plt
+plt.plot([1,11], [.444, .444])
+#print(sim.timeSeries)
+

### 2021-07-04 figures/pyide.py

@@ -3,7 +3,7 @@ import numpy as np
 import matplotlib.pyplot as plt
     
 # class for handling growth functions
-plt.rcParams.update({"text.usetex": True})
+#plt.rcParams.update({"text.usetex": True})
 class GrowthFunction:
     
     def __init__(self, g):
@@ -305,6 +305,38 @@ class IDESimulation:
             
             self.timeSeries.append(U)
             
+    def plot_wavespeed(self, predictedcstar, predictedc1, predictedc2, level=0.1, times=[], file=None):
+    
+        X = self.domain
+        U_seq = self.timeSeries
+        T = len(U_seq)
+        
+        if len(times)==0:
+            times = np.arange(T)
+            
+        fig,axs = plt.subplots()
+        
+        d0 = self.step_size*np.sum(U_seq[0]>level)
+        C = []
+        for t in times[1:]:
+            
+            U = U_seq[t]
+            d1 = self.step_size*np.sum(U>level)
+            C.append((d1-d0))
+            d0 = d1
+            
+        axs.plot(times[1:], C)
+        axs.set_xlabel('t')
+        axs.set_ylabel('c_n(t)')
+        try:
+            plt.savefig(file)
+        except:
+            pass
+        plt.plot([1, max(times)], [predictedcstar, predictedcstar], 'b--')
+        plt.plot([1, max(times)], [predictedc1, predictedc1], 'b:')
+        plt.plot([1, max(times)], [predictedc2, predictedc2], 'b:')
+        return plt
+        
     def plot(self, times=[], file=None):
     
         X = self.domain
@@ -325,5 +357,5 @@ class IDESimulation:
             plt.savefig(file)
         except:
             pass
-        plt.show()
+        return plt
     

### 2021-07-13 Nestor_Li_manuscript_revision_7_13.tex
work

--- 2021-07-04 paper_draftver7.tex
@@
 
- Let $w_1$ and $w_2$ be two functions defined by
-\begin{equation} \label{w1}
-w_1(x) := \int_x^\infty \mtwo k(y) \, dy
+\begin{lem} \label{lemmamain}
+Let $w(x) = \int_x^\infty k(y) \, dy$. Define
+\begin{equation}
+c^* = \frac{1}{2} \sup \{ x\in\mathbb R | Q[\mtwo w](x) \geq \a \}
+\end{equation}
+Let $w_1(x) = w(x)$ and $w_2(x) = Q[w](x+c^*)$. If $|| w_2 ||_\infty \leq \b $, then $w_1$ and $w_2$ satisfy
+\begin{equation} \label{lemma1claim1}
+Q[w_1](x) = w_2(x-c^*)
 \end{equation}
 and
-\begin{equation} \label{w2}
-w_2(x) = \int_x^\infty \left( \mtwo k(y-x_\a) - (\mtwo-\m)k(y-x_\b)\right) \, dy 
-\end{equation} 
-where $x_\a$ and $x_\b$ constants constants given by
-\begin{equation}
-x_\a =\sup\left\{x\in\mathbb R\mid \int_{-\infty}^{x} k(y) \, dy \leq \frac{\a}{\mtwo} \right\}, \quad
-x_\b =\sup\left\{x\in\mathbb R\mid \int_{-\infty}^{x} k(y) \, dy \leq \frac{\b}{\mtwo} \right\}
-\end{equation}
-
-\begin{lem} \label{lemmamain}
-If $ || w_2 ||_\infty \leq \b $, then $w_1$ and $w_2$ satisfy
-\begin{equation}
-Q[w_1](x) = w_2(x)
-\end{equation}
-and
-\begin{equation}
-Q[w_2](x) = w_1(x-2c^*)
-\end{equation}
-for all $x\in\mathbb R$, where $c^*$ is a constant given by
-\begin{equation}
-c^* = \frac{1}{2} \sup\{x\in\mathbb R\mid w_2(x)\geq \a\}
-\end{equation}
+\begin{equation}\label{lemma1claim2}
+Q[w_2](x) = w_1(x-c^*)
+\end{equation}
+for all $x \in \mathbb R$.
 \end{lem}
 
-%
 %
@@
 \begin{proof}
-$w_1$ is monotonically decreasing with $w_1(-\infty)=\mtwo$ and $w_1(\infty)=0$.
-It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$.
+Equation \ref{lemma1claim1} follows directly from the definition of $w_2(x)$.
+
+To prove \ref{lemma1claim2}, observer that $w_1$ is monotonically decreasing with $w_1(-\infty)=\mtwo$ and $w_1(\infty)=0$.
+It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$, where $x_a$ and $x_b$ are the solutions of
+\begin{equation}
+w_1(x_\a) = \a, \quad w_1(x_\b) = \b
+\end{equation}
 This yields
@@
 \begin{aligned}
-Q[w_1](x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
-&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \mtwo \int_{x_\b}^{x_\a} k(x-y) \, dy \\
+Q[w_1](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
+&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \mtwo \int_{x_\b}^{x_\a} k(x-y) \, dy %\\
+\end{aligned} \end{equation}
 %&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
-&= \mtwo \int_{x-x_\a}^{\infty} k(y) \, dy - (\mtwo-\m) \int_{x-x_\b}^{\infty} k(y) \, dy \\
-&= \int_{x}^{\infty} \left( \mtwo k(y-x_\a)  - (\mtwo-\m)k(y-x_\b)\right) \, dy
-\end{aligned} \end{equation}
+%&= \mtwo \int_{x-x_\a}^{\infty} k(y) \, dy - (\mtwo-\m) \int_{x-x_\b}^{\infty} k(y) \, dy \\
+Using a substitution on both integrals yields equation \eqref{w2}, proving the first part of the lemma.
 %It can now be seen that replacing $x$ with $x-c^*$ in equation \eqref{w2} produces \eqref{qw1calculation}.
@@
 %'\begin{proof}
-By Hypothesis (H4), we have assumed that the integrand on the right hand side has at most one zero.
+To prove the second half, we differentiate $w_2$ with respect to $x$:
+\begin{equation} \label{dqw1}
+\frac{dw_2}{dx} = \mtwo k(x-x_\a) - (\mtwo-\m) k(x-x_\b)
+\end{equation}
+A transformation of coordinates shows that equation \eqref{dqw1} is proportional to $k(x) - \frac{\mtwo-\m}{\mtwo} k(x+x_\a-x_\b)$; by hypothesis (H4), $\frac{dw_2}{dx}$ has at most one real zero.
+
+It can be shown by cases that $w_2$ is either monotonically decreasing or has a unique turning point $x_0 \in \mathbb R$.
+In both cases, the curve $u=w_2(x)$ crosses the horizontal line $u=\a$ exactly once at the point $x=2c^*$.
+In the latter case, we utilize the assumption that $|| w_2 ||_\infty \leq \b$ .
+In all cases,
+
+%By Hypothesis (H4), we have assumed that the integrand on the right hand side has at most one zero.
 We can now proceed in cases.
@@
 It follows that $c^* \in (\frac{x_0}{2},\infty)$, and $w_2(x)$ satisfies $g(w_2(x))=1$ for $x<2c^*$ and $g(w_2(x)) = 0$ for $x>2c^*$.
-In both cases, we have
-
+In each case, we have
+%%
 \begin{equation}
@@
 \end{proof}
+
+By Lemma \ref{lemmamain}, the wave functions $w_1(x)$ and $w_2(x)$ satisfy $Q^2[w_1](x)=w_1(x-2c^*)$ and $Q^2[w_2](x)=w_2(x-2c^*)$.
+As a result, they can be used to construct a solution which spreads in space with a mean speed of $c^*$ and alternates in shape every two time steps.
+
+%\begin{cor} If $||w_2||_\infty \leq \beta$, then for all $x\in\mathbb R$,
+%\begin{equation}
+%Q^2[w_1](x) = w_1(x-2c^*)
+%\end{equation}
+%and
+%\begin{equation}
+%Q^2[w_2](x) = w_2(x-2c^*)
+%\end{equation}
+%\end{cor}
+
+%The condition that $\sup_{x\in\mathbb R}w_2(x)\leq \b$ may be difficult to verify for some choices of dispersal kernel. Thus, we provide a sufficient condition for this assumption:
+%\begin{lem} \label{lemma}
+%Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. If $k(x)$ is unimodal and
+%$$ \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy \leq \b $$
+%then $\sup_{x\in\mathbb R}w_2(x) \leq \b$.
+%\end{lem}
+%
+%\begin{proof}
+%For all $x\in\mathbb R$, we have
+%\begin{equation} \begin{aligned}
+%w_2(x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy  \\
+%&\leq\int_{-\infty}^{\infty} k(x-y) (\m + (\m-1) \mathbf 1_{[x_\b,x_\a]}(y) )\, dy \\
+%&= \m + \int_{-\infty}^{\infty} k(x-y) (\m-1) \mathbf 1_{[x_\b,x_\a]}(y) \, dy \\
+%&= \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy .
+%\end{aligned}
+%\end{equation}
+%
+%Taking the maximum over all $x$, we may shift the function horizontally so that the bounds of integration are symmetric. Since $k(x)$ is unimodal, the integral is then maximized for $x=0$.
+%\begin{equation} \begin{aligned}
+%\sup_{x\in\mathbb R} w_2(x) &\leq \sup_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy \right) \\
+%&= \sup_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (x-y) \, dy \right) \\
+%&= \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy.
+%\end{aligned}
+%\end{equation}
+%\end{proof}
+
+\begin{thm} \label{theorem1}
+Let $u_n(x)$ be a sequence of functions defined by
+\begin{equation}
+u_n(x) = \begin{cases} \label{ptw}
+w_1(x-nc^*) & n \text{ even} \\
+w_2(x-nc^*) & n \text{ odd}
+\end{cases} \end{equation}
+If $|| w_2 ||_\infty \leq \b $, then $u_n(x)$ satisfies $u_{n+1}(x) = Q[u_n](x)$ for all $n\geq 0$.
+\end{thm}
+
+\begin{proof}
+Let $n \geq 0$. If $n$ is even, then $n+1$ is odd, so $u_n(x)=w_1(x-nc^*)$ and $u_{n+1}(x)=w_2(x-nc^*)$. Applying the integro-difference operator, we obtain
+\begin{equation} \begin{aligned}
+Q[u_n](x) &= Q[w_1](x-nc^*) \\
+&= w_2(x-nc^*) \\
+&= u_{n+1}(x)
+\end{aligned} \end{equation}
+by \eqref{w2}. On the other hand, if $n$ is odd, then $n+1$ is even, so $u_n(x)=w_2(x-nc^*+c^*)$ and $u_{n+1}(x)=w_1(x-nc^*-c^*)$. Applying the operator, we get
+\begin{equation} \begin{aligned}
+Q[u_n](x) &= Q[w_2](x-nc^*+c^*) \\
+&= w_1(x-nc^*-c^*) \\
+&= u_{n+1}(x)
+\end{aligned} \end{equation}
+by Lemma \ref{lemmamain}.
+\end{proof}
+
+The previous theorem shows that our model can exhibit a periodic traveling wave solution with alternating wave profiles.
+Furthermore, we derived a constant wave speed at which the oscillating pair of waves travels.
+We now turn our attention to the magnitude of the oscillation in the wave speed.
+For a sufficiently small $\ell > 0$, we may label the point of intersection of the curve $u=u_n(x)$ with the horizontal line $u=\ell$ by $\xi_{n,\ell}$, or simply $\xi_n$.
+It follows that $\xi_1,\xi_2,\xi_3,\dots\to\infty$ as $n\to\infty$; furthermore, the previous theorem implies that for any $\ell$, we have $\xi_{n+2}-\xi_n=2c^*$ for every $n\geq 1$.
+
+$$
+w_i(x) = \int_\Omega k(x-y+2c^*) g\left( \int_\Omega k(y-y') g(w_i(y')) \, dy' \right) \, dy
+$$
+For every $n\geq 1$, let $c_n = \xi_n - \xi_{n-1}$.
+
+We now introduce an additional hypothesis for the spread of solutions with compactly supported initial condition.
+
+Hypothesis 2. For sufficiently large $r_b$, with $r_a > r_b > 0$ and $\lambda \in (0,1)$, the equation
+
+$$ k(x+r_a) - k(x-r_a) - \lambda k(x+r_b) + \lambda k(x-r_b) $$
+
+has at most 3 solutions.
+
+\begin{thm}  \label{theorem2}
+If $||w_2|| \b$, then for all $\epsilon>0$, the sequence \ref{ptw} satisfies
+\begin{equation}
+\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n}(x)=\mtwo
+\end{equation}
+and
+\begin{equation}
+\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n+1}(x)=\m
+\end{equation}
+and 
+\begin{equation}
+\lim_{n\to\infty}\sup_{x>n(c^*+\epsilon)}u_n(x)=0.
+\end{equation}
+\end{thm}
+
+\begin{proof}
+\begin{equation} \begin{aligned}
+\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n}(x)
+&= \lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}w_1(x-2nc^*) \\
+&= \lim_{n\to\infty}\inf_{x<-2n\epsilon}w_1(x) \\
+&= \liminf_{x\to-\infty}w_1(x) \\ &= 1.
+\end{aligned} \end{equation}
+
+\begin{equation} \begin{aligned}
+\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n+1}(x)
+&= \lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}w_2(x-2nc^*) \\
+&= \lim_{n\to\infty}\inf_{x<-2n\epsilon}w_2(x) \\
+&= \liminf_{x\to-\infty}w_2(x) \\ &= \m.
+\end{aligned} \end{equation}
+
+\begin{equation} \begin{aligned}
+\lim_{n\to\infty} \sup_{x>n(c^*+\epsilon)} u_n(x) 
+&\leq \lim_{n\to\infty} \sup_{x>n(c^*+\epsilon)} \sup\{w_1(x-nc^*),w_2(x-nc^*)\} \\
+&= \lim_{n\to\infty} \sup_{x>n\epsilon} \sup\{w_1(x),w_2(x)\} \\
+&= \limsup_{x\to\infty} \sup\{w_1(x),w_2(x)\} \\ 
+&= \sup\{\limsup_{x\to\infty} w_1(x),\limsup_{x\to\infty} w_2(x)\} \\
+&= 0.
+\end{aligned} \end{equation}
+In the last calculation, the left hand side is known to be non-negative; therefore the limit is exactly equal to zero.
+\end{proof}
+
+\subsection{Spreading solutions}
+
+\textbf{Note: this section contains incomplete results.}
+
+In this section, we consider how the periodic traveling wave solutions in the preceding results correspond to solutions with a compactly supported initial population density.
+For simplicity, we restrict our attention to initial conditions where the maximum population value does not exceed the overcompensation threshold.
+
+Let $\chi_{[-r,r]}$ denote the indicator function on $[-r,r]$.
+Suppose $u_0$ is a continuous function with compact support, and suppose $u_0$ satisfies $\a \leq u_0(x) \leq \b$ for $|x| \leq r$ and $u_0(x) < \a$ otherwise.
+It follows that
+$$ g(u_0(x)) = \chi_{[-r,r]}(x) $$
+
+%
+%Let $u_n(x)$ be a sequence of continuous functions. For every $c \in \mathbb R$, define the sequence $a_n(x,c)$ by
+%$$ a_n(x,c) = u_n(x+nc) $$
+%Now, define
+%$$ a(x,c) = \limsup_{n\to\infty} a_n(x,c). $$
+%Note that since $a_n$ is bounded, this quantity must be finite. We say the rightware spreading speed of $u_0$ is defined by
+%$$ c^*_+ = \inf \{ c \in \mathbb R \mid \lim_{x\to\infty} a(x,c) = 0 \} $$
+%
+%\begin{lem}
+%If $||w_2||_\infty\leq\b$, the sequence \eqref{ptw} has a rightward spreading speed of $c^*$.
+%\end{lem}
+%
+%\begin{proof}
+%We have
+%$$ a_n(x,c) = \begin{cases}
+%w_1(x + n(c-c^*))  & n \text{ even} \\
+%w_2(x + n(c-c^*)) & n \text{ odd}
+%\end{cases} $$
+%Thus,
+%$$ \begin{aligned}
+%a(x,c) &= \limsup_{n\to\infty} a_n(x,c) \\
+%&= \limsup_{n\to\infty} \max \{ w_1(x + n(c-c^*)), w_2(x + n(c-c^*)) \} \\
+%&= \begin{cases}
+%1 & c < c^* \\
+%\max\{w_1(x),w_2(x)\} & c=c^* \\
+%0 & c>c^*
+%\end{cases} \end{aligned} $$
+%Taking the limit as $x\to\infty$,
+%$$ a(\infty,c) = \begin{cases}
+%1 & c < c^* \\
+%0 & c \geq c^*
+%\end{cases} $$
+%\end{proof}
+
+For a given $r \geq 0$, let $\phi(x,r) = \chi_{[-r,r]}(x)$, or simply $\phi_r$ for brevity. Define the operator $R[u] = g\left( Q[k*u](x) \right)$.
+
+\begin{equation}
+R[u](x) = g\left( \int k(x-y) g\left( \int k(y-z) u(z) \, dz \right) \, dy \right)
+\end{equation}
+
+\begin{lem}
+Let $u_n(x)$ be a sequence of functions satisfying $u_{n+1}(x)=Q[u_n](x)$ for all $n \geq 0$ with initial condition $u_0 \in C(\mathbb R; [0,1])$.
+Then $u_{2n}(x) = (k*R^{n-1}[g\circ u])(x)$ for all $n\geq1 $.
+\end{lem}
+
+\begin{lem}
+For sufficiently large $r \geq 0$, we have $R[\phi_r] = \phi_{r+\delta(r)}$, where $\delta(r)$ is a scalar function of $r$. It can be expressed as
+$$ \delta(r) = \int R[\phi_r](x)  \, dx $$
+\end{lem}
+
+\begin{proof}
+We have
+$$ (k*\phi_r)(x) = K(x+r) - K(x-r) $$
+Note that $(k*\phi_r)(0) = 2K(r)-1$, assuming a symmetryic dispersal kernel.
+Thus, assuming $\frac{d}{dx}(k*\phi_r)$ has at most one zero, a lower bound of $r \geq K^{-1}\left(\frac{\b+1}{2}\right)$ guarantees
+$$ R[\phi_r] = \begin{cases}
+n_1 & |x| < r_1 \\
+n_2 & r_1 \leq |x| \leq r_2 \\
+0 & |x| > r_2
+\end{cases} $$
+\end{proof}
+for some $r_2 > r_1 \geq 0$.
+
+Applying the convolution operator to this expression yields
+$$ k*R[\phi_r] (x) = n_2 \int_{-r_2}^{r_2} k(x-y)\,dy - (n_2-n_1) \int_{-r_1}^{r_1} k(x-y) \, dy $$
+$$ = n_2 \left[ K(x+r_2) - K(x-r_2)  \right] - (n_2-n_1) \left[ K(x+r_1) - K(x-r_1) \right] $$
+Taking the derivative, we find
+$$ \frac{d}{dx} \left[ k*R[\phi_r] \right] = n_2 \left[ k(x+r_2) - k(x-r_2)  \right] - (n_2-n_1) \left[ k(x+r_1) - k(x-r_1)\right] $$
+We now require the following hypothesis on the disperal kernel:
+
+(H5) For all $r_2>r_1>0$ and $\lambda \in (0,1)$, the equation
+$$ k(x+r_2) - k(x-r_2) - \lambda k(x+r_1) + \lambda k(x-r_1) = 0 $$
+has at most 3 solutions.
+
+If hypothesis (H5) holds, we can then deduce that $k*R[\phi_r]$ has at most 3 turning points.
+This leaves only two cases: either $k*R[\phi_r]$ has a single turning point at $x=0$, or has 3 turning points, one at $x=0$, and two diametrically opposed turning points $+t$ and $-t$.
+In both cases, there is a unique $r_3>0$ satisfying $(k*R[\phi_r])(x) \geq \a$ for $|x| \leq r_3$ and $(k*R[\phi_r])(x) < \a$ otherwise.
+
+\textbf{Note: the above section contains unfinished proofs.}
+
+\begin{figure}[h!] 
+\centering
+  \caption{Spreading behavior for a uniform dispersal kernel with $\alpha=0.3$, $\mu=0.6$, and $\beta=0.7$.
+The time steps corresponding to $w_1(x)$ are colored in blue, while time steps corresponding to $w_2(x)$ are colored in red.}
+\label{fig5}
+  \includegraphics[width=.8\linewidth]{figures/fig5.png}
+\end{figure}
+
+\begin{rem}
+This theorem indicates that a solution with proper compactly supported initial data coverges to translations of periodic traveling waves with profiles $w_1(x)$ and $w_2(x)$ in the positive direction and profiles $w_1(-x)$ and $w_2(-x)$ in the negative direction.
+\end{rem}
+
+\section{Examples}
+
+In this section, we construct the periodic traveling wave solution for several well-known disperal kernels in population biology, namely the uniform, Laplace, and normal distributions.
+For the uniform and Laplace kernels, we were able to construct a piecewise expression for the mean wave speed in terms of the model parameters.
+
+\begin{ex}
+The Laplace kernel is given by
+\begin{equation}\label{laplacekernel}
+k(x) = \frac{1}{2} e^{-|x|}
+\end{equation}
+
+The reader can easily verify that the Laplace kernel satisfies hypotheses (H1) - (H3); the proof of (H4) is left in the appendix \ref{laplaceproof}.
 
@@
 
-By Lemma \ref{lemmamain}, the wave functions $w_1(x)$ and $w_2(x)$ satisfy $Q^2[w_1](x)=w_1(x-2c^*)$ and $Q^2[w_2](x)=w_2(x-2c^*)$.
-As a result, they can be used to construct a solution which spreads in space with a mean speed of $c^*$ and alternates in shape every two time steps.
-
-%\begin{cor} If $||w_2||_\infty \leq \beta$, then for all $x\in\mathbb R$,
-%\begin{equation}
-%Q^2[w_1](x) = w_1(x-2c^*)
-%\end{equation}
-%and
-%\begin{equation}
-%Q^2[w_2](x) = w_2(x-2c^*)
-%\end{equation}
-%\end{cor}
-
-%The condition that $\sup_{x\in\mathbb R}w_2(x)\leq \b$ may be difficult to verify for some choices of dispersal kernel. Thus, we provide a sufficient condition for this assumption:
-%\begin{lem} \label{lemma}
-%Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. If $k(x)$ is unimodal and
-%$$ \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy \leq \b $$
-%then $\sup_{x\in\mathbb R}w_2(x) \leq \b$.
-%\end{lem}
-%
-%\begin{proof}
-%For all $x\in\mathbb R$, we have
-%\begin{equation} \begin{aligned}
-%w_2(x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy  \\
-%&\leq\int_{-\infty}^{\infty} k(x-y) (\m + (\m-1) \mathbf 1_{[x_\b,x_\a]}(y) )\, dy \\
-%&= \m + \int_{-\infty}^{\infty} k(x-y) (\m-1) \mathbf 1_{[x_\b,x_\a]}(y) \, dy \\
-%&= \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy .
-%\end{aligned}
-%\end{equation}
-%
-%Taking the maximum over all $x$, we may shift the function horizontally so that the bounds of integration are symmetric. Since $k(x)$ is unimodal, the integral is then maximized for $x=0$.
-%\begin{equation} \begin{aligned}
-%\sup_{x\in\mathbb R} w_2(x) &\leq \sup_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy \right) \\
-%&= \sup_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (x-y) \, dy \right) \\
-%&= \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy.
-%\end{aligned}
-%\end{equation}
-%\end{proof}
-
-\begin{thm} \label{theorem1}
-If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then equation \eqref{q} has a periodic traveling wave solution given by %$(u_n)_{n=0}^{\infty}$ satisfying
-%\begin{equation} \label{ptw}
-%u_n(x) = \begin{cases}
-%w_1(x-nc^*) & n \text{ even} \\
-%w_2(x-nc^*) & n \text{ odd}
+The periodic traveling wave profiles are given by
+
+\begin{equation} \label{w1laplace}
+w_1(x) =   \begin{cases} 
+n_2 - \frac{1}{2} n_2 e^{x} & x \leq 0 \\
+\frac{1}{2} n_2 e^{-x} & x > 0
+\end{cases}
+\end{equation}
+and
+%\begin{equation}\label{laplacew2}
+%w_2(x) = \begin{cases}
+%m - \frac{1}{2} e^{x - \alpha} + \frac{1-\m}{2} e^{x - \beta} & x < \beta \\
+%1 - \frac{1}{2} e^{x-\alpha} - \frac{1-\m}{2} e^{-(x-\beta)} & \beta \leq x \leq \alpha \\
+%\frac{1}{2} e^{-(x-\alpha)} - \frac{1-\m}{2} e^{-(x-\beta)} & x > \alpha
 %\end{cases}
 %\end{equation}
-
-\begin{equation} \label{ptw}
-u_n(x) = \begin{cases}
-w_1(x-nc^*) & n \text{ even} \\
-w_2(x-nc^*+c^*) & n \text{ odd}
-\end{cases}
-\end{equation}
-for all $n \geq 0$.
-\end{thm}
-
-\begin{proof}
-It suffices to show that equation \eqref{ptw} satisfies $u_{n+1}=Q[u_n]$ for all $n \geq 0$.
-If $n$ is even, then $n+1$ is odd, so $u_n(x)=w_1(x-nc^*)$ and $u_{n+1}(x)=w_2(x-nc^*)$.
-Applying the integro-difference operator, we obtain
-\begin{equation} \begin{aligned}
-Q[u_n](x) &= Q[w_1](x-nc^*) \\
-&= w_2(x-nc^*) \\
-&= u_{n+1}(x)
-\end{aligned} \end{equation}
-by \eqref{w2}. On the other hand, if $n$ is odd, then $n+1$ is even, so $u_n(x)=w_2(x-nc^*+c^*)$ and $u_{n+1}(x)=w_1(x-nc^*-c^*)$. Applying the operator, we get
-\begin{equation} \begin{aligned}
-Q[u_n](x) &= Q[w_2](x-nc^*+c^*) \\
-&= w_1(x-nc^*-c^*) \\
-&= u_{n+1}(x)
-\end{aligned} \end{equation}
-by Lemma \ref{lemmamain}.
-\end{proof}
-
-%For convenience, we will switch the index and consider the cases $u_{2n}$ and $u_{2n+1}$ separately.
-The basic case, $u_1 = Q[u_0]$, follows immediately from definition \ref{w2}.
-This proves the first half.
-Next, we have $u_2(x)=w_1(x-2c^*)$, which follows by Lemma \ref{lemma1}.
-%
-%For the inductive step, suppose $u_{2n+1}=Q[u_{2n}]$ and $u_{2n+2}=Q[u_{2n+1}]$ for some $n\geq 0$. We only need to show $u_{2n+3}=Q[u_{2n+2}]$. We have
-%\begin{equation} \begin{aligned}
-%u_{2n+3}(x) &= w_2(x-2nc^*-2c^*) \\
-%&= Q^2[w_2](x-2nc^*) \\
-%&= Q^2[u_{2n+1}](x) \\ 
-%&= Q[u_{2n+2}](x)
-%\end{aligned} \end{equation}
-% \end{proof}
+%\begin{equation} \label{w2laplace}
+%w_2(x) = \begin{cases}
+%m + C_1 e^x & x < x_\b \\
+%1 - C_2 e^x - C_3 e^{-x} & x_\b \leq x \leq x_\a \\
+%C_4 e^{-x} & x_\a < x 
+%\end{cases} \end{equation}
+%or equivalently
+
+\begin{equation} \label{w2laplace}
+w_2(x) = \begin{cases}
+\m + \left( \frac{1}{2}(\mtwo-\m)e^{-x_\b} - \frac{1}{2}\mtwo e^{-x_\a} \right) e^x & x < x_\b \\
+\mtwo - \frac{1}{2} \mtwo e^{-x_\a} e^x - \frac{1}{2} (\mtwo-\m) e^{x_\b}   e^{-x} & x_\b \leq x \leq x_\a \\
+\left( \frac{1}{2} \mtwo e^{x_\a} - \frac{1}{2}\mtwo(\mtwo-\m) e^{x_\b} \right) e^{-x} & x_\a < x 
+\end{cases} \end{equation}
+
+with $x_a = F(a)$, $x_b=F(b)$, and
+\begin{equation}
+F(p) = \begin{cases} -\ln(2p) &p \leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases}
+\end{equation}
 
@@
 
-The previous theorem shows that our model can exhibit a periodic traveling wave solution with alternating wave profiles.
-Furthermore, we derived a constant wave speed at which the oscillating pair of waves travels.
-We now turn our attention to the magnitude of the oscillation in the wave speed.
-For a sufficiently small $\ell > 0$, we may label the point of intersection of the curve $u=u_n(x)$ with the horizontal line $u=\ell$ by $\xi_{n,\ell}$, or simply $\xi_n$.
-It follows that $\xi_1,\xi_2,\xi_3,\dots\to\infty$ as $n\to\infty$; furthermore, the previous theorem implies that for any $\ell$, we have $\xi_{n+2}-\xi_n=2c^*$ for every $n\geq 1$.
-
-For every $n\geq 1$, let $c_n = \xi_n - \xi_{n-1}$.
-
-We now introduce an additional hypothesis for the spread of solutions with compactly supported initial condition.
-
-Hypothesis 2. For sufficiently large $r_b$, with $r_a > r_b > 0$ and $\lambda \in (0,1)$, the equation
-
-$$ k(x+r_a) - k(x-r_a) - \lambda k(x+r_b) + \lambda k(x-r_b) $$
-
-has at most 3 solutions.
-
-\begin{thm}  \label{theorem2}
-If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then for all $\epsilon>0$, the sequence \ref{ptw} satisfies
-\begin{equation}
-\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n}(x)=1
-\end{equation}
-and
-\begin{equation}
-\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n+1}(x)=\m
-\end{equation}
-and 
-\begin{equation}
-\lim_{n\to\infty}\sup_{x>n(c^*+\epsilon)}u_n(x)=0.
-\end{equation}
-\end{thm}
-
-\begin{proof}
-\begin{equation} \begin{aligned}
-\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n}(x)
-&= \lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}w_1(x-2nc^*) \\
-&= \lim_{n\to\infty}\inf_{x<-2n\epsilon}w_1(x) \\
-&= \liminf_{x\to-\infty}w_1(x) \\ &= 1.
-\end{aligned} \end{equation}
-
-\begin{equation} \begin{aligned}
-\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n+1}(x)
-&= \lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}w_2(x-2nc^*) \\
-&= \lim_{n\to\infty}\inf_{x<-2n\epsilon}w_2(x) \\
-&= \liminf_{x\to-\infty}w_2(x) \\ &= \m.
-\end{aligned} \end{equation}
-
-\begin{equation} \begin{aligned}
-\lim_{n\to\infty} \sup_{x>n(c^*+\epsilon)} u_n(x) 
-&\leq \lim_{n\to\infty} \sup_{x>n(c^*+\epsilon)} \sup\{w_1(x-nc^*),w_2(x-nc^*)\} \\
-&= \lim_{n\to\infty} \sup_{x>n\epsilon} \sup\{w_1(x),w_2(x)\} \\
-&= \limsup_{x\to\infty} \sup\{w_1(x),w_2(x)\} \\ 
-&= \sup\{\limsup_{x\to\infty} w_1(x),\limsup_{x\to\infty} w_2(x)\} \\
-&= 0.
-\end{aligned} \end{equation}
-In the last calculation, the left hand side is known to be non-negative; therefore the limit is exactly equal to zero.
-\end{proof}
-
-\subsection{Spreading solutions}
-
-In this section, we consider how the periodic traveling wave solutions in the preceding results correspond to solutions with a compactly supported initial population density.
-For simplicity, we restrict our attention to initial conditions where the maximum population value does not exceed the overcompensation threshold.
-
-Let $\mathbf 1_{[-r,r]}$ denote the indicator function on $[-r,r]$.
-Suppose $u_0$ is a continuous function with compact support, and suppose $u_0$ satisfies $\a \leq u_0(x) \leq \b$ for $|x| \leq r$ and $u_0(x) < \a$ otherwise.
-It follows that
-$$ g(u_0(x)) = \mathbf 1_{[-r_0,r_0]}(x) $$
-We have
-$$ Q[u_0](x) = (k*(g \circ u_0))(x) = K(x+r_0) - K(x-r_0) $$
-Assuming $r_0$ is large enough so that $ Q[u_0](x) = 2K(r_0)-1 \geq \b$, it follows that
-$$ g(Q[u_0](x)) = \begin{cases}
-n_1 & |x| < r_1 \\
-n_2 & r_1 \leq |x| \leq r_2 \\
-0 & |x| > r_2
-\end{cases} $$
-It follows that
-$$ Q^2 [u_0] (x) = n_2 \int_{-r_2}^{r_2} k(x-y)\,dy - (n_2-n_1) \int_{-r_1}^{r_1} k(x-y) \, dy $$
-$$ = n_2 K(x+r_2) - n_2K(x-r_2) - (n_2-n_1) K(x+r_1) + (n_2-n_1) K(x-r_1) $$
-Taking the derivative, we find
-$$ \frac{d}{dx} Q^2 [u_0](x) = n_2 k(x+r_2) - n_2k(x-r_2) - (n_2-n_1) k(x+r_1) + (n_2-n_1) k(x-r_1) $$
-
-We now require the following hypothesis on the disperal kernel:
-
-(H5) For all $r_2>r_1>0$ and $\lambda \in (0,1)$, the equation
-$$ k(x+r_2) - k(x-r_2) - \lambda k(x+r_1) + \lambda k(x-r_1) = 0 $$
-has at most 3 solutions.
-
-If hypothesis (H5) holds, we can then deduce that $\frac{d}{dx}Q^2[u_0]$ has at most 3 zero-crossings, hence, $Q^2[u_0]$ has at most 3 turning points.
-This leaves only two cases: either $Q^2[u_0]$ has a single turning point at $x=0$, or $Q^2[u_0]$ has 3 turning points, one at $x=0$, and two diametrically opposed turning points $+t$ and $-t$.
-In both cases, there is a unique $r_2>0$ satisfying $Q^2[u_0](x) \geq \a$ for $|x| \leq r_2$ and $Q^2[u_0](x) < \a$ otherwise.
-If $r_2 < r$, then the conclusion does not follow.
-But if $r_2 \geq r$, then the
-
-The next theorem concerns the spreading behavior of solutions to the IDE \eqref{q} with compactly supported initial data.
-
-\begin{figure}[h!] 
-\centering
-  \caption{Spreading behavior for a uniform dispersal kernel with $\alpha=0.3$, $\mu=0.6$, and $\beta=0.7$.
-The time steps corresponding to $w_1(x)$ are colored in blue, while time steps corresponding to $w_2(x)$ are colored in red.}
-\label{fig5}
-  \includegraphics[width=.8\linewidth]{figures/fig5.png}
-\end{figure}
-
-\begin{rem}
-This theorem indicates that a solution with proper compactly supported initial data coverges to translations of periodic traveling waves with profiles $w_1(x)$ and $w_2(x)$ in the positive direction and profiles $w_1(-x)$ and $w_2(-x)$ in the negative direction.
-\end{rem}
-
-\subsection{Blossoming solution}
-
-In addition to the behavior mentioned earlier, we noticed the phenomena of blossoming solution. Whenever
-
-\section{Examples}
-
-In this section, we construct the periodic traveling wave solution for several well-known disperal kernels in population biology, namely the uniform, Laplace, and normal distributions.
-For the uniform and Laplace kernels, we were able to construct a piecewise expression for the mean wave speed in terms of the model parameters.
-
-\begin{ex}
-The Laplace kernel is given by
-\begin{equation}\label{laplacekernel}
-k(x) = \frac{1}{2} e^{-|x|}
-\end{equation}
-
-The reader can easily verify that the Laplace kernel satisfies hypotheses (H1) - (H3); the proof of (H4) is left in the appendix \ref{laplaceproof}.
-
-The periodic traveling wave profiles are given by
-
-\begin{equation} \label{w1laplace}
-w_1(x) =   \begin{cases} 
-n_2 - \frac{1}{2} n_2 e^{x} & x \leq 0 \\
-\frac{1}{2} n_2 e^{-x} & x > 0
-\end{cases}
-\end{equation}
-and
-%\begin{equation}\label{laplacew2}
-%w_2(x) = \begin{cases}
-%m - \frac{1}{2} e^{x - \alpha} + \frac{1-\m}{2} e^{x - \beta} & x < \beta \\
-%1 - \frac{1}{2} e^{x-\alpha} - \frac{1-\m}{2} e^{-(x-\beta)} & \beta \leq x \leq \alpha \\
-%\frac{1}{2} e^{-(x-\alpha)} - \frac{1-\m}{2} e^{-(x-\beta)} & x > \alpha
-%\end{cases}
-%\end{equation}
-%\begin{equation} \label{w2laplace}
-%w_2(x) = \begin{cases}
-%m + C_1 e^x & x < x_\b \\
-%1 - C_2 e^x - C_3 e^{-x} & x_\b \leq x \leq x_\a \\
-%C_4 e^{-x} & x_\a < x 
-%\end{cases} \end{equation}
-%or equivalently
-
-\begin{equation} \label{w2laplace}
-w_2(x) = \begin{cases}
-\m + \left( \frac{1}{2}(\mtwo-\m)e^{-x_\b} - \frac{1}{2}\mtwo e^{-x_\a} \right) e^x & x < x_\b \\
-\mtwo - \frac{1}{2} \mtwo e^{-x_\a} e^x - \frac{1}{2} (\mtwo-\m) e^{x_\b}   e^{-x} & x_\b \leq x \leq x_\a \\
-\left( \frac{1}{2} \mtwo e^{x_\a} - \frac{1}{2}\mtwo(\mtwo-\m) e^{x_\b} \right) e^{-x} & x_\a < x 
-\end{cases} \end{equation}
-
-with $x_a = F(a)$, $x_b=F(b)$, and
-\begin{equation}
-F(p) = \begin{cases} -\ln(2p) &p \leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases}
-\end{equation}
 A necessary condition for formulas \eqref{w1laplace} and \eqref{w2laplace} to generate a periodic traveling wave solution are given in Lemma \ref{laplacebound}.
@@
 We can also explicitly calculate the speed of the wave given by
-\begin{equation} \label{c}
+\begin{equation} \label{clinear}
 c^* = \begin{cases}

### 2021-07-13 paper_draft8.tex
work

--- 2021-07-13 Nestor_Li_manuscript_revision_7_13.tex
@@
 
+ Let $w_1$ and $w_2$ be two functions defined by
+\begin{equation} \label{w1}
+w_1(x) := \int_x^\infty \mtwo k(y) \, dy
+\end{equation}
+and
+\begin{equation} \label{w2}
+w_2(x) = \int_x^\infty \left( \mtwo k(y-x_\a) - (\mtwo-\m)k(y-x_\b)\right) \, dy 
+\end{equation} 
+where $x_\a$ and $x_\b$ constants constants given by
+\begin{equation}
+x_\a =\sup\left\{x\in\mathbb R\mid \int_{-\infty}^{x} k(y) \, dy \leq \frac{\a}{\mtwo} \right\}, \quad
+x_\b =\sup\left\{x\in\mathbb R\mid \int_{-\infty}^{x} k(y) \, dy \leq \frac{\b}{\mtwo} \right\}
+\end{equation}
+
+\begin{thm} \label{theorem1}
+If $|| w_2 ||_\infty\leq \b$, then equation \eqref{q} has a periodic traveling wave solution given by %$(u_n)_{n=0}^{\infty}$ satisfying
+%\begin{equation} \label{ptw}
+%u_n(x) = \begin{cases}
+%w_1(x-nc^*) & n \text{ even} \\
+%w_2(x-nc^*) & n \text{ odd}
+%\end{cases}
+%\end{equation}
+
+\begin{equation} \label{ptw}
+u_n(x) = \begin{cases}
+w_1(x-nc^*) & n \text{ even} \\
+w_2(x-nc^*+c^*) & n \text{ odd}
+\end{cases}
+\end{equation}
+for all $n \geq 0$.
+\end{thm}
+
 \begin{lem} \label{lemmamain}
-Let $w(x) = \int_x^\infty k(y) \, dy$. Define
-\begin{equation}
-c^* = \frac{1}{2} \sup \{ x\in\mathbb R | Q[\mtwo w](x) \geq \a \}
-\end{equation}
-Let $w_1(x) = w(x)$ and $w_2(x) = Q[w](x+c^*)$. If $|| w_2 ||_\infty \leq \b $, then $w_1$ and $w_2$ satisfy
-\begin{equation} \label{lemma1claim1}
-Q[w_1](x) = w_2(x-c^*)
+If $ || w_2 ||_\infty \leq \b $, then $w_1$ and $w_2$ satisfy
+\begin{equation}
+Q[w_1](x) = w_2(x)
 \end{equation}
 and
-\begin{equation}\label{lemma1claim2}
-Q[w_2](x) = w_1(x-c^*)
-\end{equation}
-for all $x \in \mathbb R$.
+\begin{equation}
+Q[w_2](x) = w_1(x-2c^*)
+\end{equation}
+for all $x\in\mathbb R$, where $c^*$ is a constant given by
+\begin{equation} \label{c}
+c^* = \frac{1}{2} \sup\{x\in\mathbb R\mid w_2(x)\geq \a\}
+\end{equation}
 \end{lem}
 
+%
 %
@@
 \begin{proof}
-Equation \ref{lemma1claim1} follows directly from the definition of $w_2(x)$.
-
-To prove \ref{lemma1claim2}, observer that $w_1$ is monotonically decreasing with $w_1(-\infty)=\mtwo$ and $w_1(\infty)=0$.
-It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$, where $x_a$ and $x_b$ are the solutions of
-\begin{equation}
-w_1(x_\a) = \a, \quad w_1(x_\b) = \b
-\end{equation}
+$w_1$ is monotonically decreasing with $w_1(-\infty)=\mtwo$ and $w_1(\infty)=0$.
+It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$.
 This yields
@@
 It can be shown by cases that $w_2$ is either monotonically decreasing or has a unique turning point $x_0 \in \mathbb R$.
-In both cases, the curve $u=w_2(x)$ crosses the horizontal line $u=\a$ exactly once at the point $x=2c^*$.
-In the latter case, we utilize the assumption that $|| w_2 ||_\infty \leq \b$ .
-In all cases,
+In both cases, the curve $u=w_2(x)$ crosses the horizontal line $u=\a$ exactly once at the point $x=2c^*$, where $c^*$ is defined by \eqref{c}.
+In the latter case, we make the additional assumption that $|| w_2 ||_\infty \leq \b$ .
+In all the cases,
 
@@
 
-\begin{thm} \label{theorem1}
-Let $u_n(x)$ be a sequence of functions defined by
-\begin{equation}
-u_n(x) = \begin{cases} \label{ptw}
-w_1(x-nc^*) & n \text{ even} \\
-w_2(x-nc^*) & n \text{ odd}
-\end{cases} \end{equation}
-If $|| w_2 ||_\infty \leq \b $, then $u_n(x)$ satisfies $u_{n+1}(x) = Q[u_n](x)$ for all $n\geq 0$.
-\end{thm}
-
-\begin{proof}
-Let $n \geq 0$. If $n$ is even, then $n+1$ is odd, so $u_n(x)=w_1(x-nc^*)$ and $u_{n+1}(x)=w_2(x-nc^*)$. Applying the integro-difference operator, we obtain
+\begin{proof}[Proof of Theorem \ref{theorem1}]
+It suffices to show that equation \eqref{ptw} satisfies $u_{n+1}=Q[u_n]$ for all $n \geq 0$.
+If $n$ is even, then $n+1$ is odd, so $u_n(x)=w_1(x-nc^*)$ and $u_{n+1}(x)=w_2(x-nc^*)$.
+Applying the integro-difference operator, we obtain
 \begin{equation} \begin{aligned}
@@
 
-$$
-w_i(x) = \int_\Omega k(x-y+2c^*) g\left( \int_\Omega k(y-y') g(w_i(y')) \, dy' \right) \, dy
-$$
 For every $n\geq 1$, let $c_n = \xi_n - \xi_{n-1}$.
@@
 \begin{thm}  \label{theorem2}
-If $||w_2|| \b$, then for all $\epsilon>0$, the sequence \ref{ptw} satisfies
-\begin{equation}
-\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n}(x)=\mtwo
+If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then for all $\epsilon>0$, the sequence \ref{ptw} satisfies
+\begin{equation}
+\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n}(x)=1
 \end{equation}
@@
 
-\textbf{Note: this section contains incomplete results.}
-
-In this section, we consider how the periodic traveling wave solutions in the preceding results correspond to solutions with a compactly supported initial population density.
-For simplicity, we restrict our attention to initial conditions where the maximum population value does not exceed the overcompensation threshold.
-
-Let $\chi_{[-r,r]}$ denote the indicator function on $[-r,r]$.
-Suppose $u_0$ is a continuous function with compact support, and suppose $u_0$ satisfies $\a \leq u_0(x) \leq \b$ for $|x| \leq r$ and $u_0(x) < \a$ otherwise.
-It follows that
-$$ g(u_0(x)) = \chi_{[-r,r]}(x) $$
-
-%
-%Let $u_n(x)$ be a sequence of continuous functions. For every $c \in \mathbb R$, define the sequence $a_n(x,c)$ by
-%$$ a_n(x,c) = u_n(x+nc) $$
-%Now, define
-%$$ a(x,c) = \limsup_{n\to\infty} a_n(x,c). $$
-%Note that since $a_n$ is bounded, this quantity must be finite. We say the rightware spreading speed of $u_0$ is defined by
-%$$ c^*_+ = \inf \{ c \in \mathbb R \mid \lim_{x\to\infty} a(x,c) = 0 \} $$
-%
-%\begin{lem}
-%If $||w_2||_\infty\leq\b$, the sequence \eqref{ptw} has a rightward spreading speed of $c^*$.
-%\end{lem}
-%
-%\begin{proof}
-%We have
-%$$ a_n(x,c) = \begin{cases}
-%w_1(x + n(c-c^*))  & n \text{ even} \\
-%w_2(x + n(c-c^*)) & n \text{ odd}
-%\end{cases} $$
-%Thus,
-%$$ \begin{aligned}
-%a(x,c) &= \limsup_{n\to\infty} a_n(x,c) \\
-%&= \limsup_{n\to\infty} \max \{ w_1(x + n(c-c^*)), w_2(x + n(c-c^*)) \} \\
-%&= \begin{cases}
-%1 & c < c^* \\
-%\max\{w_1(x),w_2(x)\} & c=c^* \\
-%0 & c>c^*
-%\end{cases} \end{aligned} $$
-%Taking the limit as $x\to\infty$,
-%$$ a(\infty,c) = \begin{cases}
-%1 & c < c^* \\
-%0 & c \geq c^*
-%\end{cases} $$
-%\end{proof}
-
-For a given $r \geq 0$, let $\phi(x,r) = \chi_{[-r,r]}(x)$, or simply $\phi_r$ for brevity. Define the operator $R[u] = g\left( Q[k*u](x) \right)$.
+Let $u_n(x)$ be a sequence of continuous functions. For every $c \in \mathbb R$, define the sequence $a_n(x,c)$ by
+$$ a_n(x,c) = u_n(x+nc) $$
+Now, define
+$$ a(x,c) = \limsup_{n\to\infty} a_n(x,c). $$
+Note that since $a_n$ is bounded, this quantity must be finite.
+
+We say the rightware spreading speed of $u_0$ is defined by
+$$ c^*_+ = \inf \{ c \in \mathbb R \mid \lim_{x\to\infty} a(x,c) = 0 \} $$
+
+\begin{thm}
+Let $w(x) = \int_x^\infty k(y) \, dy$. Define
+$$ c^* = \frac{1}{2} \sup \{ x\in\mathbb R | Q[w](x) \geq \a \} $$
+Let $w_1(x) = w(x)$ and $w_2(x) = Q[w](x+c^*)$. Define the sequence
+$$ u_n(x) = \begin{cases}
+w_1(x-nc^*) & n \text{ even} \\
+w_2(x-nc^*) & n \text{ odd}
+\end{cases} $$
+Then $u_n(x)$ satisfies $u_{n+1}(x) = Q[u_n](x)$ for $n\geq 0$ and has a rightward spreading speed of $c^*$.
+\end{thm}
+
+\begin{proof}
+We have
+$$ a_n(x,c) = \begin{cases}
+w_1(x + n(c-c^*))  & n \text{ even} \\
+w_2(x + n(c-c^*)) & n \text{ odd}
+\end{cases} $$
+Thus,
+$$ \begin{aligned}
+a(x,c) &= \limsup_{n\to\infty} a_n(x,c) \\
+&= \limsup_{n\to\infty} \max \{ w_1(x + n(c-c^*)), w_2(x + n(c-c^*)) \} \\
+&= \begin{cases}
+1 & c < c^* \\
+\max\{w_1(x),w_2(x)\} & c=c^* \\
+0 & c>c^*
+\end{cases} \end{aligned} $$
+Taking the limit as $x\to\infty$,
+$$ a(\infty,c) = \begin{cases}
+1 & c < c^* \\
+0 & c \geq c^*
+\end{cases} $$
+\end{proof}
+
+For a given $r \geq 0$, let $\phi(x,r) = \chi_{[-r,r]}(x)$, where $\chi$ is the indicator function, or simply $\phi_r$ for brevity. Define the operator $R[u] = g\left( Q[k*u](x) \right)$.
 
@@
 $$ \delta(r) = \int R[\phi_r](x)  \, dx $$
+\end{lem}
+
+\begin{lem}
+$\lim_{r\to\infty} \delta(r) = 2c^* $
+\end{lem}
+
+Consider the sequence $A_n(x,r)=R^n[\phi_r](x)$.
+
+\begin{lem}
+If $r$ is sufficiently large, then $A_1(x,r)=R[\phi_r](x) = \phi_{r+\delta(r)}(x)$. Similarly, $A_2(x,r) = \phi_{r+\delta(r)+\delta(r+\delta(r))}$.
+\end{lem}
+
+Consider the sequence $\xi_n$ defined by $\xi_0 = r_0$ and $\xi_{n+1} = \xi_n + \delta(\xi_n)$. Then $\xi_n = 2c^*n + O(1)$.
+
+Consider the operator $R[u] = g \circ (k * u)$. Observer that $k*R[g \circ u] = Q^2 [u]$; equivalently $g \circ Q[k*u] = R^2[u]$.
+
+Or just define dimensionless parameters $a=A/N_2$, $b=B/N_2$, and $m = N_1/N_2$.
+
+For each $r \geq 0$, let $\phi_r = \chi_{[-r,r]}$, where $\chi$ is the indicator function.
+
+\begin{lem}
+If $r$ is sufficiently large, then $R^2[\phi_r] = \phi_s$, where $s=s(r)$ is a function of $r$, and $\lim_{r\to\infty}(s-r) = 2c^*$.
 \end{lem}
@@
 In both cases, there is a unique $r_3>0$ satisfying $(k*R[\phi_r])(x) \geq \a$ for $|x| \leq r_3$ and $(k*R[\phi_r])(x) < \a$ otherwise.
-
-\textbf{Note: the above section contains unfinished proofs.}
+If $r_3 < r$, then the conclusion does not follow.
+But if $r_2 \geq r$, then the
+$$
+\delta (r) = || Q[\chi_{[-r,r]}] ||_1 = \int_{-\infty}^{\infty} Q[\chi_{[-r,r]}](x) \, dx
+$$
+
+\begin{lem}
+$ \lim_{r \to \infty} ( \delta(r) - r ) = 4c^* $
+\begin{equation}
+\lim_{r\to\infty} \left( \left( \int_{-\infty}^{\infty}Q^2[\chi_{[-r,r]}(x) \, dx \right) -r \right) = 4c^* 
+\end{equation}
+\end{lem}
+
+In this section, we consider how the periodic traveling wave solutions in the preceding results correspond to solutions with a compactly supported initial population density.
+For simplicity, we restrict our attention to initial conditions where the maximum population value does not exceed the overcompensation threshold.
+
+Let $\chi_{[-r,r]}$ denote the indicator function on $[-r,r]$.
+Suppose $u_0$ is a continuous function with compact support, and suppose $u_0$ satisfies $\a \leq u_0(x) \leq \b$ for $|x| \leq r$ and $u_0(x) < \a$ otherwise.
+It follows that
+$$ g(u_0(x)) = \mathbf 1_{[-r_0,r_0]}(x) $$
+We have
+$$ Q[u_0](x) = (k*(g \circ u_0))(x) = K(x+r_0) - K(x-r_0) $$
+Assuming $r_0$ is large enough so that $ Q[u_0](x) = 2K(r_0)-1 \geq \b$, it follows that
+$$ g(Q[u_0](x)) = \begin{cases}
+n_1 & |x| < r_1 \\
+n_2 & r_1 \leq |x| \leq r_2 \\
+0 & |x| > r_2
+\end{cases} $$
+It follows that
+$$ Q^2 [u_0] (x) = n_2 \int_{-r_2}^{r_2} k(x-y)\,dy - (n_2-n_1) \int_{-r_1}^{r_1} k(x-y) \, dy $$
+$$ = n_2 K(x+r_2) - n_2K(x-r_2) - (n_2-n_1) K(x+r_1) + (n_2-n_1) K(x-r_1) $$
+Taking the derivative, we find
+$$ \frac{d}{dx} Q^2 [u_0](x) = n_2 k(x+r_2) - n_2k(x-r_2) - (n_2-n_1) k(x+r_1) + (n_2-n_1) k(x-r_1) $$
+
+We now require the following hypothesis on the disperal kernel:
+
+(H5) For all $r_2>r_1>0$ and $\lambda \in (0,1)$, the equation
+$$ k(x+r_2) - k(x-r_2) - \lambda k(x+r_1) + \lambda k(x-r_1) = 0 $$
+has at most 3 solutions.
+
+If hypothesis (H5) holds, we can then deduce that $\frac{d}{dx}Q^2[u_0]$ has at most 3 zero-crossings, hence, $Q^2[u_0]$ has at most 3 turning points.
+This leaves only two cases: either $Q^2[u_0]$ has a single turning point at $x=0$, or $Q^2[u_0]$ has 3 turning points, one at $x=0$, and two diametrically opposed turning points $+t$ and $-t$.
+In both cases, there is a unique $r_2>0$ satisfying $Q^2[u_0](x) \geq \a$ for $|x| \leq r_2$ and $Q^2[u_0](x) < \a$ otherwise.
+If $r_2 < r$, then the conclusion does not follow.
+But if $r_2 \geq r$, then the
+
+The next theorem concerns the spreading behavior of solutions to the IDE \eqref{q} with compactly supported initial data.
 
@@
 \end{rem}
+
+\subsection{Blossoming solution}
+
+In addition to the behavior mentioned earlier, we noticed the phenomena of blossoming solution. Whenever
 

### 2021-07-13 untitled-3.tex
work

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass[11pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{enumerate}
%\usepackage{caption,subcaption}
\usepackage{caption}
%\usepackage{subcaption}

%\usepackage{newpxtext,newpxmath}
\usepackage{multicol}

%\theoremstyle{definition}
\newtheorem{thm}{Theorem}
\newtheorem{cor}{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\theoremstyle{definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{ex}[thm]{Example}

\numberwithin{equation}{section}
\numberwithin{thm}{section}

%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

\usepackage{graphicx} % support the \includegraphics command and options

% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

%%% SECTION TITLE APPEARANCE
\usepackage{sectsty}
\allsectionsfont{\sffamily\mdseries\upshape} % (See the fntguide.pdf for font help)
% (This matches ConTeXt defaults)

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

\newcommand{\winva}{{w_1^{-1}(a)}}
\newcommand{\winvb}{{w_1^{-1}(b)}}
\renewcommand{\a}{a}
\renewcommand{\b}{b}
\newcommand{\m}{n_1}
\newcommand{\mtwo}{n_2}

%%% END Article customizations

%%% The "real" document content comes below...

\title{Brief Article}
\author{The Author}
%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

\begin{document}
\maketitle

Let $\chi_B$ be the characteristic function on $\mathbb{R}$ given by $\chi_B(u)=1$ if $u\in B$ and $\chi_B(u)=0$ otherwise. Assume that $k$ is a bounded and periodic function, and 
$g$ is integrable with period $\phi(>0)$ and is differentiable at least $q-1$ times. In this paper we consider the following assumptions:

\begin{enumerate}
\item $k$ has sufficient decay;
\item $\b-\a>\phi(g)$ and $\b-\a<\frac{\phi(g)\phi(\chi_{[\a,\b]})}{\phi(g)-\phi(\chi_{[\a,\b]})};$
\item $\int^{\infty}_{-\infty}k(x-y)\chi_{[\a,\b]}(y)\,\mathrm{d}y<\int^{\infty}_{-\infty}k(x-y)\chi_{[\b,\infty)}(y)\,\mathrm{d}y$.
\end{enumerate}

The main results of this paper are the following theorems:

\begin{enumerate}
\item The condition $(i)$ and $(iii)$ imply that $k$ is symmetric with respect to $\a$ and $\b$.
\item If $\a-\b>0$, then $g$ is nondecreasing.
\item $u_c=\frac{2\a\b}{\a+\b}$ is the spreading speed for  $g=k+\a-\b$ and $\a+\b>0$. 
$u_c$ is the asymptotic velocity of a spreading mode, and is well defined if the integral of $g$ is finite and positive.
\item There is a unique spreading mode if $\a-\b>0$ and $\int^{\infty}_{-\infty}g(x)\,\mathrm{d}x$ is finite.
\item If $\a-\b<0$, then $g$ is nonmonotone and $g$ has at most one minimum
\end{enumerate}
\end{document}

### 2021-08-11 Nestor_Li_manuscript_v2.tex
final

\documentclass[11pt]{article}

\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{caption}
\usepackage{subcaption}

\usepackage{multicol}

\theoremstyle{definition}
\newtheorem{thm}{Theorem}
\newtheorem{hyp}[thm]{Hypothesis}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{rem}[thm]{Remark}
\numberwithin{equation}{section}
\numberwithin{thm}{section}

\DeclareMathOperator\erf{erf}

\newcommand{\winva}{{w_1^{-1}(a)}}
\newcommand{\winvb}{{w_1^{-1}(b)}}
\renewcommand{\a}{a}
\renewcommand{\b}{b}
\newcommand{\m}{m}
\newcommand{\mtwo}{1}

\usepackage{authblk}

\title{Periodic Traveling Waves in an Integro-Difference Equation With a Nonmonotone Growth Function and Strong Allee Effect}
\date{}
\author{Michael Nestor and Bingtuan Li
\thanks{M. Nestor's email is \href{mailto:mdnest01@gmail.com}{mdnest01@gmail.com}. B. Li was partially supported by the National Science Foundation under Grant DMS-1515875 and Grant DMS-1951482.}}

\affil{Department of Mathematics, University of Louisville, \newline Louisville, KY 40292.}

\begin{document}

\maketitle
\begin{abstract}
Sufficient conditions are derived for the existence of a periodic traveling wave with two intermediate wave speeds for an integro-difference equation with a piecewise constant growth function exhibiting a period-2 cycle and a strong Allee effect. The mean traveling wave speed is shown to be the spreading speed of 
of solutions with compactly supported initial data under appropriate conditions. Case studies are conducted for the Laplace kernel and uniform kernel.
\end{abstract}

{\bf Key words:} Integro-difference equation, period two cycle, Allee effect, periodic traveling wave.
\newline

{\bf AMS Subject Classification:} 92D40, 92D25.

\section{Introduction}

Integro-difference equations in the form 
\begin{align}\label{q}
u_{n+1}(x)\;=\;Q[u_n](x)\;:=(k*(g\circ u_n))(x)\;=\,\int^{\infty}_{-\infty}k(x-y)\,g\big(u_n(y)\big)\,\mathrm{d}y,
\end{align}
are of great interest in the studies of invasions of populations with discrete generations and separate growth and dispersal stages. They have been used to predict changes in gene frequency \cite{lui82a, lui82b, lui83, slatkin, w78}, and applied to ecological problems~\cite{hh, ks, kot89, kot92, kotbook, lut, nkl,otto}. Previous rigorous studies on integro-difference equations have assumed that the growth function is nondecreasing~\cite{w78, wein82}, or  is nonmonotone without Allee effect~\cite{lui83, wang}. The results show existence of constant spreading speeds and travelng waves with fixed shapes and speeds.   Sullivan et al. ~\cite{pnas} demonstrated numerically  that an integro-difference equation with a nonmonotone growth function exhibiting  a strong Allee effect can generate traveling waves with fluctuating speeds, and Otto~\cite{otto} showed  that such an equation can have robust non-spreading solutions. In this paper we give conditions for the existence of a periodic traveling wave with two intermediate speeds for 
an integro-difference equation with a piecewise constant growth function that exhibits a strong Allee effect and a period-2 cycle.

Piecewise constant growth functions have been used in the studies of integro-difference equations; see for example~\cite{kot1, lut, otto,  pnas}. Such an equation 
is analytically tractable and it can provide specific insights into the dynamics of solutions.  For the piecewise constant growth function
\begin{equation} \label{g0}
g(u) = \begin{cases}
0, & \text{if } u < \a, \\
1, & \text{if } u \geq \a,
\end{cases}
\end{equation}
with $0<a<1$,  which exhibits a strong Allee effect and monotonicity,  Kot et al.~\cite{kot1} and Lutscher~\cite{lut} (Section 6.1) investigated the range expansion of the population and the spreading speed, and Sullivan et al. ~\cite{pnas} studied oscillations in spreading speeds when the dispersal kernel is density dependent. 
More discussions about integro-difference equations with piecewise growth functions can be found in Lutscher~\cite{lut} (Chapter 15).

In this paper, we consider the integro-difference equation (\ref{q}) with 
\begin{equation} \label{g}
g(u) = \begin{cases}
0, & \text{if } u < \a, \\
\mtwo, & \text{if } \a \leq u \leq \b, \\
\m, & \text{if } u > \b,
\end{cases}
\end{equation}
with $0<\a<\m<\b<1$. $g(u)$ is a piecewise constant nonmonotone growth function exhibiting a strong Allee effect~\cite{all}. Specifically, it has a stable fixed point at zero and a stable period two cycle $(1,\m)$ with $\a$ the Allee threshold value. This is the function considered in Otto~\cite{otto} where non-spreading solitions are studied. It may be viewed as an extension of (\ref{g0}).
  A graphical demonstration of $g$ defined by (\ref{g}) is given by Figure 1. 
\begin{figure}[h!]
\centering
  \caption{The growth of $g(u)$ defined by (\ref{g}) with  $0<\a<\m<\b<1$.}
  \includegraphics[width=.4\linewidth]{figures/fig1.jpg}
\end{figure}
We rigorously construct periodic traveling waves with two intermediate speed for (\ref{q}) with $g$ given by \eqref{g} and a proper dispersal kernel $k$. To the best of our knowledge, this is the first time that traveling waves with oscillating speeds have been analytically established  for scalar spatiotemporal equations with constant parameters. We also show that 
the mean traveling wave speed is  the spreading speed of 
solutions with compactly supported initial data under appropriate conditions.
 We finally conduct case studies for the Laplace kernel and uniform kernel.

\section{Results}

In this section, we present our main results about our model. Our assumptions about the dispersal kernel are summarized in the following hypothesis.

\begin{hyp}
$k(x)$ is a piecewise differentiable function satisfying
\begin{enumerate}[(H1)]
\item $k(x) \geq 0$ for all $x$, and $\int_{-\infty}^{\infty} k(x) \, dx = 1$, \label{h1}

\item $k(x)=k(-x)$ for all $x$,\label{h2}

\item $k(x)>0$ for all $x \in (-\sigma,\sigma)$ for some $0 < \sigma \leq \infty$,\label{h3}

\item  \label{h4}
for all $\lambda \in (0,1)$, for all $A,B\in\mathbb R$ with $A>B$, the expression
$$
k(x-A) - \lambda k(x-B)
$$
has $<2$ sign changes, and

\item \label{h5}
for all $\lambda \in (0,1)$, for all $A,B\in\mathbb R$ with $A>B$, the expression
$$
k(x-r-A) - \lambda k(x-r-B) - k(x+r+A) + \lambda k(x+r+B)
$$
has $<4$ sign changes for sufficiently large $r>0$.
\end{enumerate}
\end{hyp}

\subsection{Periodic traveling waves}

Let $w_1$ and $w_2$ be bounded, continuous functions defined by
\begin{equation} \label{w1}
w_1(x) :=\int_x^\infty k(y) \, dy
\end{equation}
and
\begin{equation} \label{w2}
w_2(x) := Q[w_1](x+c^*) =  \int_{-\infty}^{\infty} k(x+c^*-y) g(w_1(y)) \, dy
\end{equation}
where $c^*$ is a constant defined by
\begin{equation} \label{c}
c^* := \sup \{ x\in\mathbb R \mid w_2(x) = \a \}.
\end{equation}

\begin{thm} \label{theorem1}
Suppose $||w_2||_\infty < \b$. Let $v_n(x)$ be a sequence of functions defined by
\begin{equation}\label{ptw}
v_n(x) := \begin{cases}
w_1(x-nc^*), & n \text{ even}, \\
w_2(x-nc^*), & n \text{ odd},
\end{cases}
\end{equation}
for all $n \geq 0$. Then $v_n(x)$ is a periodic traveling wave (PTW) with mean wave speed $c^*$, and satisfies $v_{n+1}=Q[v_n]$ for all $n\geq0$.
\end{thm}

\begin{proof}
For each $i \in \{1,2\}$ we define the right inverse of $w_i$ by
\begin{equation}
\Phi_i(\ell) := \sup \{ x \in \mathbb R \mid w_i(x) = \ell \}, \quad i=1,2.
\end{equation}
Note that $\Phi_i(u)$ is finite for $0<\ell<||w_i||_\infty$, where $||w_1||_\infty=1$, and $\a<||w_2||_\infty<\b$ by the assumption of this theorem.

By the translation invariance property of $Q$, it suffices to show
\begin{equation} \label{qw1}
Q[w_1](x) = w_2(x-c^*)
\end{equation}
and
\begin{equation} \label{qw2}
Q[w_2](x) = w_1(x-c^*)
\end{equation}
for all $x \in \mathbb R$. The first equation follows immediately from definition \eqref{w2}. To prove the second, observe that $w_1$ is monotonically decreasing and satisfies $w_1(\infty)=0$ and $w_1(-\infty)=1$. Thus,
$$
g\circ w_1(x) = \begin{cases}
\m, & x < \Phi_1(\b), \\
1, & \Phi_1(\b) \leq x \leq \Phi_1(\a), \\
0, & x > \Phi_1(\a).
\end{cases}
$$
Applying the integro-difference operator yields
$$ \begin{aligned}
w_2(x-c^*) &= Q[w_1](x) \\
&= \m \int_{-\infty}^{\Phi_1(\b)} k(x-y) \, dy + \int_{\Phi_1(\b)}^{\Phi_1(\a)} k(x-y) \, dy \\
&= w_1(x-\Phi_1(\a)) - (1-\m) w_1(x-\Phi_1(\b)).
\end{aligned}$$
We can then differentiate with respect to $x$:
$$
\frac{dw_2}{dx} \Big| _{x-c^*}= - k(x-\Phi_1(\a)) + (\mtwo-\m) k(x-\Phi_1(\b)).
$$
From hypothesis \ref{h4}, $\frac{dw_2}{dx}$ has at most 1 sign change; thus, $w_2$ has at most 1 turning point. We also have $|| w_2 || _\infty <  \b$ hence $g\circ w_2(x) \in \{0, 1 \}$ for all $x$. We claim
\begin{equation} \label{gw2}
g\circ w_2(x) = \begin{cases}
1, & x \leq c^*, \\
0, & x > c^*,
\end{cases}
\end{equation}
where $c^*$ is defined by \eqref{c}. This can be shown by arguing in cases depending on the number of turning points of $w_2$.
\begin{enumerate}[{Case} 1.]
\item If $w_2$ has no turning points, then $w_2$ is monotone decreasing with $0 \leq w_2(x) \leq \m$ for all $x$. It follows by the intermediate value theorem (IVT) that $c^* = \Phi_2(\a)$ satisfies \eqref{gw2}.

\item If $w_2$ has one turning point, say $x_0 \in \mathbb R$, then $w_2$ must be  increasing for $x<x_0$ and decreasing for $x>x_0$. It follows that $x_0$ is a global maximum, and $w_2$ is increasing on $(-\infty,x_0)$ and decreasing on $(x_0,\infty)$. We have $g(w_2(x))=1$ for $x<x_0$. By the IVT, $c^* = \Phi_2(\a)$ is the unique solution to \eqref{gw2}.
\end{enumerate}
Taking the convolution of equation \eqref{gw2} with $k(x)$ yields
$$
Q[w_2](x) \,=\, \int_{-\infty}^{c^*} k(x-y) \, dy \,=\, w_1(x-c^*).
$$
\end{proof}

\begin{figure}
\begin{tabular}{cc}
  \includegraphics[width=65mm]{figures/fig7a.pdf} &   \includegraphics[width=65mm]{figures/fig7b.pdf}
\end{tabular}
\caption{Plot of $w_1(x)$ (left) and $w_2(x)$ (right) when $k(x)$ is the Laplace kernel (see Section 3). Blue points mark the intersection of the curves with the level sets $u=\a$ and $u=\b$.}
\end{figure}

Theorem \ref{theorem1} describes a rightward periodic traveling wave solution. We can define the corresponding leftward periodic traveling solution by $v_n(-x)$. This is due to the fact that $Q$ is symmetric and translation invariant.

We investigated the intermediate wave speed generated by the periodic traveling wave solution \eqref{ptw}. For this purpose, we define a sequence $\xi_n(\ell)$ depending on a fixed real number $\ell \in (0,\m)$ by

\begin{equation}
 \xi_n(\ell) = \sup \{ x \in \mathbb R : v_n(x) = \ell \}.
\end{equation}

The sequence $\xi_n$ is the rightmost intersection of the curve $u=v_n(x)$ with the horizontal line $u=\ell$. By computing the first difference of the sequence $\xi_n$, we obtain a new sequence $c_n(\ell)$ defined by
\begin{equation}
c_n(\ell) := \xi_{n+1}(\ell) - \xi_n(\ell).
\end{equation}
for $n \geq 0$.  It follows from Theorem \ref{theorem1} that $c_n(\ell)$ converges to a period-$2$ cycle for every $\ell \in (0,\m)$. Our results about the intermediate wave speed sequence is summarized in the following corollary.

\begin{cor}
The sequence $c_n(\ell)$ satisfies
\begin{equation}
c_n(\ell) = \begin{cases}
c_1^*(\ell), & n \text{ even}, \\
c_2^*(\ell), & n \text{ odd},
\end{cases}
\end{equation}
for all $\ell \in (0,\m)$, where $c_1^*(\ell)$ and $c_2^*(\ell)$ are given by
\begin{equation} \label{c1star}
c_1^*(\ell) := c^* + \Phi_1(\ell) - \Phi_2(\ell)
\end{equation}
and
\begin{equation} \label{c2star}
c_2^*(\ell) := c^* + \Phi_2(\ell) - \Phi_1(\ell).
\end{equation}
Furthermore, they satisfy the identity
\begin{equation}
c_1^*(\ell) + c_2^*(\ell) = 2c^*
\end{equation}
for all $\ell \in (0,\m)$.
\end{cor}

\begin{proof}
By Theorem \ref{theorem1}, we have
$$ \begin{aligned}
\xi_n(\ell) &= \begin{cases}
\sup\{x \in \mathbb R \mid w_1(x-nc^*) = \ell \}, & n \text{ even},\\
\sup\{x \in \mathbb R \mid w_2(x-nc^*) = \ell \}, & n \text{ odd},
\end{cases} \\
&= nc^* +  \begin{cases}
\Phi_1(\ell), & n \text{ even}, \\
\Phi_2(\ell), & n \text{ odd}.
\end{cases}
\end{aligned}
$$

Taking successive differences yields

$$ \begin{aligned}
c_n(\ell) &= \xi_n(\ell) - \xi_{n-1}(\ell) \\
&= nc^* +  \begin{cases}
\Phi_1(\ell), & n \text{ even}, \\
\Phi_2(\ell), & n \text{ odd},
\end{cases} - (n-1)c^* +  \begin{cases}
\Phi_2(u), & n \text{ even}, \\
\Phi_1(u), & n \text{ odd}
\end{cases} \\
&= c^* + \begin{cases}
\Phi_1(\ell) - \Phi_2(\ell), & n \text{ even}, \\
\Phi_2(\ell) - \Phi_1(\ell), & n \text{ odd}.
\end{cases}
\end{aligned} $$
\end{proof}

Thus, $\eqref{q}$ has a periodic traveling wave with wave profiles $w_1(x)$ and $w_2(x)$, intermediate wave speeds $c_1^*(\ell)$ and $c_2^*(\ell)$,  and average wave speed  $c^*$. Note that the intermediate wave speeds depend on the level $\ell$ at which they are measured, but their sum is given by the constant $2c^*$.

\subsection{Spreading solutions}

By applying the results of Theorem \ref{theorem1}, we were able to prove the asymptotic spreading speed of solutions with compact initial data. In particular, we showed that $c^*$ is the asymptotic spreading speed of initial data with sufficiently large weight above the Allee threshold but below the overcompensation threshold.

\begin{thm} \label{theorem2}
Suppose that the initial condition $u_0(x)$ of recurrence \eqref{q} is continuous, has compact support, satisfies $|| u_0 || _\infty < \b$, and that the set $A = \{ x \in \mathbb R : u_0(x) \geq \a \}$ is connected. If
\begin{enumerate}[i.]
\item $||w_2|| _\infty < \b$,
\item the diameter of $A$ is sufficiently large, and 
\item $c^* > 0$,
\end{enumerate}
then the sequence $u_n(x)$ spreads asymptotically with mean speed $c^*$ as $n\to\infty$.
\end{thm}

\newcommand{\what}{\tilde{w_1}}
\newcommand{\whattwo}{\tilde{w_2}}
\newcommand{\whatgen}{\tilde{w}}

\begin{proof}
We define two multivariate functions $\what,\whattwo : \mathbb R \times [0,\infty)\to\mathbb R$ by
\begin{equation}
\what(x,r) := w_1(x) - w_1(x+2r) = \int_{-2r}^{0} k(x-y) \, dy
\end{equation}
and
\begin{equation}
\whattwo(x,r) := Q[\what](x+c^*).
\end{equation}
Observe that $\what$ is symmetric with respect to $x=-r$, and $\whattwo$ is symmetric with respect to $x=-r-c^*$. This notation can be justified by observing that $\what(x,r) \to w_1(x)$ and $\whattwo(x,r)\to w_2(x)$ as $r\to\infty$ for all $x$. We also set
\begin{equation}
\phi_i(r,\ell) := \sup \{ x \in \mathbb R \mid \whatgen_i(x,r) = \ell \}, \quad i=1,2.
\end{equation}
$\phi_1$ and $\phi_2$ are the right-inverse of $\what$ and $\whattwo$, respectively. For a fixed $r>0$, the value of $\phi_i(r,\ell)$ is finite if $0 < \ell < || \whatgen_i(\cdot, r) || _\infty$, with the latter bound converging to $||w_i||_\infty$ as $r\to\infty$. They satisfy
$$
\lim_{r\to\infty} \phi_i (r,\ell) = \Phi_i(\ell) , \quad 0 < \ell < || w_i ||_\infty, \quad i=1,2.
$$

We now apply the growth function to $\what$, assuming $r$ is sufficiently large enough so that $\a < ||\what(\cdot,r)||_\infty < \b$; this is guaranteed by taking $r >  \Phi_1\left(\frac{1-a}{2}\right)$. We have
$$
g \circ \what(x,r)  = \begin{cases}
0, & x < -2r - \phi_1(r,a), \\
1, & -2r - \phi_1(r,a) < x < -2r - \phi_1(r,b), \\
\m, & -2r - \phi_1(r,b) < x < \phi_1(r,b),\\
1, & \phi_1(r,b) < x < \phi_1(r,a), \\
0, & x > \phi_1(r,a).
\end{cases} $$
Note that the above expression converes to $g \circ w_1(x)$ as $r\to\infty$. We then apply the convolution operator:
$$\begin{aligned} 
\whattwo(x-c^*,r) = Q[\what(\cdot,r)](x) &= \int_{-2r-\phi_1(r,a)}^{\phi_1(r,a)} k(x-y) \, dy - (1-\m) \int_{-2r-\phi_1(r,b)}^{\phi_1(r,b)} k(x-y) \, dy \\
&= w_1(x-\phi_1(r,a)) - (1-\m) w_1(x-\phi_1(r,b)) \\
&+ (1-\m) w_1(x+2r+\phi_1(r,b)) - w_1(x+2r+\phi_1(r,a)).
\end{aligned}$$
Computing the derivative of this expression yields
$$\begin{aligned} \label{qhatcomputation2}
\frac{d\whattwo}{dx}\Big|_{x-c^*} &= -k(x-\phi_1(r,a)) + (1-\m) k(x-\phi_1(r,b)) \\
& - (1-\m) k(x+2r+\phi_1(r,b)) + k(x+2r+\phi_1(r,a)).
\end{aligned}$$

By hypothesis \ref{h5}, the number of turning points of $\whattwo$ is at most 3 (assuming $r$ is sufficiently large). Furthermore, $\whattwo$ is symmetric around $x=-r-c^*$; thus the sign changes must come in pairs or occur exactly at $x=-r-c^*$. We can immediately exclude the cases of 0 and 2 turning points because $\whattwo$ is non-negative, vanishes at $\pm\infty$, and is not identically zero. As in the proof of Theorem \ref{theorem1}, this leaves two cases:
\begin{enumerate}[{Case} 1.]

\item If $\whattwo$ has 1 turning point, then it must occur at $x=-r-c^*$. We have $\whattwo(-r-c^*,r) = w_2(-r-c^*) - w_2(r+c^*) \to \m$ as $r \to \infty$; hence, it is sufficient to take $r$ large enough so that $|\whattwo(-r-c^*,r) - \m| < \min\{|\a-\m|,|\b-\m|\}$; it follows by the triangle inequality that $\whattwo(x,r) \leq \whattwo(-r-c^*,r) < \b$ for all $x$.

\item If $\whattwo$ has 3 turning points, then again by symmetry, they must be given by $\{-r-c^*-t, -r-c^*, -r-c^*+t\}$, for some $t>0$. We can label them in increasing order by $t_1<t_2<t_3$. It follows that $t_1$ and $t_3$ are maxima with $\whattwo(t_1,r)=\whattwo(t_3,r) \to ||w_2||_\infty$ as $r\to\infty$, and $t_2$ is a local minima with $\whattwo(t_2,r) \to \m$ as $r\to\infty$. Thus $\whattwo$ is monotone increasing on $(-\infty,t_1)\cup(t_2,t_3)$ and monotone decreasing on $(t_1,t_2)\cup(t_3,\infty)$. By taking $r$ sufficiently large, we can make $\left| \whattwo(t_1,r)-||w_2||_\infty \right| = \left| \whattwo(t_3,r)-||w_2||_\infty \right| < \left| \b-||w_2||_\infty \right| $ and $\left| \whattwo(t_2,r)-\m \right| < \left| \a-\m \right|$.
\end{enumerate}

In both cases, we have $\a \leq \whattwo(x,r) \leq \b$ on a closed interval of radius $r + c^* + \phi_2(r,a)$ and $\whattwo(x,r) < a$ elsewhere. Taking composition with $g$ yields
$$
g \circ \whattwo(x-c^*,r)  = \begin{cases}
0, & x < -2r - c^* -\phi_2(r,\a), \\
1, & -2r - c^* -\phi_2(r,\a) \leq x \leq  c^* + \phi_2(r,\a) ,\\
0, & x > c^* + \phi_2(r,\a).
\end{cases}
$$
Hence,
$$ \begin{aligned}
Q^2 [\what(\cdot,r)] (x)  &= w_1(x-c^* - \phi_2(r,a)) - w_1(x+2r+c^*+\phi_2(r,a)) 
\end{aligned} $$
Shifting the expression left by $c^*+\phi_2(r,a)$ units yields
\begin{equation} \begin{aligned} \label{appliedqtwice}
Q^2 [\what(\cdot,r)] (x+c^*+\phi_2(r,a)) 
&=  \what(x, r+c^*+\phi_2(r,\a)).
\end{aligned} \end{equation}

We are now prepared to prove the theorem using an inductive argument. Let $A$ be the level set defined in the statement of the theorem. Without loss of generality, we write $A=[-r_0,r_0]$, for some $r_0>0$. Hence
$$
g \circ u_0(x) = \begin{cases}
1, & -r_0 \leq x \leq r_0, \\
0, & \text{else}.
\end{cases}
$$
Applying the convolution operator yields
$$ \begin{aligned}
u_1(x) &= w_1(x-r_0) - w_1(x+r_0) \\
&= \what(x-r_0,r_0)
\end{aligned}
$$

Let $(r_n)_{n=0}^{\infty}$ be a sequence of real numbers satisfying
\begin{equation} \label{recurrence}
r_{n+1} = r_n + c^* + \phi_2(r_n,a).
\end{equation}

If $r_0$ is sufficiently large, we can show that $r_n$ is strictly increasing and unbounded. This is due to our assumption that $c^*>0$. Since $\phi_2(r,a)\to c^*$, it suffices to assume  $|\phi_2(r,a)-c^*|<c^*$, i.e. $r_0$ is sufficieintly large so that $\phi_2(r,a)>0$ for all $r>r_0$. Plugging this into the recurrence \eqref{recurrence} yields $r_{n+1}-r_n = c^* + \phi_2(r,a) > c^* > 0$.

This argument shows that, assuming $r_0$ is sufficiently large, equation \eqref{appliedqtwice} may be applied inductively. From the principle of induction, it follows that
$$
u_{2n+1}(x) = \what(x-r_n,r_n)
$$
for all $n \geq 0$. Knowing that $(r_n)$ is unbounded allows us to use equation \eqref{recurrence} to compute the asymptotic spreading speed as the difference of successive radii:
$$
\lim_{n\to\infty} (r_{n+1}-r_n) = \lim_{n\to\infty} (c^* + \phi_2(r_n,a)) = \lim_{r\to\infty} ( c^* + \phi_2(r,a)) = 2c^*.
$$

\end{proof}

\section{Examples}

In this section, we construct the periodic traveling wave solution for uniform and Laplace kernels, as well as compute expressions for the mean wave speed as well as intermediate wave speeds in terms of the model parameters.

\subsection{Laplace kernel} 
We applied our main results to the Laplace dispersal kernel given by
\begin{equation} \label{laplacekernel}
k(x) = \frac{1}{2} e^{-|x|}
\end{equation}

$k(x)$ is symmetric and has connected support, satisfying hypotheses \ref{h1}, \ref{h2}, and \ref{h3}. We will now prove that $k(x)$ satisfies hypothesis \ref{h5}. Let $A,B\in\mathbb R$ with $A>B$, let $\lambda \in (0,1)$, and define $f(x) = k(x-A) - \lambda k(x-B)$. For $r>0$ sufficiently large, we have
$$
f(x-r) - f(-x-r) = k(x-r-A) - \lambda k(x-r-B) - k(x+r+A) + \lambda k(x+r+B)
$$
$$=  \begin{cases}
\frac{1}{2} e^{x}\left(-e^{r+A}+me^{r+B}-me^{-r-B}+e^{-r-A}\right) , & x < -r-A, \\
\frac{1}{2}e^{-x}e^{-r-A}+\frac{1}{2}e^{x}\left(e^{-r-A}-me^{-r-B}+me^{r+B}\right) , & -r-A \leq x \leq -r-B, \\
\frac{1}{2}e^{-x}\left(-e^{-r-A}+me^{-r-B}\right)+\frac{1}{2}e^{x}\left(-me^{-r-B}+e^{-r-A}\right) , & -r-B < x < r+B, \\
\frac{1}{2}e^{-x}\left(-e^{-r-A}+me^{-r-B}-me^{r+B}\right)+\frac{1}{2}e^{x}e^{-r-A}, & r+B \leq x \leq r+A \\
e^{-x}\left(-e^{-r-A}+me^{-r-B}-me^{r+B}+e^{r+A}\right), & x > r+A.
\end{cases}
$$

$f$ is monotone on $(-\infty,-r-A)\cup(r+A,\infty)$ with $f(\pm\infty)=0$; thus it cannot have any sign changes there. On each of the intervals $[-r-A,-r-B]$, $(-r-B,r+B)$, and $[r+B,r+A]$, $f$ has the form $Ce^x+De^{-x}$. Depending on the sign of $C$ and $D$, $f$ can have either one or zero sign changes on each interval. Summing over each interval, it follows that $f$ has at most $3$ sign changes. This proves hypothesis \ref{h5}; the proof of hypothesis \ref{h4} follows a similar argument.

 Assuming $||w_2||_\infty<b$, the periodic traveling wave profiles are given by

\begin{equation} \label{w1laplace}
w_1(x) =   \begin{cases} 
1 - \frac{1}{2} e^{x}, & \text{if } x \leq 0, \\
\frac{1}{2} e^{-x}, & \text{if } x > 0,
\end{cases}
\end{equation}
and
\begin{equation} \label{w2laplace}
w_2(x-c^*) = \begin{cases}
\m + \left( \frac{1}{2}(\mtwo-\m)e^{-\Phi_1(\b)} - \frac{1}{2} e^{-\Phi_1(\a)} \right) e^x, & x < \Phi_1(\b), \\
\mtwo - \frac{1}{2} e^{-\Phi_1(\a)} e^x - \frac{1}{2} (\mtwo-\m) e^{\Phi_1(\b)}   e^{-x}, & \Phi_1(\b) \leq x \leq \Phi_1(\a), \\
\left( \frac{1}{2}e^{\Phi_1(\a)} - \frac{1}{2}(\mtwo-\m) e^{\Phi_1(\b)} \right) e^{-x}, & \Phi_1(\a) < x, 
\end{cases} \end{equation}
with
\begin{equation} \label{laplacecstar}
c^* = \begin{cases}
\frac{1}{2} \ln \left( \frac{\exp(\Phi_1(\a)) -(\mtwo-\m)\exp(\Phi_1(\b))}{2\a} \right), & \a \leq u_a, \\
\frac{1}{2} \ln \left( e^{\Phi_1(\a)} \left( \mtwo - \a + \sqrt{(\mtwo-\a)^2-(\mtwo-\m)e^{\Phi_1(\b)-\Phi_1(\a)}}\right)\right), & \ell_a < \a < \ell_b, \\
\frac{1}{2} \ln \left( \frac{2(\m-\a)}{\exp(-\Phi_1(\a))-(\mtwo-\m)\exp(-\Phi_1(\b))}\right), & \a \geq u_b.
\end{cases}
\end{equation}
$\ell_a$ and $\ell_b$ are constants given by
\begin{equation}
\ell_a = \frac{1}{2}\left(1 - (\mtwo-\m) e^{\Phi_1(\b)-\Phi_1(\a)} \right), \quad 
\ell_b = \frac{1}{2} \left( 1+\m- e^{\Phi_1(\b)-\Phi_1(\a)} \right).
\end{equation}

The formulas for $\Phi_1$ and $\Phi_2$ are given by
\begin{equation}
\Phi_1(\ell) = \begin{cases} -\ln(2\ell), &\ell\leq \frac{1}{2}, \\ \ln(2-2\ell), & \ell > \frac{1}{2}, \end{cases}
\end{equation}
and
\begin{equation}
\Phi_2(\ell) = -c^* + \begin{cases}
\ln \left( \frac{\exp(\Phi_1(\a)) -(\mtwo-\m)\exp(\Phi_1(\b))}{2\ell} \right), & \ell \leq w_2(\Phi_1(\a)), \\
\ln \left( e^{\Phi_1(\a)} \left( \mtwo - \ell+ \sqrt{(\mtwo-\ell)^2-(\mtwo-\m)e^{\Phi_1(\b)-\Phi_1(\a)}}\right)\right), & w_2(\Phi_1(\a)) < \ell < w_2(\Phi_1(\b)), \\
\ln \left( \frac{2(\m-\ell)}{\exp(-\Phi_1(\a))-(\mtwo-\m)\exp(-\Phi_1(\b))}\right), & \ell\geq w_2(\Phi_1(\b)).
\end{cases}
\end{equation}
For a more explicit formula for $c^*$, see appendix \ref{laplacespeedcalculations}. The intermediate wave speeds can be determined analytically by $c_1^*(\ell) = c^* + \Phi_1(\ell) - \Phi_2(\ell)$ and $c_2^*(\ell)=c^* + \Phi_2(\ell) - \Phi_1(\ell)$.

Figure \ref{fig:laplacewave} shows a numerical simulation of \eqref{q} with Laplace dispersal kernel showing the propagation of the periodic traveling wave solution ($1 \leq n \leq 11$). Later timepoints are colored in red, with earlier timepoints colored in green. The parameters used were $\a=0.2$, $\m=0.3$, and $\b=0.8$. Based on our spreading speed formula, we have $c^*=\frac{1}{2}\ln\frac{59}{5}$.

Figure \ref{fig:laplacecompact1} shows the time series plot for the same growth parameters and a compact initial condition with initial radius $r_0 = 0.58$, and Figure \ref{fig:laplacecompact2} shows a plot of the sequence of intermediate wave speeds for the same experiment. The dashed line represents $c^*$, which is the asymptotic average of the sequence based on Theorem \ref{theorem2}. The dotted lines represent $c_1^*$ and $c_2^*$ (evaluated at $\ell=\a$) which are the respective limit inferior and limit superior of the sequence.

While we did not analytically determine the minimal spreading speed in the proof of Theorem \ref{theorem2}, numerical simulations with  $\a=0.2$, $\m=0.3$, and $\b=0.8$ (see Figures  \ref{fig:qmu1} and \ref{fig:qmu2}) show that the shape of $\whattwo$ satisfies our assumptions for large enough $r$.

\begin{figure}[h!]
\centering
  \includegraphics[scale=0.5]{figures/fig3.png}
\caption{Periodic traveling wave with Laplace dispersal kernel. Later timepoint are colored red, while earlier timepoints are colored green.}
\label{fig:laplacewave}
\end{figure}

\begin{figure}
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/fig_accelerating_wave.pdf}
\end{minipage}
\begin{minipage}{.5\textwidth}
  \centering
  \raisebox{2mm}{\includegraphics[width=\linewidth]{figures/fig_accelerating_wave2.pdf}}
\end{minipage}
\par
\medskip
\noindent
\begin{minipage}[t]{.49\textwidth}
  \centering
  \captionof{figure}{The first $15$ time steps of a spreading solution with Laplace dispersal kernel and compact initial data ($r_0=0.58$). }
  \label{fig:laplacecompact1}
\end{minipage}
\hfill
\begin{minipage}[t]{.49\textwidth}
  \centering
  \captionof{figure}{Time series plots of the sequence of intermediate wave speed $c_n(\ell)$. The horizontal blue lines represent the theoretical limiting values derived in Theorem \ref{theorem2}.}
  \label{fig:laplacecompact2}
\end{minipage}
\end{figure}

\begin{figure}
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/fig6a.png}
\end{minipage}
\begin{minipage}{.5\textwidth}
  \centering
  \raisebox{6mm}{\includegraphics[width=\linewidth]{figures/fig6b.png}}
\end{minipage}
\par
\medskip
\noindent
\begin{minipage}[t]{.49\textwidth}
  \centering
  \captionof{figure}{Heatmap of $\whattwo(x-r-c^*,r)$ with Laplace dispersal kernel.}
  \label{fig:qmu1}
\end{minipage}
\hfill
\begin{minipage}[t]{.49\textwidth}
  \centering
  \captionof{figure}{Surface plot of $\whattwo(x-r-c^*,r)$ with Laplace dispersal kernel.}
  \label{fig:qmu2}
\end{minipage}
\end{figure}

\subsection{Uniform kernel}

Consider the uniform dispersal kernel given by
\begin{equation}
k(x) = \begin{cases}
\frac{1}{2}, & \text{if } |x|\leq 1, \\
0, & \text{if } |x| > 1.
\end{cases} \end{equation}
Like the previous example, $k(x)$ is symmetric around zero. We can verify hypothesis \ref{h4} by letting $A>B$ and $\lambda \in (0,1)$ and defining $f(x)=k(x-A)-\lambda k(x-B)$. There are two cases:
\begin{enumerate}[{Case} 1.]
\item If $|A-B|<2$, then
$$
f(x) = \begin{cases}
0, & x \leq B-1, \\
-\frac{\lambda}{2}, & B-1 < x \leq A-1, \\
\frac{1-\lambda}{2}, & A-1 < x < B+1, \\
\frac{1}{2}, & B+1 \leq x < A+1 \\
0, & x \geq A+1.
\end{cases}
$$

\item If $|A-B| \geq 2$, then
$$
f(x) = \begin{cases}
0, & x \leq B-1, \\
-\frac{\lambda}{2}, & B-1 < x < B+1, \\
0, & B+1 \leq x \leq  A-1, \\
\frac{1}{2}, & A-1 < x < A+1 \\
0, & x \geq A+1.
\end{cases}
$$
\end{enumerate}
In both cases, the number of sign changes is exactly 1. To extend this argument to hypothesis \ref{h5}, observe that since $k(x)$ has compact support, we have
$$
\begin{aligned}
f(x-r) - f(r-x) &= k(x-r-A) - \lambda k(x-r-B) - k(x+r+A) + \lambda k(x+r+B) \\
&=  \begin{cases}
-f(r-x), & x < -r+1, \\
0, & -r+1 \leq x \leq r-1, \\
f(x-r), & x > r-1,
\end{cases}
\end{aligned}
$$
for sufficiently large $r$.

The alternating wave profiles are given by
\begin{equation}  \label{uniformw1}
\begin{aligned}
w_1(x) 
= \begin{cases}
1, & x \in (-\infty, -1), \\
\frac{1}{2}-\frac{1}{2}x, & x \in [-1, 1] ,\\
0, & x \in (1, \infty),
\end{cases}
\end{aligned} \end{equation}
and 
\begin{equation} \label{uniformw2}
\begin{aligned}
w_2(x+c^*)
= \begin{cases}
m,
& x \in (-\infty, -2\b), \\
\frac{1-m}{2}x + m + b - mb,
& x \in [-2\b, 
 -2\a), \\
-\frac{m}{2}x +m+b- mb-a,
& x \in [-2\a, 2-2\b), \\
-\frac{1}{2} x-a+1,
& x \in [2-2\b, 2-2\a], \\
0,
& x \in (2+2\a,\infty),
\end{cases}
\end{aligned} \end{equation}
with
\begin{equation} \label{clinear}
c^* = \begin{cases}
1 - 2a, & \text{if } a \leq b/2, \\
1 -b + \frac{b - 2a}{m}, & \text{if }a > b/2.
\end{cases}
\end{equation}

Observe that $w_2$ has a global maximum at $x=-2\a$ so that $||w_2||_\infty=m+(b-a)(1-m)$. Thus, a sufficient condition for the existence of the periodic traveling wave is $w_2(-2\a)=m+(b-a)(1-m) < \b$.

The intermediate wave speeds are given by
\begin{equation} \begin{aligned}
c_1^*(\ell) 
&= 1-2\ell
\end{aligned}
\end{equation}
and
\begin{equation} \begin{aligned}
c_2^*(\ell) 
&= \begin{cases}
1 - 4a + 2\ell, & a \leq b/2, \\
1 - 2b + \frac{2b-4a}{m} + 2\ell, & a > b/2 ,
\end{cases}
\end{aligned} \end{equation}
for $0 < \ell < m + (b-a)(1-m)$. By evaluating the intermediate wave speeds at $\ell=\a$, it is easily seen that $c_1^*(\a)=c_2^*(\a)$ if $\a \leq \b/2$, and $|c_1^*(\a)-c_2^*(\a)|=2(2\a-\b)(\frac{1-\m}{\m})>0$ if $a>b/2$. So for $a>b/2$, the traveling wave is periodic with two different intermediate wave speeds. Furthermore, the difference between these two intermediate speeds is increasing with respect to the Allee threshold $\a$ and decreasing with respect to the overcompensation threshold $\b$.

Figure \ref{fig:uniformplot1} depicts the periodic traveling wave solution \ref{ptw} with the uniform kernel with growth parameters are $\a=0.325$, $\b=0.6$, and $\m=0.45$. The mean spreading speed can be analytically calculated as $c^*=\frac{13}{45}$. The intermediate speeds are $c_1^*(\a)=\frac{7}{20}$ and $c_2^*(\a)=\frac{41}{180}$. Figure \ref{fig:uniformplot2} demonstrates the spreading phenomena with initial domain rize $r_0=1$. Since our uniform kernel is compact with support $[-1,1]$, a sufficient lower bound on the initial domain size is $r_0 \geq 3$.

\begin{figure}
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \raisebox{6mm}{\includegraphics[width=\linewidth]{figures/fig8.png}}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \raisebox{6mm}{\includegraphics[width=\linewidth]{figures/fig9.png}}
\end{minipage}
\par
\medskip
\noindent
\begin{minipage}[t]{.49\textwidth}
  \centering
  \captionof{figure}{Periodic traveling wave solution with uniform dispersal kernel.}
  \label{fig:uniformplot1}
\end{minipage}%
\hfill
\begin{minipage}[t]{.49\textwidth}
  \centering
  \captionof{figure}{Spreading behavior of the uniform kernel.}
  \label{fig:uniformplot2}
\end{minipage}
\end{figure}

\begin{thebibliography}{9}
\bibitem{all}  W. C. Allee. 1931. Animal Aggregations. A Study on
General Sociology. University of Chicago Press, Chicago, IL.

%\bibitem{htw90} D. P. Hardin, P. Tak$\acute{\mbox{a}}\check{\mbox{c}}$, and G. F. Webb. 1990. Dispersion population %models discrete in time and
%continuous in space. J. Math. Biol. {\bf 28}: 1-20.

\bibitem{hh} A. Hastings and K. Higgins. 1994. Persistence of transients in spatially
structured ecological models. Science {\bf 263}: 1133-1136.

%\bibitem{hz} S.-B. Hsu and X.-Q. Zhao. 2008. Spreading speeds and traveling waves for nonmonotone integrodifference equations. SIAM J. Math. Anal. {\bf} 40: 776–789

\bibitem{ks} M. Kot and W. M. Schaffer. 1986.  Discrete-time growth-dispersal models.
Math. Biosci. {\bf 80}: 109-136.

\bibitem{kot89} M. Kot. 1989. Diffusion-driven period doubling bifurcations.
Biosystems {\bf 22}: 279-287.

\bibitem{kot92} M. Kot. 1992. Discrete-time traveling waves:
Ecological examples. J. Math. Biol. {\bf 30}: 413-436.

\bibitem{kot1} M. Kot, M. A. Lewis, and P. van den Driessche. 1996. Dispersal data and the spread of invading
organisms. Ecology {\bf 77}: 2027-2042.

%\bibitem{kot2} M. Kot, J. Medlock, T. Reluga, and D. B. Walton. 2004. Stochasticity, invasions, and branching random walks. Theor. Popul. Biol. {\bf 66}: 175-184.

%\bibitem{li09} B. Li, M. A. Lewis, and H. F. Weinberger. 2009.  Existence of traveling waves for integral recursions with nonmonotone growth functions. J. Math. Biol. {\bf 58}: 323-338.

\bibitem{kotbook} M. Kot. 2001. Elements of Mathematical Ecology.
Cambridge University Press. Cambridge, United Kingdom.

\bibitem{lui82a} R. Lui. 1982. A nonlinear integral operator arising from a model in population
genetics. I. Monotone initial data. SIAM. J. Math. Anal. {\bf 13}:
913-937.

\bibitem{lui82b} R. Lui. 1982. A nonlinear integral operator arising from a model in population
genetics. II. Initial data with compact support. SIAM. J. Math.
Anal. {\bf 13}: 938-953.

\bibitem{lui83} R. Lui. 1983. Existence and stability of traveling wave solutions of a nonlinear
integral operator. J. Math. Biol. {\bf 16}:199-220.

\bibitem{lut}
F. Lutscher. 2019. Integrodifference Equations in Spatial Ecology.  Springer.

\bibitem{nkl} M. Neubert, M. Kot, and M. A. Lewis. 1995. Dispersal and pattern formation in a
discrete-time predator-prey model. Theor. Pop. Biol. {\bf 48}
: 7-43.

\bibitem{otto} G. Otto. 2017. Non-spreading Solutiona in a Integro-Difference Model Incorporating Allee and Overcompensation Effects. Ph. D thesis, University of Louisville.

\bibitem{slatkin} M. Slatkin. 1973. Gene flow and selection in a cline.
Genetice {\bf 75}: 733-756.

\bibitem{pnas} L. L. Sullivan, B. Li, T. E. X. Miller, M. G. Neubert, and A. K. Shaw. 2017.
Density dependence in demography and dispersal generates fluctuating invasion speeds. Proc. Natl. Acad. Sci. USA {\bf
114}: 5053-5058.

\bibitem{wang} M. H. Wang, M. Kot, and M. G. Neubert. 2002. Integrodifference equations, Allee effects, and
invasions. J. Math. Biol. {\bf 44}: 150-168.

\bibitem{w78} H. F. Weinberger. 1978. Asymptotic behavior of a model in  population genetics,
in Nonlinear Partial Differential Equations  and Applications, ed.
J. M. Chadam. Lecture Notes in Mathematics {\bf 648}: 47-96.
Springer-Verlag, Berlin.

\bibitem{wein82} H. F.  Weinberger. 1982. Long-time beahvior of a class of biological models. SIAM. J.
Math. Anal. {\bf 13}: 353-396.

\end{thebibliography}

\appendix

\section{Appendix}

\begin{prop}\label{laplacespeedcalculations}
The critical spreading speed $c^*$ for the Laplace kernel falls into one of three cases:
\begin{enumerate}[{Case} 1.]

\item $\a\leq\frac{1}{2}$, $\b\leq\frac{1}{2}$:
$$
c^* = \begin{cases}
\frac{1}{2} \ln \left( \frac{\b-\a(1-\m)}{4\a^2\b} \right), & \a < \frac{\b-\a(1-\m)}{2\b}, \\
\frac{1}{2} \ln \left( \frac{1-\a + \sqrt{(1-\a)^2 - \frac{\a(1-\m)}{\b}}}{2\a} \right), & \frac{\b-\a(1-\m)}{2\b} \leq \a \leq \frac{\b(1+\m)-\a}{2\b}, \\
\frac{1}{2} \ln \left( \frac{\a-\m}{\b(1-\m)-\a}\right), & \a > \frac{\b(1+\m)-\a}{2\b}.
\end{cases}
$$

\item $\a\leq\frac{1}{2}$, $\b>\frac{1}{2}$:
$$
c^* = \begin{cases}
\frac{1}{2} \ln \left( \frac{1-4\a(1-\m)(1-\b)}{4\a^2} \right), & a<\frac{1-4\a(1-\m)(1-\b)}{2}, \\
\frac{1}{2} \ln \left( \frac{1-\a + \sqrt{(1-\a)^2 - 4\a(1-\m)(1-\b)}}{2\a} \right), & \frac{1-4\a(1-\m)(1-\b)}{2}\leq\a\leq\frac{1+\m-4\a(1-\b)}{2}, \\
\frac{1}{2} \ln \left( \frac{4(\a-\m)(1-\b)}{1-\m-4\a(1-\b)}\right), & \a>\frac{1+\m-4\a(1-\b)}{2}.
\end{cases}
$$

\item $\a>\frac{1}{2}$, $\b>\frac{1}{2}$:
$$
c^* = \begin{cases}
\frac{1}{2} \ln \left( \frac{1-\a-(1-\m)(1-\b)}{\a} \right), & \a<\frac{1-\a-(1-\m)(1-\b)}{2(1-\a)}, \\
\frac{1}{2} \ln \Big( 2(1-\a)\left[1-\a + \sqrt{\frac{(1-\a)^3-(1-\m)(1-\b) }{1-\a}}\right] \Big), & \frac{1-\a-(1-\m)(1-\b)}{2(1-\a)}\leq\a\leq\frac{\b-1+\m(1-\a)}{2(1-\a)}, \\
\frac{1}{2} \ln \left( \frac{4(\m-\a)(1-\a)(1-\b)}{1-\b+\m(1-\a)}\right), & \a>\frac{\b-1+\m(1-\a)}{2(1-\a)}.
\end{cases}
$$

\end{enumerate}
\end{prop}
\end{document}

### 2021-08-11 v1/Nestor_Li_Manuscript_v1.tex
final

\documentclass[11pt]{article}

\usepackage{amsmath,amsthm}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{caption,subcaption}

\numberwithin{equation}{section}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{remark}[theorem]{Remark}

\usepackage{authblk}

\title{Periodic Traveling Waves in an Integro-Difference Equation With a Nonmonotone Growth Function and Strong Allee Effect}

\author{Michael Nestor, Bingtuan Li
\thanks{M. Nestor's email is \href{mailto:mdnest01@gmail.com}{mdnest01@gmail.com}. B. Li was partially supported by the National Science Foundation under Grant DMS-1515875 and Grant DMS-1951482.}}

\affil{Department of Mathematics, University of Louisville, \newline Louisville, KY 40292.}

\begin{document}

\maketitle

\begin{abstract}
We analytically establish the existence of a periodic traveling wave for an integro-difference equation with a growth function exhibiting a period two cycle and a strong Allee effect. We also prove the convergence of solutions with compactly supported initial data to translations of the traveling wave under appropriate conditions. 
\end{abstract}

{\bf Key words:} Integro-difference equation, period two cycle, Allee effect, periodic traveling wave.
\newline

{\bf AMS Subject Classification:} 92D40, 92D25.

\section{Introduction}

Integro-difference equations are of great interest in the studies of invasions of populations with discrete generations and separate growth and dispersal stages. They have been used to predict changes in gene frequency \cite{lui82a, lui82b, lui83, slatkin, w78}, and applied to ecological problems~\cite{hh, ks, kot89, kot92, kotbook, lut, nkl,otto}. Previous rigrous studies on integro-difference equations have assumed that the growth function is nondecreasing~\cite{w78, wein82}, or  is nonmonotone without strong Allee effect~\cite{lui83, wang}. The results show existence of constant spreading speeds and travelng waves with fixed shapes and speeds.   Sullivan et al. ~\cite{pnas} demonstrated numerically  that an integro-difference equation with a nonmonotone growth function exhibiting  a strong Allee effect can generate traveling waves with fluctuating speeds. In this paper we analytically prove the existence of periodic traveling waves with a periodic speed for such an equation with a specific growth function and dispersal kernel.

We consider the following integro-difference equation
\begin{align}\label{q}
u_{n+1}(x)\;=\;Q[u_n](x)\;:=(k*(g\circ u_n))(x)\;=\,\int^{\infty}_{-\infty}k(x-y)\,g\big(u_n(y)\big)\,\mathrm{d}y,
\end{align}
where 
\begin{equation} \label{g}
g(u) = \begin{cases}
0, & \text{if } 0 \leq u < a, \\
n_2, & \text{if } a \leq u < b, \\
n_1, & \text{if } u \geq b,
\end{cases}
\end{equation}
with 
$0<a<n_1<b<n_2$,
and
\begin{equation} \label{k}
k(x) = \begin{cases}
\frac{1}{2\alpha}, & \text{if } |x| \leq \alpha, \\
0, & \text{otherwise},
\end{cases}
\end{equation}
with $\alpha >0$. $g(u)$ is a piecewise constant nonmonotone growth function exhibiting a strong Allee effect~\cite{all}. Specifically, it has a stable fixed point at zero and a stable period two cycle $(n_1,n_2)$ with $a$ the Allee threshold value. The graph of $g(u)$ with $a=0.33,b=0.75,n_1=0.5,n_1=1.0$ is depicted in Figure \ref{fig:g}.
\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{fig1}
\end{center}
\caption{The growth function $g(u)$ with $(a,b,n_1,n_2)=(0.33,0.75,0.5,1.0)$.}
\label{fig:g}
\end{figure}
$k(x)$ is a uniform distribution. Piecewise constant growth functions and uniform distributions have been used in the studies of integro-difference equations; see for example~\cite{kot1, lut,otto,  pnas}. We rigorously construct periodic traveling waves with periodic speeds for (\ref{q}). To the best of our knowledge, this is the first time that traveling waves with oscillating speeds have been analytically established  for scalar spatiotemporal equations with constant parameters. We also show the convergence of solutions with compactly supported initial data to translations of the traveling wave under appropriate conditions. Equation (\ref{q}) may be viewed as a symbolic model for integro-difference equations with a growth function exhibiting a strong Allee effect and a period two cycle. The results obtained this paper provide important insights into integro-difference equations with general growth functions and dispersal kernels.

\section{Periodic traveling waves}

Let $x_0 = \alpha \left(1-\frac{2b}{n_2}\right)$ and $c_1 = \alpha \left(1- \frac{2a}{n_2}\right)$.
Define 
\begin{equation}  \label{w1}
\begin{aligned}
w_1(x) 
= \begin{cases}
n_2, & x \in (-\infty, -\alpha), \\
\frac{n_2}{2} - \frac{n_2}{2\alpha}x, & x \in [-\alpha, \alpha] ,\\
0, & x \in (\alpha, \infty),
\end{cases}
\end{aligned} \end{equation}
and 
\begin{equation} \label{w2}
\begin{aligned}
w_2(x) 
= \begin{cases}
n_1,
& x \in (-\infty, x_0-\alpha), \\
\frac{n_2-n_1}{2\alpha}(x - (x_0 - \alpha))+n_1,
& x \in [x_0 - \alpha, 
 c_1- \alpha), \\
-\frac{n_1}{2\alpha}(x-(x_0+\alpha))+b-a,
& x \in [c_1 - \alpha, x_0 + \alpha), \\
-\frac{n_2}{2\alpha} (x - (c_1 + \alpha)),
& x \in [x_0 + \alpha, c_1 + \alpha], \\
0,
& x \in (c_1+\alpha,\infty).
\end{cases}
\end{aligned} \end{equation}

\begin{figure*} \label{fig2}
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[scale=0.25]{fig2a}
        \caption{$w_1(x)$}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[scale=0.25]{fig2b}
        \caption{$w_2(x)$}
    \end{subfigure}
    \caption{Profiles of $w_1(x)$ and $w_2(x)$ with $(a,b,n_1,n_2)=(0.33,0.75,0.5,1.0)$.}
    \label{fig:w1andw2}
\end{figure*}

Clearly $w_1(x)$ is non-increasing while $w_2(x)$ is nonmonotonic. The graphs of $w_1(x)$ and $w_2(x)$ with specific parameter values are given in Figure \ref{fig:w1andw2}.

\begin{theorem}\label{thm1}
Let
\begin{equation} \label{h1}
0<a<n_1<b<n_2, \  \   \frac{n_2}{n_1} < \frac{b-a}{n_1-a}.
\end{equation}
Then 
$$w_2(x)=Q[w_1](x),  \   \   w_1(x-2c^*)=Q[w_2](x),$$
 with 
\begin{equation} \label{c}
c^* = \begin{cases}
\alpha \left( 1 - \frac{2}{n_2}a \right), & \text{if } a \leq b/2, \\
\alpha \left( 1  + \frac{b - 2a}{n_1} - \frac{b}{n_2} \right), & \text{if }a > b/2.
\end{cases}
\end{equation}
\end{theorem}

\begin{proof} $w_1(x)$ can be written as
$$
    w_1(x) = n_2 (1-K(x)),
$$
where $K(x)$ is the cumulative density function $K(x) = \int_{-\infty}^{x} k(y)$. Then $w_1(x)$ is decreasing on $(-\alpha,\alpha)$, and satisfies $0\leq w_1(x)<a$ for $x\in(c_1,\infty)$, $a\leq w_1(x)<b$ for $x\in[x_0,c_1]$, and $w_1(x)\geq b$ for $x\in(-\infty,x_0)$. Thus, $g(w_1(x))$ is given by
$$
g( w_1(x)) = \begin{cases}
n_1, & x \in (-\infty, x_0), \\
n_2, & x \in [x_0, c_1], \\ 
0, & x \in (c_1, \infty). \end{cases}.
$$
Applying convolution with $k(x)$:
$$ \begin{aligned}
    Q[w_1](x) &= (k*(g\circ w_1))(x) \\&= (n_2-n_1) K(x-x_0) - n_2 K(x-c_1).
\end{aligned} $$
Computing the right hand side yields $\eqref{w2}$, thus $Q[w_1]=w_2$.

To compute $Q[w_2]$, observe that $w_2$ has a global maximum at $c_1-\alpha$, and that the last inequality in $\eqref{h1}$ is equivalent to $w_2(c_1-\alpha)<b$. Hence, $w_2(x)<b$ for all $x$. Note that $w_2(x)$ decreases from its maximum at $c_1-\alpha$ to zero on the interval $[c_1-\alpha,c_1+\alpha]$, so there is a unique point $\xi$ in this interval such that $w_2(\xi)=a$. Therefore,
$$
g(w_2(x)) = \begin{cases}
n_2, & x \in (-\infty,\xi], \\
0, & x \in (0,\infty).
\end{cases}
$$
and
$$ \begin{aligned}
Q[w_2](x)
&= n_2 (1-K(x-\xi)) \\
&= w_1(x-\xi).
\end{aligned} $$

By defining $c^*=\xi/2$, we have $w_1(x-2c^*)=Q[w_2](x)$. Thus, $w_1(x)$ and $w_2(x)$ form a period two traveling wave with average speed $c^*$.

The value of $c^*$ can be computed as the unique solution to $w_2(2c^*)=a$, or equivalently $c^*=\frac{1}{2}w_2^{-1}(a)$. Observe that $w_2(x_0+\alpha)-a=b-2a$, so there are two cases. If $a\leq b/2$ then $\xi\in[x_0+\alpha,c_1+\alpha]$, and $c^*$ is given by $c^*=\frac{1}{2}\ell_1^{-1}(a)=\alpha \left( 1 - \frac{2}{n_2}a \right)$ where
$$ \ell_1(x)=-\frac{n_2}{2\alpha} (x - (c_1 + \alpha)).$$
Otherwise, if $a>b/2$, then $\xi\in[c_1-\alpha,x_0+\alpha)$ and $c^*=\frac{1}{2}\ell_2^{-1}(a)=\alpha \left( 1  + \frac{b - 2a}{n_1} - \frac{b}{n_2} \right)$ where
$$ \ell_2(x)=-\frac{n_1}{2\alpha}(x-(x_0+\alpha))+b-a.$$
The proof is complete.
\end{proof}

\begin{remark}
$w_1(x)$ is positive for $x<\alpha$ and zero for $x\geq\alpha$, and $w_2(x)$ is positive for $x<c_1+\alpha$ and zero for $x\geq c_1+\alpha$.  $Q[w_1](x)=w_2(x)$ shows that the wave front point travels a distance $c_1$, and $Q[w_1](x)=w_1(x-2c^*)$ indicates that the wave front point travels a distance $c_2=2c^*-c_1$. This theorem shows that $\eqref{q}$ has a traveling wave with wave profiles $w_1(x)$ and $w_2(x)$, intermediate wave speeds $c_1$ and $c_2$,  and average wave speed  $c^*$.  It is easily seen that $c_1=c_2$ if $a \leq b/2$, and $c_1-c_2=2\alpha (b-2a)(\frac{1}{n_2}-\frac{1}{n_1})\not=0$ if $a>b/2$. So for $a>b/2$, the traveling wave is periodic with two different intermediate wave speeds. This behavior is illustrated with two difference choices of parameters in Figure \ref{fig:wavespeed}.
\end{remark}

\begin{remark}
The traveling wave is advancing if $c^*>0$ and receding if $c^*<0$. The sign of the wave speed can be written in two cases:
\begin{equation}
\text{sign}(c^*) = \text{sign}\left(n_2 - 2a\right), \text{ if } a \leq b/2, \end{equation}
and
\begin{equation}
\text{sign}(c^*) =
\text{sign}\left(\frac{n_1}{n_2} - \frac{2a-b}{n_2-b}\right),  \text{ if } a > b/2. 
\end{equation}
\end{remark}

\begin{remark}
$w_1(-x)$ and $w_2(-x)$ are profiles of a traveling wave moving leftward at 
 intermediate wave speeds $c_1$ and $c_2$, and average wave speed  $c^*$. This is due to the fact that $Q$ is symmetric and translation invariant.
\end{remark}

\begin{figure*}
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[scale=0.25]{fig3a}
        \caption{Constant wave speed, \newline $(a,b,n_1,n_2)=(0.2,0.8,0.5,1.0)$.}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[scale=0.25]{fig3b}
        \caption{Oscillating wave speed, \newline $(a,b,n_1,n_2)=(0.35,0.6,0.45,1.0)$.}
    \end{subfigure}
    \caption{Traveling wave behavior of $w_1(x)$ and $w_2(x)$.}
    \label{fig:wavespeed}
\end{figure*}

The regions in the parameter space where oscillating spreading speed exists can be determined as follows: for any fixed choice of $(n_1,n_2)$, with $0<n_1<n_2$, let $R$ be the set of pairs $(a,b)\in\mathbf R^2$ such that the hypothesis of Theorem 2.1 holds. Then $R$ is a triangle in the $a$-$b$ plane with endpoints at $(0,n_2)$, $(n_1,n_1)$, and $(n_1,n_2)$, depicted in Figure \ref{fig:phaseportrait}. The line $b=2a$ partitions $R$ into two non-empty sets $R_1=\{(a,b)\in R:a\leq b/2\}$ and $R_2=\{(a,b)\in R:a> b/2\}$ such that the traveling has constant speed if $(a,b)\in R_1$ and oscillating speed if $(a,b)\in R_2$.

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{fig4}
\end{center}
\caption{The shaded region $R$ indicates all pairs $(a,b)$ such that the condition in Theorem 2.1 holds for $(n_1,n_2)=(0.6,1.0)$, and the line $b=2a$ is drawn in red. The region $R_1$ contains all pairs $(a,b)$ such that the traveling wave has constant speed, and $R_2$ contains all pairs such that the traveling wave has oscillating speed.}
\label{fig:phaseportrait}
\end{figure}

The next theorem concerns convergence of solutions with compactly supported initial data to translations of the traveling wave. Let
\begin{equation}
r_0 = \max\left\{2\alpha,2\alpha-x_0\right\}.
\end{equation}
\begin{theorem} Assume that the hypothesis of Theorem~\ref{thm1} holds and $c^*\geq0$.  Let $a\leq  u_0(x)<b $ on $[L-r, L+r]$ with $r\geq r_0$ and $L$ a real number, $u_0(x)<a$  for $x\not\in [L-r, L+r]$, and $u_0(x)\equiv 0$ outside a bounded interval.  
Then the solution $u_n$ of $u_{n+1}=Q[u_n]$ is given by
\begin{equation}
u_{2n+1}(x) = \begin{cases}
w_1(x-L-r-2nc^*), & x\in[L,\infty), \\
w_1(-x+L-r-2nc^*), & x\in(-\infty,L),
\end{cases}
\end{equation}
and
\begin{equation}
u_{2n+2}(x) = \begin{cases}
w_2(x-L-r-2nc^*),  & x\in[L,\infty), \\
w_2(-x+L-r-2nc^*), & x\in(-\infty,L).
\end{cases}
\end{equation}
\end{theorem}

\begin{figure*} \label{fig5}
    \centering
    \includegraphics[scale=0.25]{fig5}
    \caption{Speading behavior for bounded initial data with $(a,b,n_1,n_2)=(0.3,0.6,0.7,1.0)$. Shapes of $u_1$ and $u_3$ are labeled in blue, shapes of $u_2$ and $u_4$ in red.}
\label{fig:spread}
\end{figure*}

\begin{proof}
The composition of $g$ with $u_0$ is given by
$$
    g(u_0(x+L)) = \begin{cases}
    n_2, & x \in [-r,r], \\
    0, & x \in(-\infty,-r)\cup(r,\infty).
    \end{cases}
$$
Applying convolution with $k$,
$$ \begin{aligned}
u_1(x+L) &= (k*(g\circ u_0))(x+L) \\
&= n_2 \left( K(x+r)-K(x-r) \right) \\
&= w_1(x-r) - w_1(x+r).
\end{aligned} $$
If $x\geq 0$ and $r\geq \alpha$, then $w_1(x+r)=0$, and hence $u_1(x)=w_1(x-r)$. By the symmetry of $g(u_0(x))$ about the line $x=L$, and the symmetry of the operator $Q$, it follows that $u_1$ is also symmetric about $x=L$, hence
$$ u_1(x+L) = \begin{cases}
w_1(x-r), & x \in [0,\infty), \\
w_1(-x-r), & x \in (-\infty,0).
\end{cases} $$
The support of $u_1$ is $[L-r-\alpha,L+r+\alpha]$. It satisfies $u_1(x+L)=n_2$ for all $x\in[-r+\alpha,r-\alpha]$. Thus $u_1(x+L)=w_1(x-r)$ for all $x\in[-r+\alpha,\infty)$. Applying the operator $Q$, it follows $Q[u_1](x+L)=Q[w_1](x-r)$ for all $x\in[-r+2\alpha,\infty)$. Since $r\geq 2\alpha$, this implies $u_2(x+L)=w_2(x-r)$ for all $x\geq 0$. $Q$ is a symmetric operator, so
$$ u_2(x+L) = \begin{cases}
		w_2(x-r), & x\in[0,\infty), \\
		w_2(-x-r), & x\in(-\infty,0).
\end{cases} $$
$u_2$ has support $[L-r-c_1-\alpha,L+r+c_1+\alpha]$. It satisfies $u_2(x+L)=n_1$ for all $x\in[-r-x_0+\alpha,r+x_0-\alpha]$. Thus $u_2(x+L)=w_2(x-r)$ for all $x\in[-r-x_0+\alpha,\infty)$. Applying the operator $Q$, it follows $Q[u_2](x+L)=Q[w_2](x-r)$ for all $x\in[-r-x_0+2\alpha,\infty)$. Since $r\geq 2\alpha-x_0$ we have $u_2(x+L)=Q[w_2](x-r)$ for all $x\geq 0$. By Theorem 2.1, $u_2(x+L)=w_1(x-r-2c^*)$ for all $x\geq 0$. Since $Q$ is a symmetric operator, we have 
$$ u_3(x+L) = \begin{cases}
		w_1(x-r-2c^*), & x\in[0,\infty), \\
		w_1(-x-r-2c^*), & x\in(-\infty,0).
\end{cases} $$
If $c^*\geq0$, then this process may be repeated inductively, so that
$$
u_{2n+1}(x+L) = \begin{cases}
w_1(x-r-2nc^*), & x\in[0,\infty), \\
w_1(-x-r-2nc^*), & x\in(-\infty,0),
\end{cases} $$
and
$$
u_{2n+2}(x+L) = \begin{cases}
w_2(x-r-2nc^*),  & x\in[0,\infty), \\
w_2(-x-r-2nc^*), & x\in(-\infty,0).
\end{cases} $$
Replacing $x$ by $x-L$, the proof is complete.
\end{proof}

\begin{remark}
This theorem indicates that a solution with proper compactly supported initial data coverges to translations of periodic traveling waves with profiles $w_1(x)$ and $w_2(x)$ in the positive direction and profiles $w_1(-x)$ and $w_2(-x)$ in the negative direction.
\end{remark}

\begin{thebibliography}{9}
\bibitem{all}  W. C. Allee. 1931. Animal Aggregations. A Study on
General Sociology. University of Chicago Press, Chicago, IL.

%\bibitem{htw90} D. P. Hardin, P. Tak$\acute{\mbox{a}}\check{\mbox{c}}$, and G. F. Webb. 1990. Dispersion population %models discrete in time and
%continuous in space. J. Math. Biol. {\bf 28}: 1-20.

\bibitem{hh} A. Hastings and K. Higgins. 1994. Persistence of transients in spatially
structured ecological models. Science {\bf 263}: 1133-1136.

%\bibitem{hz} S.-B. Hsu and X.-Q. Zhao. 2008. Spreading speeds and traveling waves for nonmonotone integrodifference equations. SIAM J. Math. Anal. {\bf} 40: 776–789

\bibitem{ks} M. Kot and W. M. Schaffer. 1986.  Discrete-time growth-dispersal models.
Math. Biosci. {\bf 80}: 109-136.

\bibitem{kot89} M. Kot. 1989. Diffusion-driven period doubling bifurcations.
Biosystems {\bf 22}: 279-287.

\bibitem{kot92} M. Kot. 1992. Discrete-time traveling waves:
Ecological examples. J. Math. Biol. {\bf 30}: 413-436.

\bibitem{kot1} M. Kot, M. A. Lewis, and P. van den Driessche. 1996. Dispersal data and the spread of invading
organisms. Ecology {\bf 77}: 2027-2042.

%\bibitem{kot2} M. Kot, J. Medlock, T. Reluga, and D. B. Walton. 2004. Stochasticity, invasions, and branching random walks. Theor. Popul. Biol. {\bf 66}: 175-184.

%\bibitem{li09} B. Li, M. A. Lewis, and H. F. Weinberger. 2009.  Existence of traveling waves for integral recursions with nonmonotone growth functions. J. Math. Biol. {\bf 58}: 323-338.

\bibitem{kotbook} M. Kot. 2001. Elements of Mathematical Ecology.
Cambridge University Press. Cambridge, United Kingdom.

\bibitem{lui82a} R. Lui. 1982. A nonlinear integral operator arising from a model in population
genetics. I. Monotone initial data. SIAM. J. Math. Anal. {\bf 13}:
913-937.

\bibitem{lui82b} R. Lui. 1982. A nonlinear integral operator arising from a model in population
genetics. II. Initial data with compact support. SIAM. J. Math.
Anal. {\bf 13}: 938-953.

\bibitem{lui83} R. Lui. 1983. Existence and stability of traveling wave solutions of a nonlinear
integral operator. J. Math. Biol. {\bf 16}:199-220.

\bibitem{lut}
F. Lutscher. 2019. Integrodifference Equations in Spatial Ecology.  Springer.

\bibitem{nkl} M. Neubert, M. Kot, and M. A. Lewis. 1995. Dispersal and pattern formation in a
discrete-time predator-prey model. Theor. Pop. Biol. {\bf 48}
: 7-43.

\bibitem{otto} G. Otto. 2017. Non-spreading Solutiona in a Integro-Difference Model Incorporating Allee and Overcompensation Effects. Ph. D thesis, University of Louisville.

\bibitem{slatkin} M. Slatkin. 1973. Gene flow and selection in a cline.
Genetice {\bf 75}: 733-756.

\bibitem{pnas} L. L. Sullivan, B. Li, T. E. X. Miller, M. G. Neubert, and A. K. Shaw. 2017.
Density dependence in demography and dispersal generates fluctuating invasion speeds. Proc. Natl. Acad. Sci. USA {\bf
114}: 5053-5058.

\bibitem{wang} M. H. Wang, M. Kot, and M. G. Neubert. 2002. Integrodifference equations, Allee effects, and
invasions. J. Math. Biol. {\bf 44}: 150-168.

\bibitem{w78} H. F. Weinberger. 1978. Asymptotic behavior of a model in  population genetics,
in Nonlinear Partial Differential Equations  and Applications, ed.
J. M. Chadam. Lecture Notes in Mathematics {\bf 648}: 47-96.
Springer-Verlag, Berlin.

\bibitem{wein82} H. F.  Weinberger. 1982. Long-time beahvior of a class of biological models. SIAM. J.
Math. Anal. {\bf 13}: 353-396.

\end{thebibliography}

\end{document}

\end{document}

### 2021-08-11 figures/fig_accelerating_wave.py

@@ -27,7 +27,7 @@ model = pyide.IDEModel(growthFunction=pyide.GrowthFunction(g),
                 
 sim = pyide.IDESimulation(model)
 sim.setDomain(xmin=-10, xmax=10, dx=0.005)
-r=.58
+r=0.58
 sim.setInitialCondition(lambda x : H(x+r)-H(x-r))
 sim.setBoundaryCondition('static')
 
@@ -38,10 +38,5 @@ plt1 = sim.plot_wavespeed(times=np.arange(1, n),
 predictedcstar = 0.8568,
 predictedc1 = 2*0.8568 + np.log(2/5),
 predictedc2 = -np.log(2/5),
-level=0.2,
-file='fig_accelerating_wave2.png')
-plt1.show()
-import matplotlib.pyplot as plt
-plt.plot([1,11], [.444, .444])
-#print(sim.timeSeries)
-
+level=alpha,
+                         file='fig_accelerating_wave2.png')

### 2021-08-11 figures/pyide.py

@@ -325,16 +325,32 @@ class IDESimulation:
             C.append((d1-d0))
             d0 = d1
             
-        axs.plot(times[1:], C)
-        axs.set_xlabel('t')
-        axs.set_ylabel('c_n(t)')
-        try:
-            plt.savefig(file)
-        except:
-            pass
+        axs.plot(times[1:], C, color='black')
+        #axs.plot(times[1:], C, 'o', color='blue')
+        axs.set_xlabel('$n$')
+        axs.set_ylabel('$c_n(a)$', rotation=0, labelpad=40)
+        
         plt.plot([1, max(times)], [predictedcstar, predictedcstar], 'b--')
         plt.plot([1, max(times)], [predictedc1, predictedc1], 'b:')
         plt.plot([1, max(times)], [predictedc2, predictedc2], 'b:')
+        
+        ax2 = axs.twinx() 
+  
+        axs.set_ylim(0.5, 1)
+        ax2.set_ylim(0.5, 1)
+    
+        #color = 'tab:green'
+        #ax2.set_ylabel('Y2-axis', color = color) 
+        ax2.plot(times[1:], C, 'o', color='black')
+        #ax2.tick_params(axis ='y', labelcolor = color) 
+        ax2.set_xticks([])
+        ax2.set_yticks([predictedc1,predictedcstar,predictedc2])
+        ax2.set_yticklabels(['$c_1^*(a)$','$c^*$','$c_2^*(a)$'])
+
+        try:
+            plt.savefig(file,bbox_inches='tight')
+        except:
+            pass
         return plt
         
     def plot(self, times=[], file=None):
@@ -351,10 +367,10 @@ class IDESimulation:
         for t in times:
             U = U_seq[t]
             axs.plot(X, U, color=(t/T,1-t/T,0))
-        axs.set_xlabel('x')
-        axs.set_ylabel('u_n(x)')
+        axs.set_xlabel('$x$')
+        axs.set_ylabel('$u_n(x)$', rotation=0, labelpad=40)
         try:
-            plt.savefig(file)
+            plt.savefig(file,bbox_inches='tight')
         except:
             pass
         return plt
